\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{MILP Model for Network Intrusion Intervention}

\subsection*{Sets and Indices}
\begin{itemize}
    \item $i \in \{1, \ldots, N\}$: Index for clusters.
    \item $\text{type} \in \{\text{isolate}, \text{scan}\}$: Intervention types.
    \item $\text{method} \in \{\text{central}, \text{distributed}\}$: Processing methods.
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item $PT_{\text{central}}^{\text{isolate}}[i]$: Processing time for isolating cluster $i$ centrally.
    \item $PT_{\text{central}}^{\text{scan}}[i]$: Processing time for scanning cluster $i$ centrally.
    \item $PT_{\text{distributed}}^{\text{isolate}}[i]$: Processing time for isolating cluster $i$ distributedly.
    \item $PT_{\text{distributed}}^{\text{scan}}[i]$: Processing time for scanning cluster $i$ distributedly.
    \item $\text{central\_cost}$: Cost per hour for central processing.
    \item $\text{distributed\_cost}$: Cost per hour for distributed processing.
    \item $\text{max\_central}$: Maximum allowable central processing hours.
    \item $\text{max\_distributed}$: Maximum allowable distributed processing hours.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item $x_{\text{central}}^{\text{isolate}}[i]$: Binary variable, 1 if isolating cluster $i$ centrally, 0 otherwise.
    \item $x_{\text{central}}^{\text{scan}}[i]$: Binary variable, 1 if scanning cluster $i$ centrally, 0 otherwise.
    \item $x_{\text{distributed}}^{\text{isolate}}[i]$: Binary variable, 1 if isolating cluster $i$ distributedly, 0 otherwise.
    \item $x_{\text{distributed}}^{\text{scan}}[i]$: Binary variable, 1 if scanning cluster $i$ distributedly, 0 otherwise.
\end{itemize}

\subsection*{Objective Function}
Minimize the total cost:
\begin{align*}
\text{Minimize} \quad & \sum_{i=1}^{N} \left( \text{central\_cost} \cdot \left( x_{\text{central}}^{\text{isolate}}[i] \cdot PT_{\text{central}}^{\text{isolate}}[i] + x_{\text{central}}^{\text{scan}}[i] \cdot PT_{\text{central}}^{\text{scan}}[i] \right) \right.\\
& \left. + \text{distributed\_cost} \cdot \left( x_{\text{distributed}}^{\text{isolate}}[i] \cdot PT_{\text{distributed}}^{\text{isolate}}[i] + x_{\text{distributed}}^{\text{scan}}[i] \cdot PT_{\text{distributed}}^{\text{scan}}[i] \right) \right)
\end{align*}

\subsection*{Constraints}
\begin{itemize}
    \item Each cluster must have exactly one type and method of intervention:
    \begin{align*}
    x_{\text{central}}^{\text{isolate}}[i] + x_{\text{central}}^{\text{scan}}[i] + x_{\text{distributed}}^{\text{isolate}}[i] + x_{\text{distributed}}^{\text{scan}}[i] = 1, \quad \forall i
    \end{align*}

    \item Total central processing time should not exceed the maximum allowed:
    \begin{align*}
    \sum_{i=1}^{N} \left( x_{\text{central}}^{\text{isolate}}[i] \cdot PT_{\text{central}}^{\text{isolate}}[i] + x_{\text{central}}^{\text{scan}}[i] \cdot PT_{\text{central}}^{\text{scan}}[i] \right) \leq \text{max\_central}
    \end{align*}

    \item Total distributed processing time should not exceed the maximum allowed:
    \begin{align*}
    \sum_{i=1}^{N} \left( x_{\text{distributed}}^{\text{isolate}}[i] \cdot PT_{\text{distributed}}^{\text{isolate}}[i] + x_{\text{distributed}}^{\text{scan}}[i] \cdot PT_{\text{distributed}}^{\text{scan}}[i] \right) \leq \text{max\_distributed}
    \end{align*}

    \item Binary constraints for decision variables:
    \begin{align*}
    x_{\text{central}}^{\text{isolate}}[i], x_{\text{central}}^{\text{scan}}[i], x_{\text{distributed}}^{\text{isolate}}[i], x_{\text{distributed}}^{\text{scan}}[i] \in \{0, 1\}, \quad \forall i
    \end{align*}
\end{itemize}

\end{document}