\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model}

\subsection*{Variables}
\begin{itemize}
    \item \( buyquantity_{i,m} \): Amount of oil \( i \) bought in month \( m \).
    \item \( refine_{i,m} \): Amount of oil \( i \) refined in month \( m \).
    \item \( storage_{i,m} \): Amount of oil \( i \) stored at the end of month \( m \).
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( price_{i,m} \): Price of oil \( i \) in month \( m \).
    \item \( sell\_price \): Selling price of the final product per ton.
    \item \( is\_vegetable_{i} \): Indicator if oil \( i \) is vegetable (1) or non-vegetable (0).
    \item \( max\_veg \): Maximum vegetable oil refining per month.
    \item \( max\_veg \): Maximum non-vegetable oil refining per month.
    \item \( storage\_size \): Maximum storage capacity for each oil.
    \item \( storage\_cost \): Cost of storage per ton per month.
    \item \( max\_hardness \): Maximum allowable hardness of the final product.
    \item \( min\_hardness \): Minimum allowable hardness of the final product.
    \item \( hardness_{i} \): Hardness of oil \( i \).
    \item \( init\_amount \): Initial amount of each type of raw oil in storage.
\end{itemize}

\subsection*{Objective Function}
Maximize profit:
\[
\text{Profit} = \sum_{m=1}^{M} \left( sell\_price \cdot \sum_{i=1}^{I} refine_{i,m} - \sum_{i=1}^{I} (price_{i,m} \cdot buyquantity_{i,m} + storage\_cost \cdot storage_{i,m}) \right)
\]

\subsection*{Constraints}

1. **Storage Update Equation:**
   \[
   storage_{i,m} = storage_{i,m-1} + buyquantity_{i,m} - refine_{i,m} \quad \forall i, m
   \]

2. **Initial Storage Requirement:**
   \[
   storage_{i,0} = init\_amount \quad \forall i
   \]

3. **Final Storage Requirement:**
   \[
   storage_{i,M} = init\_amount \quad \forall i
   \]

4. **Refining Capacity Constraints:**
   \[
   \sum_{i \,|\, is\_vegetable_{i}=1} refine_{i,m} \leq max\_veg \quad \forall m
   \]
   \[
   \sum_{i \,|\, is\_vegetable_{i}=0} refine_{i,m} \leq max\_veg \quad \forall m
   \]

5. **Storage Capacity Constraints:**
   \[
   storage_{i,m} \leq storage\_size \quad \forall i, m
   \]

6. **Hardness Constraints:**
   \[
   \frac{\sum_{i=1}^{I} (hardness_{i} \cdot refine_{i,m})}{\sum_{i=1}^{I} refine_{i,m}} \leq max\_hardness \quad \forall m
   \]
   \[
   \frac{\sum_{i=1}^{I} (hardness_{i} \cdot refine_{i,m})}{\sum_{i=1}^{I} refine_{i,m}} \geq min\_hardness \quad \forall m
   \]

\subsection*{Output Format}
\begin{itemize}
    \item Buy Quantity: \( buy = [[buyquantity_{i,m} \text{ for } i=1,...,I] \text{ for } m=1,...,M] \)
    \item Refined Quantity: \( refine = [[refine_{i,m} \text{ for } i=1,...,I] \text{ for } m=1,...,M] \)
    \item Storage: \( storage = [[storage_{i,m} \text{ for } i=1,...,I] \text{ for } m=1,...,M] \)
\end{itemize}

\end{document}