\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model}

\subsection*{Indices}
\begin{itemize}
    \item \( i \): index for system types, \( i = 1, \ldots, N \)
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \(\text{price}_i\): Price of system \( i \) in dollars.
    \item \(\text{disk}_i\): Average number of disk drives requested per system \( i \).
    \item \(\text{mem}_i\): Average number of 256K memory boards per system \( i \).
    \item \(\text{max\_cpu}\): Maximum number of CPUs available.
    \item \(\text{min\_disk}\), \(\text{max\_disk}\): Minimum and maximum disk drives available.
    \item \(\text{min\_mem}\), \(\text{max\_mem}\): Minimum and maximum 256K memory boards available.
    \item \(\text{demand}_i\): Maximum demand for system \( i \).
    \item \(\text{demand\_GP}\): Maximum demand for all general-purpose systems.
    \item \(\text{demand\_WS}\): Maximum demand for all workstation systems.
    \item \(\text{preorder}_i\): Preorders for system \( i \).
    \item \(\text{alt\_mem}\): Available alternative memory boards.
    \item \(\text{is\_workstation}[i]\): Boolean indicating if system \( i \) is a workstation.
    \item \(\text{alt\_compatible}[i]\): Boolean indicating if system \( i \) can use alternative memory.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( x_i \): Number of system \( i \) produced (continuous).
    \item \( \text{mem\_used}_i \): Number of 256K memory boards used by system \( i \).
    \item \( \text{alt\_used}_i \): Number of alternative memory boards used by system \( i \).
    \item \( \text{disk\_used}_i \): Number of disk drives used by system \( i \).
\end{itemize}

\subsection*{Objective Function}
Maximize the total profit:
\[
\text{Maximize: } \sum_{i=1}^{N} \text{price}_i \times x_i
\]

\subsection*{Constraints}
\begin{align}
    & \sum_{i=1}^{N} x_i \leq \text{max\_cpu} & \text{(CPU constraint)} \\
    & \sum_{i=1}^{N} \text{disk}_i \times x_i \leq \text{max\_disk} & \text{(Max disk constraint)} \\
    & \sum_{i=1}^{N} \text{disk}_i \times x_i \geq \text{min\_disk} & \text{(Min disk constraint)} \\
    & \sum_{i=1}^{N} \text{mem}_i \times x_i \leq \text{max\_mem} & \text{(Max memory constraint)} \\
    & \sum_{i=1}^{N} \text{mem}_i \times x_i \geq \text{min\_mem} & \text{(Min memory constraint)} \\
    & \text{mem\_used}_i + \text{alt\_used}_i = \text{mem}_i \times x_i, & \forall i \\
    & \text{alt\_used}_i \leq \text{alt\_compatible}[i] \times \text{alt\_mem}, & \forall i \\
    & x_i \leq \text{demand}_i & \forall i \\
    & \sum_{i: \neg \text{is\_workstation}[i]} x_i \leq \text{demand\_GP} & \text{(GP demand constraint)} \\
    & \sum_{i: \text{is\_workstation}[i]} x_i \leq \text{demand\_WS} & \text{(WS demand constraint)} \\
    & x_i \geq \text{preorder}_i & \forall i
\end{align}

\end{document}