\documentclass{article}
\usepackage{amsmath}

\begin{document}

\section*{Mathematical Model}

\textbf{Given:}
\begin{itemize}
    \item $W$: Number of weeks in the season.
    \item $\text{demand}_{w}$: Demand for baskets in week $w$.
    \item $\text{regular\_labor}_{w}$: Maximum regular labor hours available in week $w$.
    \item $\text{regular\_cost}$: Cost per hour for regular labor.
    \item $\text{overtime\_labor}_{w}$: Maximum overtime labor hours available in week $w$.
    \item $\text{overtime\_cost}$: Cost per hour for overtime labor.
    \item $\text{assembly\_time}$: Hours of labor required to assemble one basket.
    \item $\text{material\_cost}$: Material cost per basket.
    \item $\text{selling\_price}$: Selling price per basket.
    \item $\text{holding\_cost}$: Holding cost per unsold basket at the end of each week.
    \item $\text{salvage\_value}$: Salvage value per unsold basket at the end of week $W$.
\end{itemize}

\textbf{Variables:}
\begin{itemize}
    \item $\text{regular\_used}_{w}$: Hours of regular labor used in week $w$.
    \item $\text{overtime\_used}_{w}$: Hours of overtime labor used in week $w$.
    \item $\text{regular\_basket}_{w}$: Number of baskets assembled with regular labor in week $w$.
    \item $\text{overtime\_basket}_{w}$: Number of baskets assembled with overtime labor in week $w$.
    \item $\text{inventory}_{w}$: Number of baskets on hand at the end of week $w$.
\end{itemize}

\textbf{Objective:}

Maximize the total profit over the season:

\[
\begin{aligned}
\text{max} \quad & \sum_{w=1}^{W} \left( \text{selling\_price} \times (\text{regular\_basket}_w + \text{overtime\_basket}_w) - \text{regular\_cost} \times \text{regular\_used}_w \right. \\
& \left. - \text{overtime\_cost} \times \text{overtime\_used}_w - \text{material\_cost} \times (\text{regular\_basket}_w + \text{overtime\_basket}_w) \right. \\
& \left. - \text{holding\_cost} \times \text{inventory}_{w} \right) + \text{salvage\_value} \times \text{inventory}_{W}
\end{aligned}
\]

\textbf{Subject to:}

For each week $w = 1, \ldots, W$:

\begin{align*}
& \text{regular\_used}_{w} + \text{overtime\_used}_{w} \geq \text{assembly\_time} (\text{regular\_basket}_{w} + \text{overtime\_basket}_{w}) \\
& \text{regular\_used}_{w} \leq \text{regular\_labor}_{w} \\
& \text{overtime\_used}_{w} \leq \text{overtime\_labor}_{w} \\
& \text{inventory}_{w-1} + \text{regular\_basket}_{w} + \text{overtime\_basket}_{w} = \text{demand}_{w} + \text{inventory}_{w} \\
& \text{inventory}_{0} = 0
\end{align*}

All variables $\text{regular\_used}_{w}$, $\text{overtime\_used}_{w}$, $\text{regular\_basket}_{w}$, $\text{overtime\_basket}_{w}$, $\text{inventory}_{w}$ must be non-negative.

\end{document}