\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{MIP Model for DEC Production Planning}

\subsection*{Sets and Parameters}
\begin{itemize}
    \item \( N \): Number of different computer systems.
    \item \( \text{is\_workstation}_i \): Boolean indicating if system \( i \) is a workstation.
    \item \( \text{price}_i \): Price of system \( i \).
    \item \( \text{disk\_drives}_i \): Average units of disk drive per system \( i \).
    \item \( \text{256K\_boards}_i \): Average units of 256K memory boards per system \( i \).
    \item \( \text{max\_cpu} \): Maximum CPU units available.
    \item \( \text{min\_disk}, \text{max\_disk} \): Minimum and maximum disk drives available.
    \item \( \text{min\_mem}, \text{max\_mem} \): Minimum and maximum 256K memory boards available.
    \item \( \text{demand}_i \): Maximum demand for system \( i \).
    \item \( \text{demand\_GP} \): Maximum demand for GP systems.
    \item \( \text{demand\_WS} \): Maximum demand for WS systems.
    \item \( \text{preorder}_i \): Pre-orders for system \( i \).
    \item \( \text{alt\_mem} \): Available alternative memory boards.
    \item \( \text{alt\_compatible}_i \): Boolean indicating if system \( i \) can use alternative memory boards.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( x_i \): Number of systems \( i \) produced.
    \item \( y_i \): Number of 256K memory boards used for system \( i \).
    \item \( z_i \): Number of alternative memory boards used for system \( i \).
    \item \( w_i \): Number of disk drives used for system \( i \).
\end{itemize}

\subsection*{Objective Function}
Maximize the profit:
\[
\text{Maximize } \sum_{i=1}^{N} \text{price}_i \times x_i
\]

\subsection*{Constraints}
\begin{align}
    & \sum_{i=1}^{N} x_i \leq \text{max\_cpu} \\
    & \sum_{i=1}^{N} y_i \leq \text{max\_mem} \\
    & \sum_{i=1}^{N} z_i \leq \text{alt\_mem} \\
    & \sum_{i=1}^{N} w_i \geq \text{min\_disk} \\
    & \sum_{i=1}^{N} w_i \leq \text{max\_disk} \\
    & x_i \geq \text{preorder}_i \quad \forall i \\
    & \sum_{\text{is\_workstation}_i = \text{false}} x_i \leq \text{demand\_GP} \\
    & \sum_{\text{is\_workstation}_i = \text{true}} x_i \leq \text{demand\_WS} \\
    & x_i \leq \text{demand}_i \quad \forall i \\
    & z_i = 0 \quad \text{if } \text{alt\_compatible}_i = \text{false} \\
    & y_i + z_i = \text{256K\_boards}_i \times x_i \quad \forall i \\
    & w_i = \text{disk\_drives}_i \times x_i \quad \forall i
\end{align}

\end{document}