\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model}

Given:
\begin{itemize}
    \item \( M \): Number of machine types.
    \item \( K \): Number of products.
    \item \( I \): Number of months.
    \item \( \text{num}_m \): Number of machines for each type \( m \).
    \item \( \text{profit}_k \): Profit per unit for product \( k \).
    \item \( \text{time}_{k,m} \): Production time required for product \( k \) on machine \( m \).
    \item \( \text{down}_m \): Number of months machine \( m \) is down for maintenance.
    \item \( \text{limit}_{k,i} \): Maximum amount of product \( k \) that can be sold in month \( i \).
    \item \( \text{store\_price} \): Storage cost per unit per month.
    \item \( \text{keep\_quantity} \): Desired stock of each type of product at the end.
    \item \( \text{n\_workhours} \): Number of work hours per shift.
\end{itemize}

\textbf{Decision Variables:}
\begin{align*}
    \text{sell}_{k,i} & : \text{Quantity of product } k \text{ sold in month } i. \\
    \text{manufacture}_{k,i} & : \text{Quantity of product } k \text{ manufactured in month } i. \\
    \text{storage}_{k,i} & : \text{Quantity of product } k \text{ stored at the end of month } i. \\
    \text{maintain}_{m,i} & : \text{Number of machines of type } m \text{ under maintenance in month } i.
\end{align*}

\textbf{Objective Function:}
\[
    \max \sum_{i=1}^{I} \sum_{k=1}^{K} \left( \text{profit}_k \times \text{sell}_{k,i} - \text{store\_price} \times \text{storage}_{k,i} \right)
\]

\textbf{Constraints:}
\begin{align*}
    & \text{Balance constraint for products:} \\
    & \quad \text{storage}_{k,i} = \text{storage}_{k,i-1} + \text{manufacture}_{k,i} - \text{sell}_{k,i}, \quad \forall k, \; \forall i \\
    & \quad \text{where } \text{storage}_{k,0} = 0 \text{ (initial stock)} \\
    & \text{Sales limit:} \\
    & \quad \text{sell}_{k,i} \leq \text{limit}_{k,i}, \quad \forall k, \; \forall i \\
    & \text{Storage limit:} \\
    & \quad \text{storage}_{k,i} \leq 100, \quad \forall k, \; \forall i \\
    & \text{End stock requirement:} \\
    & \quad \text{storage}_{k,I} = \text{keep\_quantity}, \quad \forall k \\
    & \text{Machine availability constraint:} \\
    & \quad \sum_{k=1}^{K} \text{time}_{k,m} \times \text{manufacture}_{k,i} \leq \left(\text{num}_m - \text{maintain}_{m,i}\right) \times 24 \times 6 \times \text{n\_workhours}, \quad \forall m, \; \forall i \\
    & \text{Maintenance constraint:} \\
    & \quad \sum_{i=1}^{I} \text{maintain}_{m,i} = \text{down}_m, \quad \forall m
\end{align*}

All decision variables are non-negative integers.

\end{document}