\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Auto Parts Manufacturer}

\subsection*{Sets}
\begin{itemize}
    \item Let \( P \) be the number of different parts.
    \item Let \( M \) be the number of different machines.
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{time}_{m,p} \): time required on machine \( m \) to produce a batch of part \( p \) (in hours).
    \item \( \text{cost}_{m} \): cost per hour of using machine \( m \).
    \item \( \text{available}_{m} \): available hours of machine \( m \) per month.
    \item \( \text{price}_{p} \): selling price of part \( p \) per batch.
    \item \( \text{min\_batches}_{p} \): minimum number of batches of part \( p \) that must be produced.
    \item \( \text{standard\_cost} \): labor cost per hour for machine 1 during regular hours.
    \item \( \text{overtime\_cost} \): labor cost per hour for machine 1 during overtime.
    \item \( \text{overtime\_hour} \): maximum number of regular hours for machine 1.
    \item \( \text{min\_profit} \): minimum profit required.
\end{itemize}

\subsection*{Decision Variables}
Let \( \text{batches}_{p} \) be the number of batches produced for part \( p \).

\subsection*{Objective Function}
Maximize total profit:
\[
\text{Total Profit} = \sum_{p=1}^{P} (\text{price}_{p} \cdot \text{batches}_{p}) - \sum_{m=1}^{M} \left( \text{cost}_{m} \cdot \sum_{p=1}^{P} (\text{time}_{m,p} \cdot \text{batches}_{p}) \right) - \text{Labor Costs}
\]

\subsection*{Labor Costs for Machine 1}
Let \( H \) be the total hours used on machine 1:
\[
H = \sum_{p=1}^{P} (\text{time}_{1,p} \cdot \text{batches}_{p})
\]
The labor costs can be formulated as:
\[
\text{Labor Costs} =
\begin{cases}
\text{standard\_cost} \cdot H, & \text{if } H \leq \text{overtime\_hour} \\
\text{standard\_cost} \cdot \text{overtime\_hour} + \text{overtime\_cost} \cdot (H - \text{overtime\_hour}), & \text{if } H > \text{overtime\_hour}
\end{cases}
\]

\subsection*{Constraints}
1. Availability constraints for each machine \( m \):
\[
\sum_{p=1}^{P} (\text{time}_{m,p} \cdot \text{batches}_{p}) \leq \text{available}_{m}, \quad \forall m = 1, \ldots, M
\]

2. Minimum production requirements for each part \( p \):
\[
\text{batches}_{p} \geq \text{min\_batches}_{p}, \quad \forall p = 1, \ldots, P
\]

3. Profit constraint:
\[
\text{Total Profit} \geq \text{min\_profit}
\]

4. Non-negativity constraints:
\[
\text{batches}_{p} \geq 0, \quad \forall p = 1, \ldots, P
\]

\end{document}