\documentclass{article}
\usepackage{amsmath}
\begin{document}

\title{Linear Programming Model for Steel Production}
\author{}
\date{}
\maketitle

\section*{Problem Definition}

Let:
\begin{itemize}
    \item \( n \) be the required quantity of steel in tons.
    \item \( mn \) be the minimum percentage of manganese required.
    \item \( si_{\text{min}} \) and \( si_{\text{max}} \) be the minimum and maximum percentage of silicon allowed.
    \item \( K \) be the number of different types of minerals available.
    \item \( \text{contsi}_k \) be the percentage of silicon in mineral \( k \).
    \item \( \text{contmn}_k \) be the percentage of manganese in mineral \( k \).
    \item \( \text{mang\_price} \) be the price of manganese in million euros per ton.
    \item \( \text{cost}_k \) be the cost of mineral \( k \) in million euros per thousand tons.
    \item \( \text{sell\_price} \) be the selling price of steel in million euros per ton.
    \item \( \text{melt\_price} \) be the cost of melting a ton of mineral in million euros.
\end{itemize}

\section*{Decision Variables}

Let:
\begin{itemize}
    \item \( x_k \) be the amount of mineral \( k \) melted (in tons).
    \item \( y \) be the amount of manganese added (in tons).
\end{itemize}

\section*{Objective Function}

Maximize profit \( P \):

\[
P = n \cdot \text{sell\_price} - \sum_{k=1}^K \left( \frac{\text{cost}_k}{1000} \cdot x_k \right) - \text{melt\_price} \cdot \sum_{k=1}^K x_k - \text{mang\_price} \cdot y
\]

\section*{Constraints}

1. Total weight of the steel produced:
\[
\sum_{k=1}^K \left( x_k \cdot \frac{\text{contsi}_k}{100} \right) + y \geq n \cdot \frac{mn}{100}
\]

2. Silicon content constraint:
\[
si_{\text{min}} \leq \sum_{k=1}^K \left( x_k \cdot \frac{\text{contsi}_k}{100} \right) \leq si_{\text{max}}
\]

3. Manganese content constraint:
\[
\sum_{k=1}^K \left( x_k \cdot \frac{\text{contmn}_k}{100} \right) + y \geq n \cdot \frac{mn}{100}
\]

4. Non-negativity constraints:
\[
x_k \geq 0 \quad \text{for } k = 1, \ldots, K
\]
\[
y \geq 0
\]

\end{document}