\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for Intrusion Intervention in Network}

\textbf{Sets:}
\begin{itemize}
    \item \( N \): Set of clusters where \( i \in N \) represents each cluster.
\end{itemize}

\textbf{Parameters:}
\begin{itemize}
    \item \( \text{isolate\_central}_i \): Processing time for isolating cluster \( i \) centrally.
    \item \( \text{scan\_central}_i \): Processing time for scanning cluster \( i \) centrally.
    \item \( \text{isolate\_distributed}_i \): Processing time for isolating cluster \( i \) through distributed nodes.
    \item \( \text{scan\_distributed}_i \): Processing time for scanning cluster \( i \) through distributed nodes.
    \item \( \text{central\_cost} \): Cost per hour for central processing.
    \item \( \text{distributed\_cost} \): Cost per hour for distributed processing.
    \item \( \text{max\_central} \): Maximum hours available for central processing.
    \item \( \text{max\_distributed} \): Maximum hours available for distributed processing.
\end{itemize}

\textbf{Decision Variables:}
\begin{itemize}
    \item \( x_{i,j} \): Binary variable indicating if intervention type \( j \) (where \( j \in \{ \text{isolate, scan} \} \)) is applied to cluster \( i \).
    \item \( y_i \): Binary variable indicating the processing method for cluster \( i \) (where \( y_i = 1 \) for central and \( y_i = 0 \) for distributed).
\end{itemize}

\textbf{Objective Function:}
\begin{align*}
    \text{Minimize} \quad Z = \sum_{i=1}^{N} \Big(y_i \cdot \big( x_{i,\text{isolate}} \cdot \text{isolate\_central}_i + x_{i,\text{scan}} \cdot \text{scan\_central}_i \big) \cdot \text{central\_cost} + (1 - y_i) \cdot \big( x_{i,\text{isolate}} \cdot \text{isolate\_distributed}_i + x_{i,\text{scan}} \cdot \text{scan\_distributed}_i \big) \cdot \text{distributed\_cost} \Big) 
\end{align*}

\textbf{Subject to:}

\textbf{1. Intervention Type Consistency:}
\[
\sum_{j \in \{ \text{isolate}, \text{scan} \}} x_{i,j} = 1, \quad \forall i \in N
\]

\textbf{2. Central Processing Time Constraint:}
\[
\sum_{i=1}^{N} (y_i \cdot (x_{i,\text{isolate}} \cdot \text{isolate\_central}_i + x_{i,\text{scan}} \cdot \text{scan\_central}_i)) \leq \text{max\_central}
\]

\textbf{3. Distributed Processing Time Constraint:}
\[
\sum_{i=1}^{N} ((1 - y_i) \cdot (x_{i,\text{isolate}} \cdot \text{isolate\_distributed}_i + x_{i,\text{scan}} \cdot \text{scan\_distributed}_i)) \leq \text{max\_distributed}
\]

\textbf{4. Binary Constraints:}
\[
x_{i,j} \in \{0, 1\}, \quad \forall i \in N, j \in \{ \text{isolate}, \text{scan} \}
\]
\[
y_i \in \{0, 1\}, \quad \forall i \in N
\]

\textbf{Output:}
\begin{itemize}
    \item \textbf{Interventions:} A list specifying the intervention type, processing method, and amount for each cluster.
    \item \textbf{Total Cost:} The objective function value \( Z \) representing the total cost of interventions.
\end{itemize}

\end{document}