\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Oil Blending Problem}

\subsection*{Parameters:}
\begin{itemize}
    \item $I$: Number of different oils.
    \item $M$: Number of months.
    \item $price_{i,m}$: Purchase price of oil $i$ in month $m$.
    \item $sell\_price$: Selling price of the final product per ton.
    \item $max\_veg$: Maximum refining capacity for vegetable oils per month.
    \item $max\_non\_veg$: Maximum refining capacity for non-vegetable oils per month.
    \item $storage\_size$: Maximum storage capacity for each oil.
    \item $storage\_cost$: Storage cost per ton per month.
    \item $max\_hardness$: Maximum hardness constraint for the final product.
    \item $min\_hardness$: Minimum hardness constraint for the final product.
    \item $hardness_{i}$: Hardness of oil $i$.
    \item $init\_amount$: Initial storage amount of each oil.
    \item $is\_vegetable_{i}$: Indicator if oil $i$ is a vegetable oil ($1$ if vegetable, $0$ otherwise).
\end{itemize}

\subsection*{Decision Variables:}
\begin{itemize}
    \item $buyquantity_{i,m}$: Amount of oil $i$ purchased in month $m$.
    \item $refine_{i,m}$: Amount of oil $i$ refined in month $m$.
    \item $storage_{i,m}$: Amount of oil $i$ stored at the end of month $m$.
\end{itemize}

\subsection*{Objective Function:}
Maximize profit:
\[
\text{Maximize } \sum_{m=1}^{M} \left( sell\_price \times \sum_{i=1}^{I} refine_{i,m} - \sum_{i=1}^{I} (price_{i,m} \times buyquantity_{i,m} + storage\_cost \times storage_{i,m}) \right)
\]

\subsection*{Constraints:}
\begin{itemize}
    \item Storage balance:
    \[
    storage_{i,m} = storage_{i,m-1} + buyquantity_{i,m} - refine_{i,m}, \quad \forall i, \forall m
    \]
    \item Initial storage:
    \[
    storage_{i,0} = init\_amount, \quad \forall i
    \]
    \item End storage equal to initial amount:
    \[
    storage_{i,M} = init\_amount, \quad \forall i
    \]
    \item Storage capacity:
    \[
    storage_{i,m} \leq storage\_size, \quad \forall i, \forall m
    \]
    \item Vegetable oil refining capacity:
    \[
    \sum_{i=1}^{I} is\_vegetable_{i} \times refine_{i,m} \leq max\_veg, \quad \forall m
    \]
    \item Non-vegetable oil refining capacity:
    \[
    \sum_{i=1}^{I} (1 - is\_vegetable_{i}) \times refine_{i,m} \leq max\_non\_veg, \quad \forall m
    \]
    \item Hardness constraints:
    \[
    min\_hardness \leq \frac{\sum_{i=1}^{I} hardness_{i} \times refine_{i,m}}{\sum_{i=1}^{I} refine_{i,m}} \leq max\_hardness, \quad \forall m
    \]
    \item Non-negativity:
    \[
    buyquantity_{i,m}, refine_{i,m}, storage_{i,m} \geq 0, \quad \forall i, \forall m
    \]
\end{itemize}

\end{document}