\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for Digital Equipment Corporation (DEC) Production Optimization}

\subsection*{Sets}
\begin{itemize}
    \item Let \( N \) be the number of different computer systems.
    \item Let \( i \) denote each system, where \( i = 1, 2, \ldots, N \).
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{is\_workstation}_i \): Boolean, true if system \( i \) is a workstation.
    \item \( \text{price}_i \): Price of system \( i \).
    \item \( \text{disk\_drives}_i \): Average number of disk drives requested for system \( i \).
    \item \( \text{mem}_i \): Average number of 256K memory boards used for system \( i \).
    \item \( \text{max\_cpu} \): Maximum number of CPUs available.
    \item \( \text{min\_disk} \), \( \text{max\_disk} \): Minimum and maximum supply of disk drives.
    \item \( \text{min\_mem} \), \( \text{max\_mem} \): Minimum and maximum supply of 256K memory boards.
    \item \( \text{demand}_i \): Maximum demand for system \( i \).
    \item \( \text{demand\_GP} \): Maximum demand for the whole GP family.
    \item \( \text{demand\_WS} \): Maximum demand for the whole WS family.
    \item \( \text{preorder}_i \): Preorders for system \( i \).
    \item \( \text{alt\_mem} \): Units of alternative memory boards available.
    \item \( \text{alt\_compatible}_i \): Boolean, true if system \( i \) can use alternative memory boards.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item Let \( x_i \): Number of systems produced of type \( i \) (continuous variable).
    \item Let \( alt\_used_i \): Number of alternative memory boards used for system \( i \) (integer variable, if any).
    \end{itemize}

\subsection*{Objective Function}
Maximize the profit:
\[
\text{Profit} = \sum_{i=1}^{N} (\text{price}_i \cdot x_i) - \text{costs}
\]

\subsection*{Constraints}

1. **CPU Constraints**:
\[
\sum_{i=1}^{N} x_i \leq \text{max\_cpu}
\]

2. **Disk Drive Constraints**:
\[
\sum_{i=1}^{N} (\text{disk\_drives}_i \cdot x_i) \geq \text{min\_disk}
\]
\[
\sum_{i=1}^{N} (\text{disk\_drives}_i \cdot x_i) \leq \text{max\_disk}
\]

3. **256K Memory Board Constraints**:
\[
\sum_{i=1}^{N} (\text{mem}_i \cdot x_i) + \sum_{i=1}^{N} (alt\_used_i \cdot \text{alt\_compatible}_i) \geq \text{min\_mem}
\]
\[
\sum_{i=1}^{N} (\text{mem}_i \cdot x_i) + \sum_{i=1}^{N} (alt\_used_i \cdot \text{alt\_compatible}_i) \leq \text{max\_mem}
\]

4. **Demand Constraints**:
\[
x_i \geq \text{preorder}_i \quad \forall i
\]
\[
\sum_{i \in \text{GP}} x_i \leq \text{demand\_GP}
\]
\[
\sum_{i \in \text{WS}} x_i \leq \text{demand\_WS}
\]

5. **Alternative Memory Board Usage**:
\[
alt\_used_i \leq \text{alt\_mem} \cdot \text{alt\_compatible}_i
\]

\subsection*{Output Format}
\begin{itemize}
    \item \textit{"system\_output"}: A list with details of each system produced:
    \[
    \text{system\_output} = \{ 
        \text{num\_produced} = x_i, \, 
        \text{total\_256K\_boards\_used} = \text{mem}_i \cdot x_i, \,
        \text{total\_alt\_boards\_used} = alt\_used_i, \,
        \text{total\_disk\_drives\_used} = \text{disk\_drives}_i \cdot x_i 
    \}
    \]
    \item \textit{"profit"}: Total profit for the next quarter.
\end{itemize}

\end{document}