\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Steel Production}

\subsection*{Parameters}
\begin{itemize}
    \item \( n_{\text{steel\_quant}} \): Total amount of steel to produce (in tons).
    \item \( mn_{\text{percent}} \): Minimum percentage of manganese (Mn).
    \item \( si_{\text{min}} \): Minimum percentage of silicon (Si).
    \item \( si_{\text{max}} \): Maximum percentage of silicon (Si).
    \item \( contsi_k \): Percentage of silicon in mineral \( k \).
    \item \( contmn_k \): Percentage of manganese in mineral \( k \).
    \item \( mang_{\text{price}} \): Price of manganese per ton (in million euros).
    \item \( cost_k \): Cost of mineral \( k \) per thousand tons (in million euros).
    \item \( sell_{\text{price}} \): Selling price of steel per ton (in million euros).
    \item \( melt_{\text{price}} \): Cost of smelting per ton of mineral (in million euros).
\end{itemize}

\subsection*{Variables}
\begin{itemize}
    \item \( amount_k \): Amount of mineral \( k \) to be melted.
    \item \( num_{\text{mang}} \): Amount of manganese to be directly added.
\end{itemize}

\subsection*{Objective Function}
Maximize profit:
\[
Z = sell_{\text{price}} \cdot n_{\text{steel\_quant}} - \sum_{k=1}^{K} (cost_k \cdot \frac{amount_k}{1000} + melt_{\text{price}} \cdot amount_k) - mang_{\text{price}} \cdot num_{\text{mang}}
\]

\subsection*{Constraints}

\begin{align}
\text{1. Total Steel Requirement:} & \quad \sum_{k=1}^{K} amount_k + num_{\text{mang}} = n_{\text{steel\_quant}} \\
\text{2. Manganese Content:} & \quad \frac{\sum_{k=1}^{K} contmn_k \cdot amount_k + num_{\text{mang}}}{n_{\text{steel\_quant}}} \geq \frac{mn_{\text{percent}}}{100} \\
\text{3. Silicon Content (Min):} & \quad \frac{\sum_{k=1}^{K} contsi_k \cdot amount_k}{n_{\text{steel\_quant}}} \geq \frac{si_{\text{min}}}{100} \\
\text{4. Silicon Content (Max):} & \quad \frac{\sum_{k=1}^{K} contsi_k \cdot amount_k}{n_{\text{steel\_quant}}} \leq \frac{si_{\text{max}}}{100} \\
\text{5. Non-negativity Constraints:} & \quad amount_k \geq 0, \quad num_{\text{mang}} \geq 0, \quad \forall k
\end{align}

\end{document}