\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for DEC's Computer Systems Production}

\subsection*{Variables}
Let \( x_i \) be the number of systems of type \( i \) produced, where \( i = 1, 2, \ldots, N \).

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{is\_workstation}_i \) : boolean indicating if system \( i \) is a workstation.
    \item \( \text{price}_i \) : price of system \( i \).
    \item \( \text{disk\_drives}_i \) : average number of disk drives requested for system \( i \).
    \item \( \text{256K\_boards}_i \) : average memory boards required for system \( i \).
    \item \( \text{max\_cpu} \) : maximum number of CPUs available.
    \item \( \text{min\_disk} \) : minimum number of disk drives available.
    \item \( \text{max\_disk} \) : maximum number of disk drives available.
    \item \( \text{min\_mem} \) : minimum number of 256K memory boards available.
    \item \( \text{max\_mem} \) : maximum number of 256K memory boards available.
    \item \( \text{demand}_i \) : maximum demand for system \( i \).
    \item \( \text{demand\_GP} \) : maximum demand for general-purpose systems.
    \item \( \text{demand\_WS} \) : maximum demand for workstation systems.
    \item \( \text{preorder}_i \) : preorders for system \( i \).
    \item \( \text{alt\_mem} \) : available alternative memory boards.
    \item \( \text{alt\_compatible}_i \) : boolean for compatibility with alternative memory boards for system \( i \).
\end{itemize}

\subsection*{Objective Function}
Maximize the profit:

\[
\text{Profit} = \sum_{i=1}^{N} \left( \text{price}_i \cdot x_i - \text{costs}(x_i) \right)
\]

Where \(\text{costs}(x_i)\) accounts for memory and disk drive costs.

\subsection*{Constraints}
1. CPU constraint:
\[
\sum_{i=1}^{N} x_i \leq \text{max\_cpu}
\]

2. Disk drive constraint:
\[
\sum_{i=1}^{N} \text{disk\_drives}_i \cdot x_i \geq \text{min\_disk}
\]
\[
\sum_{i=1}^{N} \text{disk\_drives}_i \cdot x_i \leq \text{max\_disk}
\]

3. Memory board constraint:
\[
\sum_{i=1}^{N} \text{256K\_boards}_i \cdot x_i \geq \text{min\_mem}
\]
\[
\sum_{i=1}^{N} \text{256K\_boards}_i \cdot x_i + \sum_{i=1}^{N} \text{alt\_compatible}_i \cdot x_i \leq \text{max\_mem} + \text{alt\_mem}
\]

4. Demand constraints:
\[
\sum_{i \,:\, \text{is\_workstation}_i} x_i \leq \text{demand\_WS}
\]
\[
\sum_{i \,:\, \neg \text{is\_workstation}_i} x_i \leq \text{demand\_GP}
\]

5. Preorder constraints:
\[
x_i \geq \text{preorder}_i, \quad \forall i \in \{1, 2, \ldots, N\}
\]

6. Demand limits:
\[
x_i \leq \text{demand}_i, \quad \forall i
\]

\subsection*{Output Format}
The output should be formatted as follows:
\begin{verbatim}
{
    "system_output": [
        {
            "num_produced": x_i,
            "total_256K_boards_used": \text{boards_used}_i,
            "total_alt_boards_used": \text{alt_boards_used}_i,
            "total_disk_drives_used": \text{disk_used}_i
        } 
        \text{ for } i = 1, \ldots, N
    ],
    "profit": \text{total_profit}
}
\end{verbatim}

\end{document}