\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{MILP Model for Engineering Factory Operations}

\textbf{Parameters:}
\begin{itemize}
    \item Let \( M \) be the number of machines.
    \item Let \( K \) be the number of products.
    \item Let \( I \) be the number of months.
    \item \( \text{profit}_k \): Profit per unit of product \( k \).
    \item \( \text{time}_{k,m} \): Production time required for product \( k \) on machine \( m \).
    \item \( \text{down}_m \): Number of months machine \( m \) is under maintenance.
    \item \( \text{limit}_{k,i} \): Sales limit for product \( k \) in month \( i \).
    \item \( \text{store\_price} \): Storage cost per unit per month.
    \item \( \text{keep\_quantity} \): Desired stock of each product at the end of the planning period.
    \item \( n_{\text{workhours}} \): Number of work hours available per day.
\end{itemize}

\textbf{Decision Variables:}
\begin{itemize}
    \item \( \text{sell}_{k,i} \): Quantity of product \( k \) sold in month \( i \).
    \item \( \text{manufacture}_{k,i} \): Quantity of product \( k \) manufactured in month \( i \).
    \item \( \text{storage}_{k,i} \): Quantity of product \( k \) stored at the end of month \( i \).
    \item \( \text{maintain}_{m,i} \): Binary variable indicating whether machine \( m \) is under maintenance in month \( i \) (1 if under maintenance, 0 otherwise).
\end{itemize}

\textbf{Objective Function:}
\[
\text{Maximize } Z = \sum_{i=1}^{I} \sum_{k=1}^{K} \left( \text{profit}_k \cdot \text{sell}_{k,i} - \text{store\_price} \cdot \text{storage}_{k,i} \right)
\]

\textbf{Subject to:}

\begin{align*}
\sum_{k=1}^{K} \text{manufacture}_{k,i} \cdot \text{time}_{k,m} & \leq n_{\text{workhours}} \cdot 12 \cdot (24 - \text{down}_m) \quad \forall m \in \{1, \ldots, M\}, i \in \{1, \ldots, I\} \\
\text{sell}_{k,i} & \leq \text{limit}_{k,i} \quad \forall k \in \{1, \ldots, K\}, i \in \{1, \ldots, I\} \\
\text{storage}_{k,i} & = \text{storage}_{k,i-1} + \text{manufacture}_{k,i} - \text{sell}_{k,i} \quad \forall k \in \{1, \ldots, K\}, i \in \{2, \ldots, I\} \\
\text{storage}_{k,1} & = 0 \quad \forall k \in \{1, \ldots, K\} \\
\text{storage}_{k,I} & \geq \text{keep\_quantity} \quad \forall k \in \{1, \ldots, K\} \\
\sum_{i=1}^{I} \text{maintain}_{m,i} & \leq \text{down}_m \quad \forall m \in \{1, \ldots, M\} \\
\text{manufacture}_{k,i}, \text{sell}_{k,i}, \text{storage}_{k,i} & \geq 0 \quad \forall k \in \{1, \ldots, K\}, i \in \{1, \ldots, I\} \\
\text{maintain}_{m,i} & \in \{0, 1\} \quad \forall m \in \{1, \ldots, M\}, i \in \{1, \ldots, I\}
\end{align*}

\end{document}