\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Custom Tees Advertising Campaign}

\subsection*{Parameters}
\begin{itemize}
    \item Let \( A \) be the number of different ad types.
    \item Let \( \text{goal\_young} \) be the goal of clicks from visitors aged 18-25 (in thousands).
    \item Let \( \text{goal\_old} \) be the goal of clicks from visitors older than 25 (in thousands).
    \item Let \( \text{goal\_unique\_young} \) be the goal of unique clicks from visitors aged 18-25 (in thousands).
    \item Let \( \text{goal\_unique\_old} \) be the goal of unique clicks from visitors older than 25 (in thousands).
    \item Let \( \text{young\_clicks}_a \) be the estimated percentage of clicks from the 18-25 age range for ad type \( a \).
    \item Let \( \text{old\_clicks}_a \) be the estimated percentage of clicks from older visitors for ad type \( a \).
    \item Let \( \text{cost}_a \) be the cost per 1000 clicks for ad type \( a \).
    \item Let \( \text{max\_clicks}_a \) be the maximum allowable clicks for ad type \( a \) (in thousands).
    \item Let \( \text{unique\_clicks}_a \) be the estimated percentage of unique visitors for each ad type \( a \).
\end{itemize}

\subsection*{Decision Variables}
Let \( x_a \) be the number of clicks purchased for ad type \( a \) (in thousands).

\subsection*{Objective Function}
Minimize the total cost:
\[
\text{Minimize } z = \sum_{a=1}^{A} \text{cost}_a \cdot x_a
\]

\subsection*{Constraints}
\begin{align*}
\sum_{a=1}^{A} \text{young\_clicks}_a \cdot x_a & \geq \text{goal\_young} \quad \text{(Total clicks from age 18-25)} \\
\sum_{a=1}^{A} \text{old\_clicks}_a \cdot x_a & \geq \text{goal\_old} \quad \text{(Total clicks from age > 25)} \\
\sum_{a=1}^{A} \text{unique\_clicks}_a \cdot x_a & \geq \text{goal\_unique\_young} \quad \text{(Unique clicks from age 18-25)} \\
\sum_{a=1}^{A} \text{unique\_clicks}_a \cdot x_a & \geq \text{goal\_unique\_old} \quad \text{(Unique clicks from age > 25)} \\
x_a & \leq \text{max\_clicks}_a \quad \forall a \in \{1, \ldots, A\} \quad \text{(Maximum allowable clicks)} \\
x_a & \geq 0 \quad \forall a \in \{1, \ldots, A\} \quad \text{(Non-negativity constraint)}
\end{align*}

\subsection*{Output}
The solution will provide:
\begin{itemize}
    \item \( x_a \): the number of clicks purchased for each ad type (in thousands).
    \item \( z \): the total cost of the ad campaign.
\end{itemize}

\end{document}