\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Auto Parts Manufacturer}

\subsection*{Parameters}
\begin{itemize}
    \item Let \( P \) be the number of different parts.
    \item Let \( M \) be the number of different machines.
    \item Let \( \text{time}_{m,p} \) be the time required on machine \( m \) to produce a batch of part \( p \) (in hours).
    \item Let \( \text{cost}_{m} \) be the cost per hour for using machine \( m \).
    \item Let \( \text{available}_{m} \) be the available hours per month for machine \( m \).
    \item Let \( \text{price}_{p} \) be the price per batch of part \( p \).
    \item Let \( \text{min\_batches}_{p} \) be the minimum number of batches of part \( p \) required.
    \item Let \( \text{standard\_cost} \) be the labor cost per hour up to certain overtime hours.
    \item Let \( \text{overtime\_cost} \) be the labor cost per hour after overtime hours.
    \item Let \( \text{overtime\_hour} \) be the maximum hours before an overtime rate applies.
    \item Let \( \text{min\_profit} \) be the minimum desired profit.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item Let \( \text{batches}_{p} \) be the number of batches produced for part \( p \).
\end{itemize}

\subsection*{Objective Function}
Maximize total profit:
\[
\text{total\_profit} = \sum_{p=1}^{P} \left( \text{price}_{p} \cdot \text{batches}_{p} \right) - \sum_{m=1}^{M} \left( \text{cost}_{m} \cdot \sum_{p=1}^{P} \left( \text{time}_{m,p} \cdot \text{batches}_{p} \right) \right) - \text{labor\_cost}
\]
Where labor cost can be calculated based on the hours worked on Machine 1:
\[
\text{labor\_cost} = \begin{cases}
\text{standard\_cost} \cdot h & \text{if } h \leq \text{overtime\_hour} \\
\text{standard\_cost} \cdot \text{overtime\_hour} + \text{overtime\_cost} \cdot (h - \text{overtime\_hour}) & \text{if } h > \text{overtime\_hour}
\end{cases}
\]
where \( h = \sum_{p=1}^{P} \text{time}_{1,p} \cdot \text{batches}_{p} \).

\subsection*{Constraints}
1. Batch production constraints:
   \[
   \text{batches}_{p} \geq \text{min\_batches}_{p}, \quad \forall p = 1, \ldots, P
   \]
   
2. Machine availability constraints:
   \[
   \sum_{p=1}^{P} \text{time}_{m,p} \cdot \text{batches}_{p} \leq \text{available}_{m}, \quad \forall m = 1, \ldots, M
   \]
   
3. Profit constraint:
   \[
   \text{total\_profit} \geq \text{min\_profit}
   \]

\subsection*{Non-negativity Constraints}
\[
\text{batches}_{p} \geq 0, \quad \forall p = 1, \ldots, P
\]

\end{document}