\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for Power Generation Optimization}

\subsection*{Parameters}
\begin{itemize}
    \item Let \( T \) be the number of periods in a day.
    \item Let \( K \) be the number of types of generating units.
    \item \( demand_t \): Demand in period \( t \) for \( t = 1, \ldots, T \).
    \item \( num_k \): Number of generators of type \( k \) for \( k = 1, \ldots, K \).
    \item \( minlevel_k \): Minimum operational level of type \( k \) generator.
    \item \( maxlevel_k \): Maximum operational level of type \( k \) generator.
    \item \( runcost_k \): Hourly cost of running type \( k \) generator at minimum level.
    \item \( extracost_k \): Extra hourly cost per megawatt for type \( k \) generator above the minimum level.
    \item \( startcost_k \): Startup cost for type \( k \) generator.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( numon_{k,t} \): Number of generators of type \( k \) that are on in period \( t \).
    \item \( level_{k,t} \): Level of generation for type \( k \) in period \( t \).
    \item \( startup_{k,t} \): Binary variable indicating whether type \( k \) generator is started in period \( t \) (1 if started, 0 otherwise).
\end{itemize}

\subsection*{Objective Function}
Minimize the total cost:
\[
\text{Minimize } Z = \sum_{t=1}^{T} \sum_{k=1}^{K} \left( runcost_k \cdot numon_{k,t} + startcost_k \cdot startup_{k,t} + extracost_k \cdot (level_{k,t} - minlevel_k) \cdot numon_{k,t} \right)
\]

\subsection*{Constraints}

1. **Demand Satisfaction**:
\[
\sum_{k=1}^{K} level_{k,t} \geq demand_t, \quad \forall t = 1, \ldots, T
\]

2. **Operational Levels**:
\[
minlevel_k \cdot numon_{k,t} \leq level_{k,t} \leq maxlevel_k \cdot numon_{k,t}, \quad \forall k = 1, \ldots, K, \quad \forall t = 1, \ldots, T
\]

3. **Number of Generators On**:
\[
numon_{k,t} \leq num_k, \quad \forall k = 1, \ldots, K, \quad \forall t = 1, \ldots, T
\]

4. **Level and Startup Relation**:
\[
level_{k,t} \leq maxlevel_k \cdot startup_{k,t}, \quad \forall k = 1, \ldots, K, \quad \forall t = 1, \ldots, T
\]

5. **Binary Variables**:
\[
startup_{k,t} \in \{0, 1\}, \quad \forall k = 1, \ldots, K, \quad \forall t = 1, \ldots, T
\]

\end{document}