\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{MIP Formulation for DEC's Production Problem}

\subsection*{Parameters:}

\begin{itemize}
    \item $N$: Number of computer systems.
    \item $price_i$: Price of system $i$.
    \item $disk_i$: Average disk drives requested for system $i$.
    \item $mem_i$: Average 256K memory boards used for system $i$.
    \item $max\_cpu$: Maximum units of CPUs available.
    \item $min\_disk$, $max\_disk$: Supply range of disk drives.
    \item $min\_mem$, $max\_mem$: Supply range of 256K memory boards.
    \item $demand_i$: Maximum demand for system $i$.
    \item $demand\_GP$: Maximum demand for GP family.
    \item $demand\_WS$: Maximum demand for WS family.
    \item $preorder_i$: Pre-orders for system $i$.
    \item $alt\_mem$: Units of alternative memory boards available.
    \item $is\_workstation_i$: Boolean indicating if system $i$ is a workstation.
    \item $alt\_compatible_i$: Boolean indicating if system $i$ can use alternative memory.
\end{itemize}

\subsection*{Decision Variables:}

\begin{itemize}
    \item $x_i$: Number of system $i$ produced (continuous).
    \item $y_{alt,i}$: Alternative memory boards used in system $i$.
    \item $y_{256K,i}$: 256K memory boards used in system $i$.
    \item $d_{disk,i}$: Disk drives used in system $i$.
\end{itemize}

\subsection*{Objective Function:}

Maximize the profit,

\[
\text{Maximize} \quad Z = \sum_{i=1}^{N} price_i \times x_i
\]

\subsection*{Constraints:}

1. CPU constraint:

\[
\sum_{i=1}^{N} x_i \leq max\_cpu
\]

2. Disk drive supply constraints:

\[
\sum_{i=1}^{N} d_{disk,i} \geq min\_disk
\]
\[
\sum_{i=1}^{N} d_{disk,i} \leq max\_disk
\]

3. Memory board supply constraints:

\[
\sum_{i=1}^{N} y_{256K,i} \geq min\_mem
\]
\[
\sum_{i=1}^{N} y_{256K,i} \leq max\_mem
\]

4. Demand fulfillment for each system:

\[
x_i \leq demand_i \quad \forall i
\]

5. Pre-order fulfillment:

\[
x_i \geq preorder_i \quad \forall i
\]

6. Demand for GP and WS families:

\[
\sum_{\substack{i=1 \\ \text{is\_workstation}_i = \text{false}}}^{N} x_i \leq demand\_GP
\]
\[
\sum_{\substack{i=1 \\ \text{is\_workstation}_i = \text{true}}}^{N} x_i \leq demand\_WS
\]

7. Memory boards usage:

\[
y_{256K,i} = mem_i \times x_i \quad \forall i
\]

8. Alternative memory boards usage:

\[
y_{alt,i} \leq alt\_compatible_i \times alt\_mem \quad \forall i
\]
\[
\sum_{i=1}^{N} y_{alt,i} \leq alt\_mem
\]

9. Disk drive usage:

\[
d_{disk,i} = disk_i \times x_i \quad \forall i
\]

\subsection*{Solution:}

The solution will include the number of each system produced, the total memory boards used, and the total disk drives used, along with the maximized profit.

\end{document}