\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model}

\subsection*{Sets and Indices}
\begin{itemize}
    \item \( i \in \{1, \ldots, N\} \): Index for computer systems.
    \item \( \text{GP}, \text{WS} \): Sets for general-purpose and workstation systems respectively.
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{price}_i \): Price of system \( i \).
    \item \( \text{disk}_i \): Average units of disk drive requested for system \( i \).
    \item \( \text{mem}_i \): Average units of 256K memory boards used by system \( i \).
    \item \( \text{max\_cpu} \): Maximum units of CPUs available.
    \item \( \text{min\_disk}, \text{max\_disk} \): Range of available disk drives.
    \item \( \text{min\_mem}, \text{max\_mem} \): Range of available 256K memory boards.
    \item \( \text{demand}_i \): Maximum demand for system \( i \).
    \item \( \text{demand\_GP}, \text{demand\_WS} \): Maximum demand for GP and WS systems.
    \item \( \text{preorder}_i \): Preorders for system \( i \) to be fulfilled.
    \item \( \text{alt\_mem} \): Units of alternative memory boards available.
    \item \( \text{alt\_compatible}_i \): Boolean indicating if system \( i \) can use alternative memory.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( x_i \): Number of systems \( i \) to produce (continuous).
    \item \( \text{mem\_used}_i \): Total 256K memory boards used by system \( i \).
    \item \( \text{alt\_used}_i \): Total alternative boards used by system \( i \) (if compatible).
    \item \( \text{disk\_used}_i \): Total disk drives used by system \( i \).
\end{itemize}

\subsection*{Objective Function}
Maximize the total profit:
\[
\text{Profit} = \sum_{i=1}^{N} \text{price}_i \times x_i
\]

\subsection*{Constraints}
\begin{align}
    & \sum_{i=1}^{N} x_i \leq \text{max\_cpu} & \text{(CPU availability)} \\
    & \sum_{i=1}^{N} \text{disk}_i \times x_i \leq \text{max\_disk} & \text{(Disk drive upper limit)} \\
    & \sum_{i=1}^{N} \text{disk}_i \times x_i \geq \text{min\_disk} & \text{(Disk drive lower limit)} \\
    & \sum_{i=1}^{N} \text{mem\_used}_i \leq \text{max\_mem} & \text{(256K memory board upper limit)} \\
    & \sum_{i=1}^{N} \text{mem\_used}_i \geq \text{min\_mem} & \text{(256K memory board lower limit)} \\
    & \sum_{i \in \text{GP}} x_i \leq \text{demand\_GP} & \text{(GP systems demand)} \\
    & \sum_{i \in \text{WS}} x_i \leq \text{demand\_WS} & \text{(WS systems demand)} \\
    & x_i \leq \text{demand}_i & \forall i \text{ (Demand for system \( i \))} \\
    & x_i \geq \text{preorder}_i & \forall i \text{ (Preorders)}

\end{align}

For alternative memory usage:
\begin{align}
    & \text{alt\_used}_i = 0, & \text{if }\text{alt\_compatible}_i = \text{false} \\
    & \sum_{i=1}^{N} \text{alt\_used}_i \leq \text{alt\_mem} & \text{(Alternative memory limit)}
\end{align}

\end{document}