\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for Auto Parts Manufacturer}

\subsection*{Sets}
\begin{itemize}
    \item Let \( P \) be the number of different parts.
    \item Let \( M \) be the number of different machines.
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( time_{m,p} \): time required (in hours) on machine \( m \) to produce a batch of part \( p \).
    \item \( cost_{m} \): cost (in currency units) per hour for using machine \( m \).
    \item \( available_{m} \): availability (in hours) of machine \( m \) per month.
    \item \( price_{p} \): selling price (in currency units) of part \( p \) per batch.
    \item \( setup\_time_{p} \): setup time (in hours) required for machine 1 before producing part \( p \).
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( batches_{p} \): number of batches of part \( p \) produced (for \( p = 1, \ldots, P \)).
    \item \( setup\_flag_{p} \): binary variable indicating whether part \( p \) is set up (\( setup\_flag_{p} = 1 \)) or not (\( setup\_flag_{p} = 0 \)).
\end{itemize}

\subsection*{Objective Function}
Maximize total profit:
\[
\text{Total Profit} = \sum_{p=1}^{P} (price_{p} \cdot batches_{p}) - \sum_{m=1}^{M} (cost_{m} \cdot \text{hours\_used}_{m})
\]
where 
\[
\text{hours\_used}_{m} = \sum_{p=1}^{P} (time_{m,p} \cdot batches_{p}) + \sum_{p=1}^{P} (setup\_time_{p} \cdot setup\_flag_{p}) \text{ for } m = 1
\]
and 
\[
\text{hours\_used}_{m} = \sum_{p=1}^{P} (time_{m,p} \cdot batches_{p}) \text{ for } m \neq 1
\]

\subsection*{Constraints}
1. Machine availability constraints:
\[
\sum_{p=1}^{P} (time_{m,p} \cdot batches_{p}) + \sum_{p=1}^{P} (setup\_time_{p} \cdot setup\_flag_{p}) \leq available_{m} \quad \forall m \in \{1, 2, \ldots, M\}
\]

2. Non-negativity constraints:
\[
batches_{p} \geq 0 \quad \forall p \in \{1, 2, \ldots, P\}
\]

3. Binary setup flag constraints:
\[
setup\_flag_{p} \in \{0, 1\} \quad \forall p \in \{1, 2, \ldots, P\}
\]

\subsection*{Output}
The output will include:
\begin{itemize}
    \item \( batches_{p} \): the number of batches of each part produced.
    \item \( setup\_flag_{p} \): indicates whether part \( p \) is set up.
    \item \( total\_profit \): representing the total profit obtained for the month.
\end{itemize}

\end{document}