\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for Seaport Container Unloading and Loading}

\subsection*{Parameters:}

\begin{itemize}
    \item $T$: Total number of months.
    \item $\text{demand}_t$: Demand for containers by ships in month $t$.
    \item $\text{unload\_cost}_t$: Cost to unload a single container in month $t$.
    \item $\text{unload\_capacity}_t$: Maximum number of containers that can be unloaded in month $t$.
    \item $\text{holding\_cost}$: Cost for holding one container for a month.
    \item $\text{max\_container}$: Maximum storage capacity of the yard.
    \item $\text{init\_container}$: Initial number of containers in the yard.
    \item $\text{num\_cranes}$: Maximum number of cranes that can be rented each month.
    \item $\text{crane\_capacity}$: Number of containers a single crane can load each month.
    \item $\text{crane\_cost}$: Cost to rent one crane.
\end{itemize}

\subsection*{Decision Variables:}

\begin{itemize}
    \item $x_t$: Number of containers unloaded in month $t$.
    \item $y_t$: Number of cranes rented in month $t$.
    \item $z_t$: Number of containers stored in the yard at the end of month $t$.
\end{itemize}

\subsection*{Objective Function:}

Minimize the total cost, which includes cost for unloading, holding, and renting cranes:

\[
\text{Minimize} \quad \sum_{t=1}^{T} \left( \text{unload\_cost}_t \cdot x_t + \text{holding\_cost} \cdot z_t + \text{crane\_cost} \cdot y_t \right)
\]

\subsection*{Constraints:}

\begin{itemize}
    \item \textbf{Demand Fulfillment:}
    \[
    \text{demand}_t = x_t + z_{t-1} - z_t \quad \text{for } t = 1, \ldots, T
    \]
    Ensure containers loaded meet demand and adjust inventory.

    \item \textbf{Unloading Capacity:}
    \[
    0 \leq x_t \leq \text{unload\_capacity}_t \quad \text{for } t = 1, \ldots, T
    \]

    \item \textbf{Storage Capacity:}
    \[
    0 \leq z_t \leq \text{max\_container} \quad \text{for } t = 1, \ldots, T
    \]

    \item \textbf{Initial Condition:}
    \[
    z_0 = \text{init\_container}
    \]

    \item \textbf{End Condition:}
    \[
    z_T = 0
    \]

    \item \textbf{Crane Usage:}
    \[
    \text{demand}_t \leq y_t \cdot \text{crane\_capacity} \quad \text{for } t = 1, \ldots, T
    \]
    \[
    0 \leq y_t \leq \text{num\_cranes} \quad \text{for } t = 1, \ldots, T
    \]

    \item \textbf{Non-negativity:}
    \[
    x_t, y_t, z_t \geq 0 \quad \text{and integers for } t = 1, \ldots, T
    \]
\end{itemize}

\end{document}