\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Manufacturing Optimization}

\subsection*{Parameters}
\begin{itemize}
    \item Let \( M \) be the total number of machines, \( K \) be the total number of products, and \( I \) be the total number of months.
    \item \( num_m \): Total number of machines.
    \item \( profit_k \): Profit gained from selling product \( k \).
    \item \( time_{k,m} \): Time required to produce product \( k \) on machine \( m \).
    \item \( maintain_{i,m} \): Number of machines down for maintenance in month \( i \).
    \item \( limit_{k,i} \): Marketing limitation on product \( k \) in month \( i \).
    \item \( store\_price \): Cost of storing one unit of product per month.
    \item \( keep\_quantity \): Desired quantity to keep in stock at the end of month \( i \).
    \item \( n\_workhours \): Number of working hours per day.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( sell_{k,i} \): Quantity of product \( k \) sold in month \( i \).
    \item \( manufacture_{k,i} \): Quantity of product \( k \) manufactured in month \( i \).
    \item \( storage_{k,i} \): Quantity of product \( k \) stored at the end of month \( i \).
\end{itemize}

\subsection*{Objective Function}
Maximize the total profit:
\[
\text{Maximize } Z = \sum_{i=1}^{I} \sum_{k=1}^{K} (profit_k \cdot sell_{k,i}) - \sum_{i=1}^{I} \sum_{k=1}^{K} (store\_price \cdot storage_{k,i})
\]

\subsection*{Constraints}
1. **Production Time Constraint**: The total production time must not exceed available machine hours.
\[
\sum_{k=1}^{K} \sum_{m=1}^{M} (time_{k,m} \cdot manufacture_{k,i}) \leq (n\_workhours \cdot (6 \cdot 24 - \sum_{m=1}^{M} maintain_{i,m})) \quad \forall i
\]

2. **Marketing Limits**: The quantity sold must not exceed market limitations.
\[
sell_{k,i} \leq limit_{k,i} \quad \forall k, \, \forall i
\]

3. **Storage Calculation**: The storage must account for production, sales, and desired ending inventory.
\[
storage_{k,i} = storage_{k,i-1} + manufacture_{k,i} - sell_{k,i} \quad \forall k, \, \forall i
\]

4. **Non-negativity Constraints**: All decision variables must be non-negative.
\[
sell_{k,i} \geq 0, \quad manufacture_{k,i} \geq 0, \quad storage_{k,i} \geq 0 \quad \forall k, \, \forall i
\]

5. **Ending Inventory Requirement**: At the end of each month, maintain required stock levels.
\[
storage_{k,I} \geq keep\_quantity \quad \forall k
\]

\end{document}