\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for Intrusion Intervention}

\subsection*{Sets}
\begin{itemize}
    \item Let \( N \) be the number of clusters.
    \item Let \( C \) be the set of intervention types, where \( C = \{ \text{isolate, scan} \} \).
    \item Let \( M \) be the set of processing methods, where \( M = \{ \text{central, distributed} \} \).
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{isolate\_central}_i \): Processing time for isolation in cluster \( i \) using central method.
    \item \( \text{scan\_central}_i \): Processing time for scanning in cluster \( i \) using central method.
    \item \( \text{isolate\_distributed}_i \): Processing time for isolation in cluster \( i \) using distributed method.
    \item \( \text{scan\_distributed}_i \): Processing time for scanning in cluster \( i \) using distributed method.
    \item \( \text{central\_cost} \): Cost per hour for central processing.
    \item \( \text{distributed\_cost} \): Cost per hour for distributed processing.
    \item \( \text{max\_central} \): Maximum hours available for central processing.
    \item \( \text{max\_distributed} \): Maximum hours available for distributed processing.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item Let \( x_{i,j,k} \) be a binary decision variable where:
        \[
        x_{i,j,k} =
        \begin{cases}
        1 & \text{if intervention type } j \text{ is used for cluster } i \text{ with method } k \\
        0 & \text{otherwise}
        \end{cases}
        \]
    where \( i \in \{1, \ldots, N\}, j \in C, k \in M \).
\end{itemize}

\subsection*{Objective Function}
Minimize the total cost:
\[
\text{Total Cost} = \sum_{i=1}^{N} \sum_{j \in C} \sum_{k \in M} c_{j,k} \cdot t_{j,k,i} \cdot x_{i,j,k}
\]
where:
\[
c_{j,k} =
\begin{cases}
\text{central\_cost} & \text{if } k = \text{central} \\
\text{distributed\_cost} & \text{if } k = \text{distributed}
\end{cases}
\]
and \( t_{j,k,i} \) is the processing time for intervention type \( j \) in cluster \( i \) with method \( k \).

\subsection*{Constraints}
1. Each cluster must have exactly one intervention:
\[
\sum_{j \in C} \sum_{k \in M} x_{i,j,k} = 1, \quad \forall i \in \{1, \ldots, N\}
\]

2. Central processing time constraint:
\[
\sum_{i=1}^{N} \sum_{j \in C} \text{isolate\_central}_i \cdot x_{i,\text{isolate},\text{central}} + \sum_{i=1}^{N} \sum_{j \in C} \text{scan\_central}_i \cdot x_{i,\text{scan},\text{central}} \leq \text{max\_central}
\]

3. Distributed processing time constraint:
\[
\sum_{i=1}^{N} \sum_{j \in C} \text{isolate\_distributed}_i \cdot x_{i,\text{isolate},\text{distributed}} + \sum_{i=1}^{N} \sum_{j \in C} \text{scan\_distributed}_i \cdot x_{i,\text{scan},\text{distributed}} \leq \text{max\_distributed}
\]

\subsection*{Output}
The solution will provide:
\begin{itemize}
    \item A set of interventions for each cluster in the format:
    \[
    \text{interventions} =
    \begin{cases}
        \{ \text{cluster\_id}, \text{type}, \text{method}, \text{amount} \} & \forall i \in \{1, \ldots, N\}
    \end{cases}
    \]
    \item The total cost: \( \text{total\_cost} \).
\end{itemize}

\end{document}