\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Custom Tees Online Advertising Campaign}

\subsection*{Parameters}
\begin{itemize}
    \item Let \( A \): Number of different ad types.
    \item Let \( \text{goal\_young} \): Target clicks from visitors aged 18-25 (in thousands).
    \item Let \( \text{goal\_old} \): Target clicks from visitors older than 25 (in thousands).
    \item Let \( \text{goal\_unique\_young} \): Target unique clicks from visitors aged 18-25 (in thousands).
    \item Let \( \text{goal\_unique\_old} \): Target unique clicks from visitors older than 25 (in thousands).
    \item Let \( \text{young\_click}_{a} \): Percentage of clicks from 18-25 age range for ad type \( a \).
    \item Let \( \text{old\_click}_{a} \): Percentage of clicks from visitors older than 25 for ad type \( a \).
    \item Let \( \text{cost}_{a} \): Cost of ad type \( a \) per 1000 clicks.
    \item Let \( \text{max\_click}_{a} \): Maximum allowable clicks for ad type \( a \) (in thousands).
    \item Let \( \text{unique\_click}_{a} \): Estimated percentage of unique visitors for ad type \( a \).
\end{itemize}

\subsection*{Decision Variables}
Let \( x_a \): Number of clicks purchased for ad type \( a \) (in thousands) for \( a = 1, \ldots, A \).

\subsection*{Objective Function}
The objective is to minimize the total cost:
\[
\text{Minimize} \quad Z = \sum_{a=1}^{A} \text{cost}_{a} \cdot x_{a}
\]

\subsection*{Constraints}
1. Clicks from visitors aged 18-25:
\[
\sum_{a=1}^{A} \text{young\_click}_{a} \cdot x_{a} \geq \text{goal\_young}
\]

2. Clicks from visitors older than 25:
\[
\sum_{a=1}^{A} \text{old\_click}_{a} \cdot x_{a} \geq \text{goal\_old}
\]

3. Unique clicks from visitors aged 18-25:
\[
\sum_{a=1}^{A} \text{unique\_click}_{a} \cdot x_{a} \geq \text{goal\_unique\_young}
\]

4. Unique clicks from visitors older than 25:
\[
\sum_{a=1}^{A} \text{unique\_click}_{a} \cdot x_{a} \geq \text{goal\_unique\_old}
\]

5. Maximum allowable clicks for each ad type:
\[
x_{a} \leq \text{max\_click}_{a} \quad \forall a = 1, \ldots, A
\]

6. Non-negativity constraints:
\[
x_{a} \geq 0 \quad \forall a = 1, \ldots, A
\]

\subsection*{Output}
The output will include:
\begin{itemize}
    \item Clicks purchased for each ad type: \( \{ x_{a} \}_{a=1}^{A} \) in thousands.
    \item Total cost of the ad campaign: \( Z \).
\end{itemize}

\end{document}