\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Auto Parts Manufacturer}

\subsection*{Parameters}
\begin{itemize}
    \item Let \( P \) be the number of different parts.
    \item Let \( M \) be the number of different machines.
    \item Let \( \text{time}_{m,p} \) be the hours required on machine \( m \) to produce a batch of 100 parts \( p \).
    \item Let \( \text{cost}_{m} \) be the charge per hour for using machine \( m \).
    \item Let \( \text{available}_{m} \) be the availability of machine \( m \) in hours per month.
    \item Let \( \text{price}_{p} \) be the selling price per batch of part \( p \).
    \item Let \( \text{min\_batches}_{p} \) be the minimum number of batches of part \( p \) to be produced to fulfill a contract.
    \item Let \( \text{standard\_cost} \) be the labor cost per hour up to a limit.
    \item Let \( \text{overtime\_cost} \) be the labor cost per hour after the limit.
    \item Let \( \text{overtime\_hour} \) be the maximum hours before overtime charges apply.
    \item Let \( \text{min\_profit} \) be the minimum desired profit.
\end{itemize}

\subsection*{Decision Variables}
Let \( x_{p} \) be the number of batches of part \( p \) produced.

\subsection*{Objective Function}
Maximize total profit:
\[
\text{Total Profit} = \sum_{p=1}^{P} \left( \text{price}_{p} \cdot x_{p} \right) - \sum_{m=1}^{M} \left( \text{cost}_{m} \cdot \left( \sum_{p=1}^{P} \text{time}_{m,p} \cdot x_{p} \right) \right) - \text{Labor Costs}
\]

\subsection*{Labor Costs}
\[
\text{Labor Costs} = 
\begin{cases} 
\text{standard\_cost} \cdot \text{overtime\_hour} & \text{if } \sum_{p=1}^{P} \sum_{m=1}^{M} \text{time}_{m,p} \cdot x_{p} \leq \text{overtime\_hour} \\ 
\text{standard\_cost} \cdot \text{overtime\_hour} + \text{overtime\_cost} \cdot \left( \sum_{p=1}^{P} \sum_{m=1}^{M} \text{time}_{m,p} \cdot x_{p} - \text{overtime\_hour} \right) & \text{if } \sum_{p=1}^{P} \sum_{m=1}^{M} \text{time}_{m,p} \cdot x_{p} > \text{overtime\_hour}
\end{cases}
\]

\subsection*{Constraints}
1. Machine Availability Constraints:
\[
\sum_{p=1}^{P} \text{time}_{m,p} \cdot x_{p} \leq \text{available}_{m} \quad \text{for all } m = 1, \ldots, M
\]

2. Minimum Batches Requirement:
\[
x_{p} \geq \text{min\_batches}_{p} \quad \text{for all } p = 1, \ldots, P
\]

3. Minimum Profit Requirement:
\[
\text{Total Profit} \geq \text{min\_profit}
\]

4. Non-negativity Constraints:
\[
x_{p} \geq 0 \quad \text{for all } p = 1, \ldots, P
\]

\end{document}