\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for DEC Production Optimization}

\subsection*{Indices}
\begin{itemize}
    \item $i \in \{1, \ldots, N\}$: Index for different computer systems.
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item $is\_workstation_i$: Boolean indicating if system $i$ is a workstation.
    \item $price_i$: Price of system $i$ (in dollars).
    \item $disk_i$: Average number of disk drives requested per system $i$.
    \item $mem_i$: Average number of 256K memory boards requested per system $i$.
    \item $max\_cpu$: Maximum number of CPUs available.
    \item $min\_disk$: Minimum available disk drives.
    \item $max\_disk$: Maximum available disk drives.
    \item $min\_mem$: Minimum available 256K memory boards.
    \item $max\_mem$: Maximum available 256K memory boards.
    \item $demand_i$: Maximum demand for system $i$.
    \item $demand\_GP$: Maximum demand for the whole GP family.
    \item $demand\_WS$: Maximum demand for the whole WS family.
    \item $preorder_i$: Preorders for system $i$.
    \item $alt\_mem$: Available alternative memory boards.
    \item $alt\_compatible_i$: Boolean indicating compatibility of alternative memory for system $i$.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item $x_i$: Number of systems produced for system $i$.
    \item $y_i$: Number of alternative memory boards used for system $i$.
\end{itemize}

\subsection*{Objective Function}
Maximize the profit:
\[
\text{Maximize} \quad Z = \sum_{i=1}^{N} (price_i \cdot x_i) - \text{Cost}
\]

\subsection*{Constraints}
\begin{align*}
\text{CPU Constraint:} & \quad \sum_{i=1}^{N} x_i \leq max\_cpu \\
\text{Disk Drive Demand:} & \quad \sum_{i=1}^{N} disk_i \cdot x_i \leq max\_disk \\
\text{Memory Board Demand:} & \quad \sum_{i=1}^{N} mem_i \cdot x_i + \sum_{i=1}^{N} y_i \leq max\_mem \\
\text{Minimum Disk Supply:} & \quad \sum_{i=1}^{N} disk_i \cdot x_i \geq min\_disk \\
\text{Minimum Memory Supply:} & \quad \sum_{i=1}^{N} mem_i \cdot x_i + \sum_{i=1}^{N} y_i \geq min\_mem \\
\text{Demand Satisfaction for System } i: & \quad x_i \leq demand_i \\
\text{Demand Satisfaction for GP Family:} & \quad \sum_{i: is\_workstation_i = false} x_i \leq demand\_GP \\
\text{Demand Satisfaction for WS Family:} & \quad \sum_{i: is\_workstation_i = true} x_i \leq demand\_WS \\
\text{Preorder Constraint for System } i: & \quad x_i \geq preorder_i \\
\text{Alternative Memory Usage:} & \quad y_i \leq alt\_mem \quad (alt\_compatible_i = true)
\end{align*}

\end{document}