\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Custom Tees Advertising Campaign}

\subsection*{Variables}
Let \( x_a \) be the number of clicks purchased for ad type \( a \) (in thousands), where \( a = 1, 2, \ldots, A \).

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{goal\_young} \): Target clicks from visitors aged 18-25 (in thousands).
    \item \( \text{goal\_old} \): Target clicks from visitors older than 25 (in thousands).
    \item \( \text{goal\_unique\_young} \): Target unique clicks from visitors aged 18-25 (in thousands).
    \item \( \text{goal\_unique\_old} \): Target unique clicks from visitors older than 25 (in thousands).
    \item \( \text{young\_click}_a \): Percentage of clicks from the 18-25 age range for ad type \( a \).
    \item \( \text{old\_click}_a \): Percentage of clicks from older visitors for ad type \( a \).
    \item \( \text{cost}_a \): Cost per 1000 clicks for ad type \( a \).
    \item \( \text{max\_click}_a \): Maximum allowable clicks for ad type \( a \) (in thousands).
    \item \( \text{unique\_click}_a \): Estimated percentage of unique visitors from ad type \( a \).
    \item \( \text{budget} \): Total advertising budget.
\end{itemize}

\subsection*{Objective Function}
Maximize the total number of unique clicks:
\[
\text{Maximize} \quad Z = \sum_{a=1}^{A} (\text{unique\_click}_a \cdot x_a)
\]

\subsection*{Constraints}
\begin{align*}
    & \text{Clicks from young visitors:} \\
    & \sum_{a=1}^{A} (\text{young\_click}_a \cdot x_a) \geq \text{goal\_young} \\
    & \text{Clicks from old visitors:} \\
    & \sum_{a=1}^{A} (\text{old\_click}_a \cdot x_a) \geq \text{goal\_old} \\
    & \text{Unique clicks from young visitors:} \\
    & \sum_{a=1}^{A} \left( \frac{\text{unique\_click}_a}{100} \cdot x_a \right) \geq \text{goal\_unique\_young} \\
    & \text{Unique clicks from old visitors:} \\
    & \sum_{a=1}^{A} \left( \frac{\text{unique\_click}_a}{100} \cdot x_a \right) \geq \text{goal\_unique\_old} \\
    & \text{Budget constraint:} \\
    & \sum_{a=1}^{A} \left( \text{cost}_a \cdot x_a \right) \leq \text{budget} \\
    & \text{Maximum clicks constraint:} \\
    & 0 \leq x_a \leq \text{max\_click}_a \quad \forall a
\end{align*}

\subsection*{Output Variables}
\begin{itemize}
    \item \( \text{clicks} = [x_a \text{ for } a = 1, \ldots, A] \) : Number of clicks purchased for each ad type (in thousands).
    \item \( \text{total\_unique\_clicks} = Z \): Total number of unique clicks.
\end{itemize}

\end{document}