\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for Translator Selection Problem}

\subsection*{Parameters}
\begin{itemize}
    \item \( N \): Total number of translators available.
    \item \( M \): Total number of required languages.
    \item \( \text{cost}_i \): Cost of hiring translator \( i \) (for \( i = 1, \ldots, N \)).
    \item \( \text{languages}_i \): Set of languages translator \( i \) can translate into.
    \item \( \text{required\_languages} = \{language_1, language_2, \ldots, language_M\} \): Set of languages that need to be translated.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( x_i \): Binary variable indicating whether translator \( i \) is hired (\( x_i = 1 \)) or not (\( x_i = 0 \)).
\end{itemize}

\subsection*{Objective Function}
Minimize the total cost of hiring translators:
\[
\text{Minimize } Z = \sum_{i=1}^{N} \text{cost}_i \cdot x_i
\]

\subsection*{Constraints}
1. Ensure all required languages are covered:
\[
\sum_{i=1}^{N} x_i \cdot \mathbb{1}_{\text{language}_j \in \text{languages}_i} \geq 1 \quad \forall j = 1, \ldots, M
\]
where \( \mathbb{1}_{\text{language}_j \in \text{languages}_i} \) is an indicator function that equals 1 if language \( j \) is included in the languages translated by translator \( i \), and 0 otherwise.

2. Binary decision variables:
\[
x_i \in \{0, 1\} \quad \forall i = 1, \ldots, N
\]

\subsection*{Output}
The output will include:
\begin{itemize}
    \item \( \text{selected\_translators} \): List of translator IDs selected.
    \item \( \text{total\_cost} \): Total cost for hiring the selected translators.
\end{itemize}

\end{document}