\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for MILP Problem}

\subsection*{Parameters}
\begin{itemize}
    \item Let $N$ be the number of clusters.
    \item Let $isolate\_central_{i}$ be the processing time for isolation of cluster $i$ using central processing, for $i = 1, \ldots, N$.
    \item Let $scan\_central_{i}$ be the processing time for scanning of cluster $i$ using central processing, for $i = 1, \ldots, N$.
    \item Let $isolate\_distributed_{i}$ be the processing time for isolation of cluster $i$ using distributed processing, for $i = 1, \ldots, N$.
    \item Let $scan\_distributed_{i}$ be the processing time for scanning of cluster $i$ using distributed processing, for $i = 1, \ldots, N$.
    \item Let $central\_cost$ be the opportunity cost for central processing per hour.
    \item Let $distributed\_cost$ be the opportunity cost for distributed processing per hour.
    \item Let $max\_central$ be the maximum hours allowed for central processing.
    \item Let $max\_distributed$ be the maximum hours allowed for distributed processing.
\end{itemize}

\subsection*{Decision Variables}
Let:
\begin{itemize}
    \item $x_{i}^{isolate\_central}$ = 1 if cluster $i$ is isolated using central processing, 0 otherwise.
    \item $x_{i}^{scan\_central}$ = 1 if cluster $i$ is scanned using central processing, 0 otherwise.
    \item $x_{i}^{isolate\_distributed}$ = 1 if cluster $i$ is isolated using distributed processing, 0 otherwise.
    \item $x_{i}^{scan\_distributed}$ = 1 if cluster $i$ is scanned using distributed processing, 0 otherwise.
\end{itemize}

\subsection*{Objective Function}
Minimize the total cost:
\[
\text{Total Cost} = \sum_{i=1}^{N} \left( central\_cost \cdot (isolate\_central_{i} \cdot x_{i}^{isolate\_central} + scan\_central_{i} \cdot x_{i}^{scan\_central}) + distributed\_cost \cdot (isolate\_distributed_{i} \cdot x_{i}^{isolate\_distributed} + scan\_distributed_{i} \cdot x_{i}^{scan\_distributed}) \right)
\]

\subsection*{Constraints}

\begin{itemize}
    \item Each cluster must have exactly one type of intervention:
    \[
    x_{i}^{isolate\_central} + x_{i}^{scan\_central} + x_{i}^{isolate\_distributed} + x_{i}^{scan\_distributed} = 1, \quad \forall i = 1, \ldots, N
    \]

    \item Central processing time constraint:
    \[
    \sum_{i=1}^{N}(isolate\_central_{i} \cdot x_{i}^{isolate\_central} + scan\_central_{i} \cdot x_{i}^{scan\_central}) \leq max\_central
    \]

    \item Distributed processing time constraint:
    \[
    \sum_{i=1}^{N}(isolate\_distributed_{i} \cdot x_{i}^{isolate\_distributed} + scan\_distributed_{i} \cdot x_{i}^{scan\_distributed}) \leq max\_distributed
    \]
\end{itemize}

\subsection*{Output}

The output will detail the selected intervention for each cluster and the total cost incurred:
\[
\text{Output} = 
\begin{cases} 
\text{interventions:} \\
\{(cluster\_id = i, type = "isolate" \text{ or } "scan", method = "central" \text{ or } "distributed", amount = amount_i)\} \\
\text{for } i = 1, \ldots, N 
\end{cases}
\]

\[
\text{total\_cost} = \text{Total Cost}
\]

\end{document}