\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model}

\subsection*{Parameters}
\begin{align*}
&\text{Let } I \text{ be the number of different oils.} \\
&\text{Let } M \text{ be the number of months.} \\
&\text{Let } \text{buy\_price}_{i,m} \text{ be the purchase price of oil } i \text{ in month } m. \\
&\text{Let } \text{sell\_price} \text{ be the selling price per ton of the final product.} \\
&\text{Let } \text{is\_vegetable}_{i} \text{ be 1 if oil } i \text{ is vegetable, 0 otherwise.} \\
&\text{Let } \text{max\_veg} \text{ be the maximum tons of vegetable oils refined per month.} \\
&\text{Let } \text{max\_non\_veg} \text{ be the maximum tons of non-vegetable oils refined per month.} \\
&\text{Let } \text{storage\_size} \text{ be the maximum storage capacity for each oil.} \\
&\text{Let } \text{storage\_cost} \text{ be the storage cost per ton per month.} \\
&\text{Let } \text{max\_hardness} \text{ and } \text{min\_hardness} \text{ be the hardness bounds.} \\
&\text{Let } \text{hardness}_{i} \text{ be the hardness of oil } i. \\
&\text{Let } \text{init\_amount} \text{ be the initial tons of each oil in storage.}
\end{align*}

\subsection*{Decision Variables}
\begin{align*}
&\text{Let } \text{buyquantity}_{i, m} \text{ be the amount of oil } i \text{ bought in month } m. \\
&\text{Let } \text{refine}_{i, m} \text{ be the amount of oil } i \text{ refined in month } m. \\
&\text{Let } \text{storage}_{i, m} \text{ be the storage of oil } i \text{ at the end of month } m. \\
\end{align*}

\subsection*{Objective Function}
Maximize the profit:
\[
\sum_{m=1}^{M} \left( \text{sell\_price} \cdot \sum_{i=1}^{I} \text{refine}_{i, m} - \sum_{i=1}^{I} \left( \text{buy\_price}_{i, m} \cdot \text{buyquantity}_{i, m} + \text{storage\_cost} \cdot \text{storage}_{i, m} \right) \right)
\]

\subsection*{Constraints}
\begin{align*}
&\text{Storage balance:}\\
&\ \ \text{storage}_{i, m-1} + \text{buyquantity}_{i, m} = \text{refine}_{i, m} + \text{storage}_{i, m} \quad \forall i, \, \forall m \\
&\text{Initial storage:}\\
&\ \ \text{storage}_{i, 0} = \text{init\_amount} \quad \forall i \\
&\text{Final storage:}\\
&\ \ \text{storage}_{i, M} = \text{init\_amount} \quad \forall i \\
&\text{Refining capacity (vegetable oils):}\\
&\ \ \sum_{i: \text{is\_vegetable}_{i} = 1} \text{refine}_{i, m} \leq \text{max\_veg} \quad \forall m \\
&\text{Refining capacity (non-vegetable oils):}\\
&\ \ \sum_{i: \text{is\_vegetable}_{i} = 0} \text{refine}_{i, m} \leq \text{max\_non\_veg} \quad \forall m \\
&\text{Storage capacity:}\\
&\ \ \text{storage}_{i, m} \leq \text{storage\_size} \quad \forall i, \, \forall m \\
&\text{Hardness constraint:}\\
&\ \ \sum_{i=1}^{I} \text{hardness}_{i} \cdot \text{refine}_{i, m} \leq \text{max\_hardness} \cdot \sum_{i=1}^{I} \text{refine}_{i, m} \quad \forall m \\
&\ \ \sum_{i=1}^{I} \text{hardness}_{i} \cdot \text{refine}_{i, m} \geq \text{min\_hardness} \cdot \sum_{i=1}^{I} \text{refine}_{i, m} \quad \forall m \\
&\text{Non-negativity:}\\
&\ \ \text{buyquantity}_{i, m}, \text{refine}_{i, m}, \text{storage}_{i, m} \geq 0 \quad \forall i, \, \forall m \\
\end{align*}

\end{document}