\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Auto Parts Manufacturing}

\subsection*{Sets and Parameters}
\begin{itemize}
    \item Let \( P \) be the number of different parts.
    \item Let \( M \) be the number of different machines.
    \item Let \( \text{time}_{m,p} \) be the time required on machine \( m \) to produce a batch of part \( p \) (in hours).
    \item Let \( \text{cost}_{m} \) be the cost per hour of using machine \( m \).
    \item Let \( \text{available}_{m} \) be the available hours for machine \( m \) per month.
    \item Let \( \text{price}_{p} \) be the selling price per batch of part \( p \).
    \item Let \( \text{min\_batches}_{p} \) be the minimum number of batches of part \( p \) that must be produced.
    \item Let \( \text{standard\_cost} \) be the standard labor cost per hour.
    \item Let \( \text{overtime\_cost} \) be the overtime labor cost per hour.
    \item Let \( \text{overtime\_hour} \) be the number of hours before overtime rates apply.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item Let \( \text{batches}_{p} \) be the number of batches produced for part \( p \).
\end{itemize}

\subsection*{Objective Function}
Maximize the total profit:
\[
\text{Total Profit} = \sum_{p=1}^{P} \left( \text{price}_{p} \cdot \text{batches}_{p} \right) - \sum_{m=1}^{M} \left( \text{cost}_{m} \cdot \text{hours}_{m} \right)
\]

where
\[
\text{hours}_{m} = \sum_{p=1}^{P} \left( \text{time}_{m,p} \cdot \text{batches}_{p} \right)
\]

\subsection*{Constraints}
1. Machine availability constraints:
\[
\sum_{p=1}^{P} \left( \text{time}_{m,p} \cdot \text{batches}_{p} \right) \leq \text{available}_{m}, \quad \forall m = 1, \ldots, M
\]

2. Minimum production requirements:
\[
\text{batches}_{p} \geq \text{min\_batches}_{p}, \quad \forall p = 1, \ldots, P
\]

3. Labor cost considerations for Machine 1:
\[
\text{Labor Cost} =
\begin{cases} 
\text{standard\_cost} \cdot \text{hours}_{1}, & \text{if } \text{hours}_{1} \leq \text{overtime\_hour} \\
\text{standard\_cost} \cdot \text{overtime\_hour} + \text{overtime\_cost} \cdot (\text{hours}_{1} - \text{overtime\_hour}), & \text{if } \text{hours}_{1} > \text{overtime\_hour}
\end{cases}
\]

4. Non-negativity constraints:
\[
\text{batches}_{p} \geq 0, \quad \forall p = 1, \ldots, P
\]

\end{document}