\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for the MILP Problem}

\subsection*{Parameters}
\begin{itemize}
    \item Let \( N \) be the number of clusters.
    \item Let \( \text{isolate\_central}_{i} \) be the processing time for isolating nodes centrally in cluster \( i \).
    \item Let \( \text{scan\_central}_{i} \) be the processing time for scanning nodes centrally in cluster \( i \).
    \item Let \( \text{isolate\_distributed}_{i} \) be the processing time for isolating nodes through distributed processing in cluster \( i \).
    \item Let \( \text{scan\_distributed}_{i} \) be the processing time for scanning nodes through distributed processing in cluster \( i \).
    \item Let \( \text{central\_cost} \) be the cost per hour for central processing.
    \item Let \( \text{distributed\_cost} \) be the cost per hour for distributed processing.
    \item Let \( \text{max\_central} \) be the maximum hours allowed for central processing.
    \item Let \( \text{max\_distributed} \) be the maximum hours allowed for distributed processing.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item Let \( x_{i}^{\text{isolate,central}} \) be a binary variable that equals 1 if the intervention type "isolate" is done centrally for cluster \( i \), and 0 otherwise.
    \item Let \( x_{i}^{\text{scan,central}} \) be a binary variable that equals 1 if the intervention type "scan" is done centrally for cluster \( i \), and 0 otherwise.
    \item Let \( y_{i}^{\text{isolate,distributed}} \) be a binary variable that equals 1 if the intervention type "isolate" is done through distributed processing for cluster \( i \), and 0 otherwise.
    \item Let \( y_{i}^{\text{scan,distributed}} \) be a binary variable that equals 1 if the intervention type "scan" is done through distributed processing for cluster \( i \), and 0 otherwise.
\end{itemize}

\subsection*{Objective Function}
Minimize the total cost:
\[
\text{Total Cost} = \sum_{i=1}^{N} \left( \text{isolate\_central}_{i} \cdot x_{i}^{\text{isolate,central}} + \text{scan\_central}_{i} \cdot x_{i}^{\text{scan,central}} \cdot \text{central\_cost} + \text{isolate\_distributed}_{i} \cdot y_{i}^{\text{isolate,distributed}} + \text{scan\_distributed}_{i} \cdot y_{i}^{\text{scan,distributed}} \cdot \text{distributed\_cost} \right)
\]

\subsection*{Constraints}

1. Each cluster must have one intervention type consistently:
\[
x_{i}^{\text{isolate,central}} + x_{i}^{\text{scan,central}} + y_{i}^{\text{isolate,distributed}} + y_{i}^{\text{scan,distributed}} = 1, \quad \forall i = 1, \ldots, N
\]

2. Central processing time must not exceed maximum hours:
\[
\sum_{i=1}^{N} \left( \text{isolate\_central}_{i} \cdot x_{i}^{\text{isolate,central}} + \text{scan\_central}_{i} \cdot x_{i}^{\text{scan,central}} \right) \leq \text{max\_central}
\]

3. Distributed processing time must not exceed maximum hours:
\[
\sum_{i=1}^{N} \left( \text{isolate\_distributed}_{i} \cdot y_{i}^{\text{isolate,distributed}} + \text{scan\_distributed}_{i} \cdot y_{i}^{\text{scan,distributed}} \right) \leq \text{max\_distributed}
\]

\subsection*{Output Information}
The output will include:
\begin{itemize}
    \item An array detailing the intervention type ('isolate' or 'scan') and processing method ('central' or 'distributed') for each cluster.
    \item The total cost of all interventions across the clusters.
\end{itemize}

\end{document}