\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for the Engineering Factory}

\textbf{Indices:}
\begin{itemize}
    \item $k$: index for products, $k = 1, 2, \ldots, K$.
    \item $m$: index for machines, $m = 1, 2, \ldots, M$.
    \item $i$: index for months, $i = 1, 2, \ldots, I$.
\end{itemize}

\textbf{Parameters:}
\begin{itemize}
    \item $num_m$: number of machines available.
    \item $profit_k$: profit from selling product $k$.
    \item $time_{k, m}$: time required to produce product $k$ on machine $m$ (in hours).
    \item $maintain_{i, m}$: number of machines down for maintenance in month $i$.
    \item $limit_{k, i}$: marketing limitation on product $k$ in month $i$.
    \item $store\_price$: cost of storing one unit of product per month.
    \item $keep\_quantity$: desired amount of each product to keep in stock at the end of the month.
    \item $n\_workhours$: number of working hours in a day.
\end{itemize}

\textbf{Decision Variables:}
\begin{itemize}
    \item $sell_{k,i}$: quantity of product $k$ sold in month $i$.
    \item $manufacture_{k,i}$: quantity of product $k$ manufactured in month $i$.
    \item $storage_{k,i}$: quantity of product $k$ stored at the end of month $i$.
\end{itemize}

\textbf{Objective Function:}
\begin{align*}
    \text{Maximize } Z = & \sum_{i=1}^{I} \sum_{k=1}^{K} (profit_k \cdot sell_{k, i}) - \sum_{i=1}^{I} \sum_{k=1}^{K} (store\_price \cdot storage_{k, i})
\end{align*}

\textbf{Subject to:}
\begin{align}
    & \sum_{k=1}^{K} sell_{k, i} \leq limit_{k, i} & \forall k, i \tag{1} \\
    & storage_{k, i} = storage_{k, i-1} + manufacture_{k, i} - sell_{k, i} & \forall k, i \tag{2} \\
    & storage_{k, i} \leq 100 & \forall k, i \tag{3} \\
    & manufacture_{k,i} \leq \sum_{m=1}^{M} \left( \frac{n\_workhours \times (6 \times 24 - \sum_{m=1}^{M} maintain_{i, m})}{time_{k, m}} \right) & \forall k, i \tag{4} \\
    & storage_{k, I} \geq keep\_quantity & \forall k \tag{5} \\
    & sell_{k, i}, manufacture_{k, i}, storage_{k, i} \geq 0 & \forall k, i \tag{6}
\end{align}

\textbf{Where:}
\begin{itemize}
    \item (1): Sales must not exceed marketing limits.
    \item (2): Storage condition for each month based on manufacture and sales.
    \item (3): Storage must not exceed the maximum capacity.
    \item (4): Manufacture is limited by machine availability and production time.
    \item (5): End-month storage must meet the desired quantity.
    \item (6): Non-negativity constraints on decision variables.
\end{itemize}

\end{document}