\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Optimal Path Problem in a Grid}

Consider a delivery person starting at the intersection of the \(1^{st}\) Avenue and \(1^{st}\) Street, with the aim to reach the intersection of the \(W^{th}\) Avenue and \(N^{th}\) Street. The path forms an \((N-1) \times (W-1)\) grid, allowing movement only north or west.

\subsection*{Definitions}
Let:
\begin{itemize}
    \item \( \text{west\_time}_{n,w} \) be the time to move from the intersection of the \(w^{th}\) Avenue and \(n^{th}\) Street to the \( (w+1)^{th} \) Avenue and \(n^{th}\) Street.
    \item \( \text{north\_time}_{n,w} \) be the time to move from the intersection of the \(w^{th}\) Avenue and \(n^{th}\) Street to the \(w^{th}\) Avenue and \( (n+1)^{th} \) Street.
\end{itemize}

\subsection*{Input Format}
The input format is defined as follows:
\[
\begin{aligned}
    \text{Input: } & \{ \\
    & \quad \text{"west\_time": } [[\text{west}_{n,w} \text{ for } w \text{ in } 1, ..., W-1] \text{ for } n \text{ in } 1, ..., N], \\
    & \quad \text{"north\_time": } [[\text{north}_{n,w} \text{ for } w \text{ in } 1, ..., W] \text{ for } n \text{ in } 1, ..., N-1] \\
    & \}
\end{aligned}
\]

\subsection*{Objective}
The goal is to determine the optimal path for the delivery person to ensure that the package is delivered in the least amount of time. 

\subsection*{Variables}
Define:
\begin{itemize}
    \item \( x_{n,w} \): binary variable indicating whether the path goes through the intersection of \(w^{th}\) Avenue and \(n^{th}\) Street.
\end{itemize}

\subsection*{Objective Function}
The total time taken to travel this path can be represented as:
\[
\text{total\_time} = \sum_{n=1}^{N-1} \sum_{w=1}^{W-1} (\text{west\_time}_{n,w} \cdot x_{n,w} + \text{north\_time}_{n,w} \cdot x_{n,w})
\]

\subsection*{Constraints}
\begin{itemize}
    \item The delivery person must leave from the start position \((1, 1)\) and reach the end position \((W, N)\).
    \item The person can only move to the next block either to the north or west.
    \item There should be continuity in the path taken.
\end{itemize}

\subsection*{Output Format}
The expected output format is:
\[
\{ 
    \text{"paths": } [(street_{n}, avenue_{w}) \text{ for } id \text{ in } 1, ..., m], 
    \text{"total\_time": } total\_travel\_time 
\}
\]

\end{document}