\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}

\begin{document}

\section*{Mixed Integer Programming Model for Power Generation Scheduling}

\subsection*{Parameters}
\begin{itemize}
    \item \( T \): Number of time periods in a day.
    \item \( K \): Number of types of generators.
    \item \( \text{demand}_t \): Demand in period \( t \).
    \item \( \text{num}_k \): Number of units of type \( k \).
    \item \( \text{minlevel}_k \): Minimum level at which a type \( k \) generator can operate.
    \item \( \text{maxlevel}_k \): Maximum level at which a type \( k \) generator can operate.
    \item \( \text{runcost}_k \): Hourly cost of running a type \( k \) generator at its minimum level.
    \item \( \text{extracost}_k \): Extra hourly cost per megawatt above the minimum level for a type \( k \) generator.
    \item \( \text{startcost}_k \): Starting cost for a type \( k \) generator.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( \text{numon}_{k,t} \): Number of type \( k \) generators on in period \( t \).
    \item \( \text{level}_{k,t} \): Generation level of a type \( k \) generator in period \( t \) (above the minimum level).
    \item \( \text{start}_{k,t} \): Binary variable indicating whether a type \( k \) generator is started in period \( t \).
\end{itemize}

\subsection*{Objective Function}
Minimize the total cost:
\[
\min \sum_{t=1}^{T} \sum_{k=1}^{K} \left( \text{runcost}_k \cdot \text{numon}_{k,t} + \text{extracost}_k \cdot \text{level}_{k,t} \cdot \text{numon}_{k,t} + \text{startcost}_k \cdot \text{start}_{k,t} \right)
\]

\subsection*{Constraints}
\begin{itemize}
    \item \textbf{Demand satisfaction:}
    \[
    \sum_{k=1}^{K} \left( \text{minlevel}_k \cdot \text{numon}_{k,t} + \text{level}_{k,t} \cdot \text{numon}_{k,t} \right) \geq \text{demand}_t, \quad \forall t
    \]

    \item \textbf{Capacity constraints:}
    \[
    0 \leq \text{level}_{k,t} \leq \left( \text{maxlevel}_k - \text{minlevel}_k \right) \cdot \text{numon}_{k,t}, \quad \forall k, t
    \]

    \item \textbf{Number of operational units:}
    \[
    0 \leq \text{numon}_{k,t} \leq \text{num}_k, \quad \forall k, t
    \]

    \item \textbf{Startup constraint:}
    \[
    \text{start}_{k,t} \geq \text{numon}_{k,t} - \text{numon}_{k,t-1}, \quad \forall k, t
    \]
    \quad Assuming \( \text{numon}_{k,0} = 0 \) for initialization.
\end{itemize}

\end{document}