\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for Intrusion Intervention}

\subsection*{Parameters}
\begin{itemize}
    \item Let \( N \) be the number of clusters.
    \item Let \( \text{isolate\_central}_{i} \) be the processing time for isolating cluster \( i \) using central processing.
    \item Let \( \text{scan\_central}_{i} \) be the processing time for scanning cluster \( i \) using central processing.
    \item Let \( \text{isolate\_distributed}_{i} \) be the processing time for isolating cluster \( i \) using distributed processing.
    \item Let \( \text{scan\_distributed}_{i} \) be the processing time for scanning cluster \( i \) using distributed processing.
    \item Let \( \text{central\_cost} \) be the cost per hour for central processing.
    \item Let \( \text{distributed\_cost} \) be the cost per hour for distributed processing.
    \item Let \( \text{max\_central} \) be the maximum hours allotted for central processing.
    \item Let \( \text{max\_distributed} \) be the maximum hours allotted for distributed processing.
\end{itemize}

\subsection*{Decision Variables}
Let 
\[
x_{i,j,k} = 
\begin{cases} 
1 & \text{if intervention } j \text{ (isolate or scan) is applied to cluster } i \text{ using method } k \text{ (central or distributed)} \\ 
0 & \text{otherwise}
\end{cases}
\]
where \( j \in \{ \text{isolate, scan} \} \) and \( k \in \{ \text{central, distributed} \} \).

\subsection*{Objective Function}
Minimize the total cost:
\[
\text{Total Cost} = \sum_{i=1}^{N} \sum_{j} \sum_{k} c_{j,k} \cdot p_{j,k,i} \cdot x_{i,j,k}
\]
where
\[
c_{j,k} = 
\begin{cases} 
\text{central\_cost} & \text{if } k = \text{central} \\ 
\text{distributed\_cost} & \text{if } k = \text{distributed}
\end{cases}
\]
and
\[
p_{j,k,i} = 
\begin{cases} 
\text{isolate\_central}_{i} & \text{if } j = \text{isolate} \text{ and } k = \text{central} \\ 
\text{scan\_central}_{i} & \text{if } j = \text{scan} \text{ and } k = \text{central} \\ 
\text{isolate\_distributed}_{i} & \text{if } j = \text{isolate} \text{ and } k = \text{distributed} \\ 
\text{scan\_distributed}_{i} & \text{if } j = \text{scan} \text{ and } k = \text{distributed}
\end{cases}
\]

\subsection*{Constraints}
1. Each cluster must have exactly one intervention type:
\[
\sum_{j} \sum_{k} x_{i,j,k} = 1 \quad \forall i \in \{1, \dots, N\}
\]

2. Central processing time constraint:
\[
\sum_{i=1}^{N} \sum_{j} \text{max\_central} \cdot x_{i,j,\text{central}} \leq \text{max\_central}
\]

3. Distributed processing time constraint:
\[
\sum_{i=1}^{N} \sum_{j} \text{max\_distributed} \cdot x_{i,j,\text{distributed}} \leq \text{max\_distributed}
\]

\subsection*{Output}
The output will provide details of the interventions:
\begin{verbatim}
{
    "interventions": [
        {
            "cluster_id": i,
            "type": j,
            "method": k,
            "amount": x_{i,j,k}
        },
        for i in 1, ..., N
    ]
    "total_cost": Total Cost
}
\end{verbatim}

\end{document}