\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mixed Integer Linear Programming (MILP) Model for Network Intrusion Interventions}

\subsection*{Sets}
\begin{itemize}
    \item $N$: Number of clusters.
    \item $C = \{1, 2, \ldots, N\}$: Set of cluster indices.
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item $isolate\_central_i$: Processing time for isolating cluster $i$ centrally.
    \item $scan\_central_i$: Processing time for scanning cluster $i$ centrally.
    \item $isolate\_distributed_i$: Processing time for isolating cluster $i$ through distributed nodes.
    \item $scan\_distributed_i$: Processing time for scanning cluster $i$ through distributed nodes.
    \item $central\_cost$: Opportunity cost for central processing (per hour).
    \item $distributed\_cost$: Opportunity cost for distributed processing (per hour).
    \item $max\_central$: Maximum hours allowed for central processing.
    \item $max\_distributed$: Maximum hours allowed for distributed processing.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item $x_{i}^{isolate} \in \{0, 1\}$: 1 if cluster $i$ is isolated, 0 otherwise.
    \item $x_{i}^{scan} \in \{0, 1\}$: 1 if cluster $i$ is scanned, 0 otherwise.
    \item $y_{i}^{central} \in \{0, 1\}$: 1 if intervention for cluster $i$ is centralized, 0 otherwise.
    \item $y_{i}^{distributed} \in \{0, 1\}$: 1 if intervention for cluster $i$ is distributed, 0 otherwise.
\end{itemize}

\subsection*{Objective Function}
Minimize the total cost:
\[
\text{Minimize } Z = \sum_{i=1}^{N} \left( (isolate\_central_i \cdot y_{i}^{central} + scan\_central_i \cdot y_{i}^{central} + isolate\_distributed_i \cdot y_{i}^{distributed} + scan\_distributed_i \cdot y_{i}^{distributed}) \cdot (central\_cost \cdot y_{i}^{central} + distributed\_cost \cdot y_{i}^{distributed}) \right)
\]

\subsection*{Constraints}

\begin{itemize}
    \item \textbf{Cluster Intervention Consistency:}
    \[
    x_{i}^{isolate} + x_{i}^{scan} = 1, \quad \forall i \in C
    \]

    \item \textbf{Central Processing Time Constraint:}
    \[
    \sum_{i=1}^{N} (isolate\_central_i \cdot y_{i}^{central} + scan\_central_i \cdot y_{i}^{central}) \leq max\_central
    \]

    \item \textbf{Distributed Processing Time Constraint:}
    \[
    \sum_{i=1}^{N} (isolate\_distributed_i \cdot y_{i}^{distributed} + scan\_distributed_i \cdot y_{i}^{distributed}) \leq max\_distributed
    \]

    \item \textbf{Intervention Type Selection:}
    \[
    x_{i}^{isolate} \cdot y_{i}^{central} + x_{i}^{isolate} \cdot y_{i}^{distributed} = x_{i}^{isolate}, \quad \forall i \in C
    \]
    \[
    x_{i}^{scan} \cdot y_{i}^{central} + x_{i}^{scan} \cdot y_{i}^{distributed} = x_{i}^{scan}, \quad \forall i \in C
    \]
\end{itemize}

\subsection*{Output}
The output should specify for each cluster $i$:
\begin{itemize}
    \item \texttt{cluster\_id}: cluster $i$.
    \item \texttt{type}: "isolate" or "scan".
    \item \texttt{method}: "central" or "distributed".
    \item \texttt{amount}: amount processed.
\end{itemize}
The total cost can be computed as:
\[
\text{total\_cost} = Z
\]

\end{document}