\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model}

\subsection*{Parameters}

\begin{align*}
& \text{buy\_price}_{i,m} & \text{Cost of oil } i \text{ in month } m. \\
& \text{sell\_price} & \text{Selling price per ton of final product.} \\
& \text{is\_vegetable}_i & \text{Indicator if oil } i \text{ is vegetable.} \\
& \text{max\_veg} & \text{Max refining capacity for vegetable oils per month.} \\
& \text{max\_non\_veg} & \text{Max refining capacity for non-vegetable oils per month.} \\
& \text{storage\_size} & \text{Max storage size per oil type.} \\
& \text{storage\_cost} & \text{Cost of storage per ton per month.} \\
& \text{max\_hardness} & \text{Max permissible hardness of the final product.} \\
& \text{min\_hardness} & \text{Min permissible hardness of the final product.} \\
& \text{hardness}_i & \text{Hardness of oil } i. \\
& \text{init\_amount} & \text{Initial storage amount for each oil type.} \\
\end{align*}

\subsection*{Decision Variables}

\begin{align*}
& \text{buyquantity}_{i,m} & \text{Amount of oil } i \text{ bought in month } m. \\
& \text{refine}_{i,m} & \text{Amount of oil } i \text{ refined in month } m. \\
& \text{storage}_{i,m} & \text{Amount of oil } i \text{ stored at the end of month } m. \\
\end{align*}

\subsection*{Objective Function}

Maximize the profit:
\[
\sum_{m=1}^{M} \left( \text{sell\_price} \times \sum_{i=1}^{I} \text{refine}_{i,m} - \sum_{i=1}^{I} (\text{buy\_price}_{i,m} \times \text{buyquantity}_{i,m} + \text{storage\_cost} \times \text{storage}_{i,m}) \right)
\]

\subsection*{Constraints}

1. \textbf{Refining Capacity}
\begin{align*}
& \sum_{i \in \text{vegetable oils}} \text{refine}_{i,m} \leq \text{max\_veg} & \forall m \\
& \sum_{i \in \text{non-vegetable oils}} \text{refine}_{i,m} \leq \text{max\_non\_veg} & \forall m \\
\end{align*}

2. \textbf{Hardness Constraint}
\begin{align*}
\text{min\_hardness} \leq \frac{\sum_{i=1}^{I} \text{hardness}_i \times \text{refine}_{i,m}}{\sum_{i=1}^{I} \text{refine}_{i,m}} \leq \text{max\_hardness} & \forall m \\
\end{align*}

3. \textbf{Storage Constraints}
\begin{align*}
& \text{storage}_{i,0} = \text{init\_amount} & \forall i \\
& \text{storage}_{i,M} = \text{init\_amount} & \forall i \\
& \text{storage}_{i,m-1} + \text{buyquantity}_{i,m} - \text{refine}_{i,m} = \text{storage}_{i,m} & \forall i, m > 0 \\
& 0 \leq \text{storage}_{i,m} \leq \text{storage\_size} & \forall i, m \\
\end{align*}

This model will help determine the optimal buying, refining, and storage strategies for the company to maximize its profit, adhering to the given constraints.

\end{document}