\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{MILP Formulation for Floppy Disk Backup Problem}

\subsection*{Sets and Indices}
\begin{itemize}
    \item $j \in \{1, \ldots, N\}$: Index for files, where $N$ is the total number of files.
    \item $i \in \{1, \ldots, N\}$: Index for disks (at most $N$ disks are needed if each file is on a separate disk).
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item $capacity$: Capacity of each floppy disk (in GB).
    \item $size_j$: Size of file $j$ (in GB).
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item $x_{ij} \in \{0, 1\}$: Binary variable, where $x_{ij} = 1$ if file $j$ is assigned to disk $i$, and 0 otherwise.
    \item $y_i \in \{0, 1\}$: Binary variable, where $y_i = 1$ if disk $i$ is used, and 0 otherwise.
\end{itemize}

\subsection*{Objective Function}
Minimize the number of disks used:
\[
\min \sum_{i=1}^{N} y_i
\]

\subsection*{Constraints}
\begin{itemize}
    \item Each file must be placed on exactly one disk:
    \[
    \sum_{i=1}^{N} x_{ij} = 1, \quad \forall j \in \{1, \ldots, N\}
    \]
    
    \item The total size of files on each disk must not exceed its capacity:
    \[
    \sum_{j=1}^{N} size_j \cdot x_{ij} \leq capacity \cdot y_i, \quad \forall i \in \{1, \ldots, N\}
    \]
    
    \item A disk $i$ is used if at least one file is assigned to it:
    \[
    x_{ij} \leq y_i, \quad \forall i \in \{1, \ldots, N\}, \forall j \in \{1, \ldots, N\}
    \]
\end{itemize}

\subsection*{Model Description}
This MILP model seeks to distribute the files across a set of floppy disks in a way that minimizes the number of disks used. The constraints ensure that no disk exceeds its capacity and that each file is assigned to exactly one disk. The decision variable $y_i$ indicates whether disk $i$ is used.

\end{document}