\documentclass{article}
\usepackage{amsmath}
\begin{document}

\title{Mixed Integer Programming Model for DEC Computer Systems Production}
\author{}
\date{}
\maketitle

\section*{Problem Formulation}

\subsection*{Parameters}
\begin{itemize}
    \item $N$: Number of computer systems.
    \item $is\_workstation[i]$: Boolean indicating if system $i$ is a workstation (true) or general-purpose (false).
    \item $price[i]$: Price of system $i$ in dollars.
    \item $disk[i]$: Average number of disk drives requested by customers for system $i$.
    \item $mem[i]$: Average number of 256K memory boards used by system $i$.
    \item $max\_cpu$: Maximum number of CPUs available.
    \item $min\_disk$: Minimum number of disk drives available.
    \item $max\_disk$: Maximum number of disk drives available.
    \item $min\_mem$: Minimum number of 256K memory boards available.
    \item $max\_mem$: Maximum number of 256K memory boards available.
    \item $demand[i]$: Maximum demand for system $i$ in the next quarter.
    \item $demand\_GP$: Maximum demand for all general-purpose systems.
    \item $demand\_WS$: Maximum demand for all workstation systems.
    \item $preorder[i]$: Preorders for system $i$ that must be fulfilled.
    \item $alt\_mem$: Available alternative memory boards.
    \item $alt\_compatible[i]$: Boolean indicating if system $i$ can use alternative memory boards.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item $x[i]$: Number of systems produced of type $i$, where $i = 1, \ldots, N$.
    \item $y[i]$: Number of alternative memory boards used for system $i$.
\end{itemize}

\subsection*{Objective Function}
Maximize total profit:
\[
Z = \sum_{i=1}^{N} (price[i] \cdot x[i]) - \text{costs of memory and disks}
\]

\subsection*{Constraints}
\begin{align}
    \sum_{i=1}^{N} x[i] & \leq max\_cpu \quad \text{(CPU constraint)} \\
    \sum_{i=1}^{N} disk[i] \cdot x[i] & \geq min\_disk \\
    \sum_{i=1}^{N} disk[i] \cdot x[i] & \leq max\_disk \\
    \sum_{i=1}^{N} mem[i] \cdot x[i] & \geq min\_mem \\
    \sum_{i=1}^{N} mem[i] \cdot x[i] & \leq max\_mem \\
    x[i] & \leq demand[i] \quad \forall i \\
    \sum_{i \text{ s.t. } is\_workstation[i]=true} x[i] & \leq demand\_WS \\
    \sum_{i \text{ s.t. } is\_workstation[i]=false} x[i] & \leq demand\_GP \\
    x[i] & \geq preorder[i] \quad \forall i \\
    y[i] & \leq alt\_mem \quad \text{(Alternative memory constraint)}
\end{align}

\subsection*{Output Format}
\texttt{
\{
    "system\_output": [
        {
            "num\_produced": x[i],
            "total\_256K\_boards\_used": mem[i] \cdot x[i],
            "total\_alt\_boards\_used": y[i],
            "total\_disk\_drives\_used": disk[i] \cdot x[i]
        }
        \text{ for } i = 1, \ldots, T
    ],
    "profit": Z
\}
}

\end{document}