\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Oil Refinement}

\subsection*{Variables}
\begin{itemize}
    \item \( buyquantity_{i,m} \): Amount of oil \( i \) bought in month \( m \).
    \item \( refine_{i,m} \): Amount of oil \( i \) refined in month \( m \).
    \item \( storage_{i,m} \): Amount of oil \( i \) stored at the end of month \( m \).
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( price_{i,m} \): Buying price of oil \( i \) in month \( m \).
    \item \( sell\_price \): Selling price of the final product per ton.
    \item \( is\_vegetable_{i} \): Indicator if oil \( i \) is vegetable (1) or non-vegetable (0).
    \item \( max\_veg \): Maximum tons of vegetable oils that can be refined per month.
    \item \( max\_veg \): Maximum tons of non-vegetable oils that can be refined per month.
    \item \( storage\_size \): Maximum storage capacity per oil.
    \item \( storage\_cost \): Cost of storing oil per ton per month.
    \item \( max\_hardness \): Maximum allowed hardness of the final product.
    \item \( min\_hardness \): Minimum allowed hardness of the final product.
    \item \( hardness_{i} \): Hardness of oil \( i \).
    \item \( init\_amount \): Initial amount of each type of oil in storage.
\end{itemize}

\subsection*{Objective Function}
Maximize profit:
\[
\text{Maximize} \quad Z = \sum_{m=1}^{M} \left( sell\_price \cdot ( \sum_{i=1}^{I} refine_{i,m} ) - \sum_{i=1}^{I} \left( price_{i,m} \cdot buyquantity_{i,m} + storage\_cost \cdot storage_{i,m} \right) \right)
\]

\subsection*{Constraints}
1. **Storage Constraints:**
\[
storage_{i,m} = storage_{i,m-1} + buyquantity_{i,m} - refine_{i,m} \quad \forall i, m
\]
2. **Initial Storage Condition:**
\[
storage_{i,0} = init\_amount \quad \forall i
\]
3. **Final Storage Condition:**
\[
storage_{i,M} = init\_amount \quad \forall i
\]
4. **Refining Capacity Constraints:**
\[
\sum_{i \in \text{veg}} refine_{i,m} \leq max\_veg \quad \forall m
\]
\[
\sum_{i \in \text{non-veg}} refine_{i,m} \leq max\_veg \quad \forall m
\]
5. **Hardness Constraint:**
\[
min\_hardness \leq \frac{\sum_{i=1}^{I} (hardness_{i} \cdot refine_{i,m})}{\sum_{i=1}^{I} refine_{i,m}} \leq max\_hardness \quad \forall m
\]
6. **Storage Limit:**
\[
storage_{i,m} \leq storage\_size \quad \forall i, m
\]

\end{document}