\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for DEC Computer Systems Production}

\subsection*{Variables}

Let \( x_i \) be the number of systems produced for system \( i \) where \( i = 1, 2, \ldots, N \).

Let \( y_i \) be the number of alternative memory boards used for system \( i \) where \( i = 1, 2, \ldots, N \).

\subsection*{Parameters}

\begin{itemize}
    \item \( \text{is\_workstation}[i] \): Boolean indicating if system \( i \) is a workstation (WS).
    \item \( \text{price}[i] \): Price of system \( i \) in dollars.
    \item \( \text{disk\_drives}[i] \): Average number of disk drives requested for system \( i \).
    \item \( \text{256K\_boards}[i] \): Average number of 256K memory boards used for system \( i \).
    \item \( \text{max\_cpu} \): Maximum available CPUs.
    \item \( \text{min\_disk} \): Minimum available disk drives.
    \item \( \text{max\_disk} \): Maximum available disk drives.
    \item \( \text{min\_mem} \): Minimum available 256K memory boards.
    \item \( \text{max\_mem} \): Maximum available 256K memory boards.
    \item \( \text{demand}[i] \): Maximum demand for system \( i \).
    \item \( \text{demand\_GP} \): Maximum demand for the whole GP family.
    \item \( \text{demand\_WS} \): Maximum demand for the whole WS family.
    \item \( \text{preorder}[i] \): Preorders for system \( i \).
    \item \( \text{alt\_mem} \): Available alternative memory boards.
    \item \( \text{alt\_compatible}[i] \): Boolean indicating if alternative memory can be used in system \( i \).
\end{itemize}

\subsection*{Objective Function}

Maximize the profit:

\[
\text{Profit} = \sum_{i=1}^{N} ( \text{price}[i] \cdot x_i - \text{cost\_of\_boards}[i] - \text{cost\_of\_disks}[i] )
\]

where:
\[
\text{cost\_of\_boards}[i] = \text{256K\_boards}[i] \cdot x_i + \text{alt\_mem} \cdot y_i
\]
\[
\text{cost\_of\_disks}[i] = \text{disk\_drives}[i] \cdot x_i
\]

\subsection*{Constraints}

\begin{align*}
    & \sum_{i=1}^{N} x_i \leq \text{max\_cpu} & \text{(CPU Constraint)} \\
    & \sum_{i=1}^{N} \text{disk\_drives}[i] \cdot x_i \leq \text{max\_disk} & \text{(Disk Drive Constraint)} \\
    & \sum_{i=1}^{N} \text{256K\_boards}[i] \cdot x_i + \sum_{i=1}^{N} y_i \cdot \text{alt\_compatible}[i] \leq \text{max\_mem} & \text{(Memory Board Constraint)} \\
    & x_i \geq \text{preorder}[i] & \text{(Preorder Fulfillment)} \\
    & x_i \leq \text{demand}[i] & \text{(Individual Demand)} \\
    & x_i \leq \text{demand\_GP} & \text{(GP Family Demand)} \text{ if } \text{is\_workstation}[i] = \text{false} \\
    & x_i \leq \text{demand\_WS} & \text{(WS Family Demand)} \text{ if } \text{is\_workstation}[i] = \text{true} \\
    & x_i \geq 0, \quad y_i \geq 0 \quad \forall i & \text{(Non-negativity)}
\end{align*}

\subsection*{Output}

The output will include:
\begin{itemize}
    \item A list of systems produced, detailing the number produced, total 256K boards used, total alternative boards used, and total disk drives used.
    \item The total profit calculated from the above model.
\end{itemize}

\end{document}