\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for DEC Production Optimization}

\subsection*{Variables}
Let \( x_i \) be the number of systems produced of type \( i \) where \( i = 1, \ldots, N \).

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{is\_workstation}_i \): boolean indicating if system \( i \) is a workstation.
    \item \( \text{price}_i \): price of system \( i \).
    \item \( \text{disk}_i \): average disk drives requested for system \( i \).
    \item \( \text{mem}_i \): average 256K memory boards used for system \( i \).
    \item \( \text{max\_cpu} \): maximum number of CPUs available.
    \item \( \text{min\_disk}, \text{max\_disk} \): range of disk drives available.
    \item \( \text{min\_mem}, \text{max\_mem} \): range of 256K memory boards available.
    \item \( \text{demand}_i \): maximum demand for system \( i \).
    \item \( \text{demand\_GP} \): maximum demand for the GP family.
    \item \( \text{demand\_WS} \): maximum demand for the WS family.
    \item \( \text{preorder}_i \): preorder quantity for system \( i \).
    \item \( \text{alt\_mem} \): alternative memory boards available.
    \item \( \text{alt\_compatible}_i \): boolean indicating if system \( i \) is compatible with alternative memory boards.
\end{itemize}

\subsection*{Objective Function}
Maximize the profit:
\[
\text{Profit} = \sum_{i=1}^{N} (\text{price}_i \cdot x_i) - \text{Cost}
\]

\subsection*{Constraints}
1. CPU constraints:
\[
\sum_{i=1}^{N} x_i \leq \text{max\_cpu}
\]

2. Disk drive constraints:
\[
\sum_{i=1}^{N} \text{disk}_i \cdot x_i \geq \text{min\_disk} \quad \text{and} \quad \sum_{i=1}^{N} \text{disk}_i \cdot x_i \leq \text{max\_disk}
\]

3. Memory board constraints:
\[
\sum_{i=1}^{N} \text{mem}_i \cdot x_i \geq \text{min\_mem} \quad \text{and} \quad \sum_{i=1}^{N} \text{mem}_i \cdot x_i \leq \text{max\_mem}
\]

4. Demand constraints for each system \( i \):
\[
x_i \leq \text{demand}_i \quad \forall i
\]

5. Demand constraints for GP and WS families:
\[
\sum_{i: \text{is\_workstation}_i} x_i \leq \text{demand\_WS}
\]
\[
\sum_{i: \neg \text{is\_workstation}_i} x_i \leq \text{demand\_GP}
\]

6. Preorder fulfillment:
\[
x_i \geq \text{preorder}_i \quad \forall i
\]

7. Alternative memory boards usage:
\[
\sum_{i} \text{alt\_compatible}_i \cdot x_i \leq \text{alt\_mem}
\]

\subsection*{Output Information}
\begin{itemize}
    \item "system\_output": List of systems produced along with their respective quantities and board usage.
    \item "profit": Total profit generated from the production.
\end{itemize}

\end{document}