\documentclass{article}
\usepackage{amsmath}
\begin{document}

\title{Linear Programming Model for Maximizing Net Income}
\author{}
\date{}
\maketitle

\section*{Variables}
Let:
\begin{itemize}
    \item \( P \) be the number of different products.
    \item \( x_i \) be the production quantity of the \( i \)-th product, for \( i = 1, \ldots, P \).
    \item \( u \) be a binary variable indicating the upgrade decision, where \( u = 1 \) if the company upgrades its machine capacity and \( u = 0 \) otherwise.
\end{itemize}

\section*{Parameters}
Given parameters are:
\begin{itemize}
    \item \( \text{cash} \): available cash.
    \item \( \text{hour}_i \): machine hours required for producing one unit of the \( i \)-th product.
    \item \( \text{cost}_i \): production cost per unit of the \( i \)-th product.
    \item \( \text{price}_i \): selling price per unit of the \( i \)-th product.
    \item \( \text{investPercentage}_i \): percentage of sales revenue that will be reinvested from the \( i \)-th product.
    \item \( \text{upgradeHours} \): additional machine hours available after upgrade.
    \item \( \text{upgradeCost} \): cost of upgrade.
    \item \( \text{availableHours} \): initial machine hours available in the current production period.
\end{itemize}

\section*{Objective Function}
Maximize the total net income:
\[
\text{Net Income} = \sum_{i=1}^{P} \left( \text{price}_i \cdot x_i - \text{cost}_i \cdot x_i - \text{investPercentage}_i \cdot \text{price}_i \cdot x_i \right) - u \cdot \text{upgradeCost}
\]

\section*{Constraints}
1. Cash constraint:
\[
\sum_{i=1}^{P} \text{cost}_i \cdot x_i + u \cdot \text{upgradeCost} \leq \text{cash}
\]

2. Machine hours constraint:
\[
\sum_{i=1}^{P} \text{hour}_i \cdot x_i \leq \text{availableHours} + u \cdot \text{upgradeHours}
\]

3. Non-negativity constraints:
\[
x_i \geq 0 \quad \text{for } i = 1, \ldots, P
\]

4. Upgrade decision constraint:
\[
u \in \{0, 1\}
\end{document}