\documentclass{article}
\usepackage{amsmath}

\begin{document}

\title{MILP Model for Network Intrusion Intervention}
\date{}
\maketitle

\section*{Model Parameters}

\begin{itemize}
    \item $N$: Number of clusters.
    \item $T_{i}^{\text{central, isolate}}$: Processing time to isolate the $i$-th cluster using central processing.
    \item $T_{i}^{\text{central, scan}}$: Processing time to scan the $i$-th cluster using central processing.
    \item $T_{i}^{\text{distributed, isolate}}$: Processing time to isolate the $i$-th cluster using distributed processing.
    \item $T_{i}^{\text{distributed, scan}}$: Processing time to scan the $i$-th cluster using distributed processing.
    \item $C^{\text{central}}$: Opportunity cost per hour for central processing.
    \item $C^{\text{distributed}}$: Opportunity cost per hour for distributed processing.
    \item $H^{\text{central}}_{\text{max}}$: Maximum hours available for central processing.
    \item $H^{\text{distributed}}_{\text{max}}$: Maximum hours available for distributed processing.
\end{itemize}

\section*{Decision Variables}

\begin{itemize}
    \item $x_{i}^{\text{central, isolate}}$: Binary variable, equals 1 if the $i$-th cluster is isolated using central processing, 0 otherwise.
    \item $x_{i}^{\text{central, scan}}$: Binary variable, equals 1 if the $i$-th cluster is scanned using central processing, 0 otherwise.
    \item $x_{i}^{\text{distributed, isolate}}$: Binary variable, equals 1 if the $i$-th cluster is isolated using distributed processing, 0 otherwise.
    \item $x_{i}^{\text{distributed, scan}}$: Binary variable, equals 1 if the $i$-th cluster is scanned using distributed processing, 0 otherwise.
\end{itemize}

\section*{Objective Function}

\[
\min \sum_{i=1}^{N} \left( C^{\text{central}} \cdot \left(T_{i}^{\text{central, isolate}} \cdot x_{i}^{\text{central, isolate}} + T_{i}^{\text{central, scan}} \cdot x_{i}^{\text{central, scan}}\right) + C^{\text{distributed}} \cdot \left(T_{i}^{\text{distributed, isolate}} \cdot x_{i}^{\text{distributed, isolate}} + T_{i}^{\text{distributed, scan}} \cdot x_{i}^{\text{distributed, scan}}\right) \right)
\]

\section*{Constraints}

\begin{align}
    & \sum_{i=1}^{N} \left(T_{i}^{\text{central, isolate}} \cdot x_{i}^{\text{central, isolate}} + T_{i}^{\text{central, scan}} \cdot x_{i}^{\text{central, scan}}\right) \leq H^{\text{central}}_{\text{max}} \\
    & \sum_{i=1}^{N} \left(T_{i}^{\text{distributed, isolate}} \cdot x_{i}^{\text{distributed, isolate}} + T_{i}^{\text{distributed, scan}} \cdot x_{i}^{\text{distributed, scan}}\right) \leq H^{\text{distributed}}_{\text{max}} \\
    & x_{i}^{\text{central, isolate}} + x_{i}^{\text{central, scan}} + x_{i}^{\text{distributed, isolate}} + x_{i}^{\text{distributed, scan}} = 1, \quad \forall i \in \{1, \ldots, N\}
\end{align}

\section*{Notes}

\begin{itemize}
    \item Constraint (1) ensures the total central processing time does not exceed the maximum hours allowed.
    \item Constraint (2) ensures the total distributed processing time does not exceed the maximum hours allowed.
    \item Constraint (3) ensures each cluster receives exactly one type of intervention using one method.
\end{itemize}

\end{document}