\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Maximizing Net Income}

\textbf{Parameters:}
\begin{itemize}
    \item Let \( P \) be the number of different products.
    \item Let \( \text{cash} \) be the available cash.
    \item Let \( \text{hour}_i \) be the machine hours required for product \( i \) where \( i \in \{1, 2, \ldots, P\} \).
    \item Let \( \text{cost}_i \) be the production cost per unit of product \( i \).
    \item Let \( \text{price}_i \) be the selling price per unit of product \( i \).
    \item Let \( \text{investPercentage}_i \) be the percentage of sales revenue from product \( i \) allocated for operations.
    \item Let \( \text{upgradeHours} \) be the additional machine hours available through upgrading.
    \item Let \( \text{upgradeCost} \) be the cost of upgrading the machine.
    \item Let \( \text{availableHours} \) be the current available machine hours.
\end{itemize}

\textbf{Decision Variables:}
\begin{itemize}
    \item Let \( x_i \) be the quantity produced of product \( i \).
    \item Let \( \text{upgrade} \in \{0, 1\} \) be a binary variable indicating whether the company chooses to upgrade its machine capacity (1 for yes, 0 for no).
\end{itemize}

\textbf{Objective Function:}
We aim to maximize the total net income given by:
\[
\max \quad \text{net\_income} = \sum_{i=1}^{P} \left( ( \text{price}_i - \text{cost}_i - \text{investPercentage}_i \cdot \text{price}_i ) \cdot x_i \right) - \text{upgradeCost} \cdot \text{upgrade}
\]

\textbf{Constraints:}
1. **Cash Constraint:**
\[
\sum_{i=1}^{P} \text{cost}_i \cdot x_i \leq \text{cash} - \text{investPercentage}_i \cdot \text{price}_i \cdot \sum_{i=1}^{P} x_i \cdot \text{upgrade}
\]

2. **Machine Hours Constraint:**
\[
\sum_{i=1}^{P} \text{hour}_i \cdot x_i \leq \text{availableHours} + \text{upgradeHours} \cdot \text{upgrade}
\]

3. **Non-negativity Constraints:**
\[
x_i \geq 0 \quad \forall i \in \{1, 2, \ldots, P\}
\]
\[
\text{upgrade} \in \{0, 1\}
\]

\textbf{Output Variables:}
\begin{itemize}
    \item The net income is given by \( \text{net\_income} \).
    \item The production quantities are given by \( x_i \) for \( i \in \{1, 2, \ldots, P\} \).
    \item The variable \( \text{upgrade} \) indicates whether an upgrade is performed or not.
\end{itemize}

\end{document}