\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model}

\textbf{Parameters:}
\begin{itemize}
    \item $price_{i,m}$: Price of oil $i$ in month $m$.
    \item $sell\_price$: Selling price of the final product per ton.
    \item $is\_vegetable_{i}$: Indicator variable for oil $i$, where 1 indicates vegetable oil and 0 indicates non-vegetable oil.
    \item $max\_veg$: Maximum tons of vegetable oils that can be refined per month.
    \item $max\_veg$: Maximum tons of non-vegetable oils that can be refined per month.
    \item $storage\_size$: Maximum storage capacity for each raw oil.
    \item $storage\_cost$: Cost of storage per ton per month.
    \item $max\_hardness$: Maximum allowable hardness of the final product.
    \item $min\_hardness$: Minimum allowable hardness of the final product.
    \item $hardness_{i}$: Hardness value of oil $i$.
    \item $init\_amount$: Initial amount of each type of raw oil in storage.
\end{itemize}

\textbf{Decision Variables:}
\begin{itemize}
    \item $buyquantity_{i,m}$: Amount of oil $i$ bought in month $m$.
    \item $refine_{i,m}$: Amount of oil $i$ refined in month $m$.
    \item $storage_{i,m}$: Amount of oil $i$ stored at the end of month $m$.
\end{itemize}

\textbf{Objective Function:}
\begin{align*}
\text{Maximize } Z = \sum_{m=1}^{M} \left( sell\_price \cdot \sum_{i=1}^{I} refine_{i,m} - \sum_{i=1}^{I} price_{i,m} \cdot buyquantity_{i,m} - storage\_cost \cdot \sum_{i=1}^{I} storage_{i,m} \right)
\end{align*}

\textbf{Subject to:}

\underline{Production Constraints:}
\begin{align*}
\sum_{i \,|\, is\_vegetable_i = 1} refine_{i,m} & \leq max\_veg & \forall m \\
\sum_{i \,|\, is\_vegetable_i = 0} refine_{i,m} & \leq max\_veg & \forall m 
\end{align*}

\underline{Storage Constraints:}
\begin{align*}
storage_{i,m} & \leq storage\_size & \forall i, m \\
storage_{i,m} & = storage_{i,m-1} + buyquantity_{i,m} - refine_{i,m} & \forall i, m \\
storage_{i,m} & = init\_amount & \forall i, m = M
\end{align*}

\underline{Hardness Constraints:}
\begin{align*}
\frac{\sum_{i=1}^{I} hardness_{i} \cdot refine_{i,m}}{\sum_{i=1}^{I} refine_{i,m}} & \leq max\_hardness & \forall m \\
\frac{\sum_{i=1}^{I} hardness_{i} \cdot refine_{i,m}}{\sum_{i=1}^{I} refine_{i,m}} & \geq min\_hardness & \forall m
\end{align*}

\underline{Non-negativity Constraints:}
\begin{align*}
buyquantity_{i,m} & \geq 0 & \forall i, m \\
refine_{i,m} & \geq 0 & \forall i, m \\
storage_{i,m} & \geq 0 & \forall i, m
\end{align*}

\end{document}