\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for Network Intervention Problem}

\subsection*{Sets and Indices}
\begin{itemize}
    \item Let \( N \) be the number of clusters in the network.
    \item Let \( i \) index the clusters, where \( i = 1, 2, \ldots, N \).
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{isolate\_central}_i \): Processing time to isolate cluster \( i \) centrally.
    \item \( \text{scan\_central}_i \): Processing time to scan cluster \( i \) centrally.
    \item \( \text{isolate\_distributed}_i \): Processing time to isolate cluster \( i \) using distributed processing.
    \item \( \text{scan\_distributed}_i \): Processing time to scan cluster \( i \) using distributed processing.
    \item \( \text{central\_cost} \): Opportunity cost per hour for central processing.
    \item \( \text{distributed\_cost} \): Opportunity cost per hour for distributed processing.
    \item \( \text{max\_central} \): Maximum available hours for central processing.
    \item \( \text{max\_distributed} \): Maximum available hours for distributed processing.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( x_{i,j,k} \): Binary variable, 1 if cluster \( i \) is processed with intervention \( j \) (where \( j \in \{\text{isolate, scan}\} \)) using method \( k \) (where \( k \in \{\text{central, distributed}\} \)), 0 otherwise.
\end{itemize}

\subsection*{Objective Function}
Minimize the total cost of interventions:
\[
\begin{align*}
\text{Minimize } & \sum_{i=1}^{N} \left( \text{central\_cost} \times (\text{isolate\_central}_i \times x_{i, \text{isolate}, \text{central}} + \text{scan\_central}_i \times x_{i, \text{scan}, \text{central}}) \right. \\
& \left. + \text{distributed\_cost} \times (\text{isolate\_distributed}_i \times x_{i, \text{isolate}, \text{distributed}} + \text{scan\_distributed}_i \times x_{i, \text{scan}, \text{distributed}}) \right)
\end{align*}
\]

\subsection*{Constraints}
\begin{itemize}
    \item Each cluster must be treated with one intervention type and one processing method:
    \[
    x_{i, \text{isolate}, \text{central}} + x_{i, \text{scan}, \text{central}} + x_{i, \text{isolate}, \text{distributed}} + x_{i, \text{scan}, \text{distributed}} = 1, \quad \forall i
    \]

    \item Central processing time limit:
    \[
    \sum_{i=1}^{N} (\text{isolate\_central}_i \times x_{i, \text{isolate}, \text{central}} + \text{scan\_central}_i \times x_{i, \text{scan}, \text{central}}) \leq \text{max\_central}
    \]

    \item Distributed processing time limit:
    \[
    \sum_{i=1}^{N} (\text{isolate\_distributed}_i \times x_{i, \text{isolate}, \text{distributed}} + \text{scan\_distributed}_i \times x_{i, \text{scan}, \text{distributed}}) \leq \text{max\_distributed}
    \]

    \item Binary constraints:
    \[
    x_{i, j, k} \in \{0, 1\}, \quad \forall i, j \in \{\text{isolate, scan}\}, k \in \{\text{central, distributed}\}
    \]
\end{itemize}

\end{document}