\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for MILP Problem}

\subsection*{Sets}
Let \( N \) be the total number of clusters.

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{isolate\_central}_{i} \): Processing time for isolating cluster \( i \) using central processing.
    \item \( \text{scan\_central}_{i} \): Processing time for scanning cluster \( i \) using central processing.
    \item \( \text{isolate\_distributed}_{i} \): Processing time for isolating cluster \( i \) using distributed processing.
    \item \( \text{scan\_distributed}_{i} \): Processing time for scanning cluster \( i \) using distributed processing.
    \item \( C_c \): Central processing cost per hour.
    \item \( C_d \): Distributed processing cost per hour.
    \item \( \text{max\_central} \): Maximum hours available for central processing.
    \item \( \text{max\_distributed} \): Maximum hours available for distributed processing.
\end{itemize}

\subsection*{Decision Variables}
Let \( x_{i,j,k} \) be a binary variable where:
\[
x_{i,j,k} = \begin{cases}
1 & \text{if intervention type } j \text{ (isolate or scan) is chosen for cluster } i \text{ with method } k \text{ (central or distributed)} \\
0 & \text{otherwise}
\end{cases}
\]
where \( j \in \{ \text{isolate}, \text{scan} \} \) and \( k \in \{ \text{central}, \text{distributed} \} \).

\subsection*{Objective Function}
Minimize the total cost:
\[
\text{Total Cost} = \sum_{i=1}^{N} \sum_{j \in \{ \text{isolate}, \text{scan} \}} \sum_{k \in \{ \text{central}, \text{distributed} \}} C_k \cdot x_{i,j,k} \cdot \text{processing\_time}_{i,j,k}
\]

\subsection*{Constraints}

\textbf{1. Processing Time Constraints:}
\begin{align*}
\sum_{j \in \{ \text{isolate}, \text{scan} \}} \sum_{k \in \{ \text{central} \}} \text{processing\_time}_{i,j,k} \cdot x_{i,j,k} & \leq \text{max\_central} \quad \forall i \\
\sum_{j \in \{ \text{isolate}, \text{scan} \}} \sum_{k \in \{ \text{distributed} \}} \text{processing\_time}_{i,j,k} \cdot x_{i,j,k} & \leq \text{max\_distributed} \quad \forall i
\end{align*}

\textbf{2. Intervention Type Consistency:}
\[
\sum_{j \in \{ \text{isolate}, \text{scan} \}} \sum_{k \in \{ \text{central}, \text{distributed} \}} x_{i,j,k} = 1 \quad \forall i
\]

\textbf{3. Binary Constraints:}
\[
x_{i,j,k} \in \{0, 1\} \quad \forall i, \forall j, \forall k
\]

\subsection*{Output}
\textbf{Interventions:}
\[
\text{interventions} = \{ (i, j, k, \text{amount}) \; \text{for} \; i \in 1, \ldots, N \}
\]

\textbf{Total Cost:}
\[
\text{total\_cost} = \text{Total Cost}
\]

\end{document}