\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for DEC System Production}

\subsection*{Sets}
\begin{itemize}
    \item Let \( N \) = number of different computer systems.
    \item Let \( i \in \{1, 2, \ldots, N\} \) denote each computer system.
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{is\_workstation}_i \): boolean indicating if system \( i \) is a workstation.
    \item \( \text{price}_i \): price of system \( i \) (in dollars).
    \item \( \text{disk\_drives}_i \): average number of disk drives requested by customers for system \( i \).
    \item \( \text{256K\_boards}_i \): average number of 256K memory boards used by system \( i \).
    \item \( \text{max\_cpu} \): maximum number of CPUs available.
    \item \( \text{min\_disk} \): minimum number of disk drives available.
    \item \( \text{max\_disk} \): maximum number of disk drives available.
    \item \( \text{min\_mem} \): minimum number of 256K memory boards available.
    \item \( \text{max\_mem} \): maximum number of 256K memory boards available.
    \item \( \text{demand}_i \): maximum demand for system \( i \).
    \item \( \text{demand\_GP} \): maximum demand for the whole GP family.
    \item \( \text{demand\_WS} \): maximum demand for the whole WS family.
    \item \( \text{preorder}_i \): preorder units for system \( i \).
    \item \( \text{alt\_mem} \): units of alternative memory board available.
    \item \( \text{alt\_compatible}_i \): boolean indicating if system \( i \) is compatible with alternative memory.
\end{itemize}

\subsection*{Decision Variables}
Let:
\[
x_i = \text{number of systems produced for system } i
\]
\[
y_i = \text{number of alternative memory boards used for system } i
\]

\subsection*{Objective Function}
Maximize profit:
\[
\text{Profit} = \sum_{i=1}^{N} (\text{price}_i \cdot x_i) - \text{cost\_of\_components}
\]

\subsection*{Constraints}
\begin{itemize}
    \item \text{CPU constraint:}
    \[
    \sum_{i=1}^{N} x_i \leq \text{max\_cpu}
    \]

    \item \text{Disk drives constraint:}
    \[
    \sum_{i=1}^{N} \text{disk\_drives}_i \cdot x_i \leq \text{max\_disk}
    \]
    
    \item \text{Memory boards constraints:}
    \[
    \sum_{i=1}^{N} \text{256K\_boards}_i \cdot x_i + \sum_{i=1}^{N} y_i \leq \text{max\_mem}
    \]
    \[
    \sum_{i=1}^{N} y_i \leq \text{alt\_mem}  \quad \text{(if } \text{alt\_compatible}_i \text{ is true)}
    \]

    \item \text{Demand constraints:}
    \[
    x_i \geq \text{preorder}_i \quad \forall i
    \]
    \[
    \sum_{i \in \text{GP}} x_i \leq \text{demand\_GP}
    \]
    \[
    \sum_{i \in \text{WS}} x_i \leq \text{demand\_WS}
    \]
    \[
    x_i \leq \text{demand}_i \quad \forall i
    \]

    \item \text{Non-negativity:}
    \[
    x_i \geq 0 \quad \forall i
    \]
    \[
    y_i \geq 0 \quad \forall i \text{ if } \text{alt\_compatible}_i = \text{true}
    \]
\end{itemize}

\end{document}