\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model}

\textbf{Decision Variables:}
\begin{itemize}
    \item Let \( x_i \) be the production quantity of the \( i \)-th product, where \( i = 1, 2, \ldots, P \).
    \item Let \( upgrade \) be a binary variable that indicates whether the company should upgrade its machine capacity (1 if upgrade is chosen, 0 otherwise).
\end{itemize}

\textbf{Parameters:}
\begin{itemize}
    \item \( cash \): Available cash for the production period.
    \item \( hour_i \): Machine hours required for one unit of the \( i \)-th product.
    \item \( cost_i \): Production cost per unit of the \( i \)-th product.
    \item \( price_i \): Selling price per unit of the \( i \)-th product.
    \item \( investPercentage_i \): Percentage of sales revenue reinvested from the \( i \)-th product.
    \item \( upgradeHours \): Additional machine hours gained from the upgrade.
    \item \( upgradeCost \): Cost for the machine upgrade.
    \item \( availableHours \): Available machine hours for production.
\end{itemize}

\textbf{Objective Function:}

Maximize total net income:
\[
Z = \sum_{i=1}^{P} \left( (price_i - cost_i) x_i - investPercentage_i \cdot price_i \cdot x_i \right) - upgradeCost \cdot upgrade
\]

\textbf{Constraints:}

1. Machine Hour Constraint:
\[
\sum_{i=1}^{P} hour_i \cdot x_i \leq availableHours + upgradeHours \cdot upgrade
\]

2. Cash Availability Constraint:
\[
\sum_{i=1}^{P} cost_i \cdot x_i \leq cash
\]

3. Non-negativity Constraints:
\[
x_i \geq 0 \quad \forall i = 1, 2, \ldots, P
\]
\[
upgrade \in \{0, 1\}
\]

\textbf{Output Variables:}
\begin{itemize}
    \item \( net\_income \): The total net income of the company.
    \item \( production \): The production quantities \( [production_i] \) for each product \( i \).
    \item \( upgrade \): Indicates if the company should upgrade its machine capacity (true/false).
\end{itemize}

\end{document}