\documentclass{article}
\usepackage{amsmath}
\begin{document}

\title{Linear Programming Model for Auto Parts Manufacturer}
\author{}
\date{}
\maketitle

\section*{Problem Definition}

Let \( P \) be the number of different parts produced and \( M \) be the number of different machines used. 

\subsection*{Parameters}

\begin{itemize}
    \item \( \text{time}_{m,p} \): Time required on machine \( m \) to produce a batch of part \( p \) (in hours).
    \item \( \text{cost}_{m} \): Cost per hour of using machine \( m \).
    \item \( \text{available}_{m} \): Total available hours for machine \( m \) per month.
    \item \( \text{price}_{p} \): Selling price per batch of part \( p \).
    \item \( \text{min\_batches}_{p} \): Minimum number of batches of part \( p \) that must be produced.
    \item \( \text{standard\_cost} \): Standard labor cost per hour.
    \item \( \text{overtime\_cost} \): Overtime labor cost per hour.
    \item \( \text{overtime\_hour} \): Number of hours at standard cost before overtime applies.
\end{itemize}

\subsection*{Decision Variables}

Let \( batches_{p} \) be the number of batches produced for part \( p \) each month.

\subsection*{Objective Function}

The objective is to maximize the total profit, defined as:

\[
\text{Maximize } Z = \sum_{p=1}^{P} \left( \text{price}_p \cdot batches_p \right) - \sum_{m=1}^{M} \left( \text{cost}_m \cdot \sum_{p=1}^{P} \text{time}_{m,p} \cdot batches_p \right) - \text{Labor\_Cost}
\]

where:

\[
\text{Labor\_Cost} =
\begin{cases} 
\text{standard\_cost} \cdot \text{total\_time} & \text{if } \text{total\_time} \leq \text{overtime\_hour} \\ 
\text{standard\_cost} \cdot \text{overtime\_hour} + \text{overtime\_cost} \cdot (\text{total\_time} - \text{overtime\_hour}) & \text{if } \text{total\_time} > \text{overtime\_hour} 
\end{cases}
\]

with \( \text{total\_time} = \sum_{m=1}^{M} \sum_{p=1}^{P} \text{time}_{m,p} \cdot batches_p \).

\subsection*{Constraints}

1. Machine availability constraints:
\[
\sum_{p=1}^{P} \text{time}_{m,p} \cdot batches_p \leq \text{available}_{m} \quad \forall m = 1, \ldots, M
\]

2. Minimum production requirements:
\[
batches_p \geq \text{min\_batches}_{p} \quad \forall p = 1, \ldots, P
\]

3. Non-negativity:
\[
batches_p \geq 0 \quad \forall p = 1, \ldots, P
\]

\end{document}