\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{MILP Model for Profit Maximization}

\subsection*{Sets and Indices}
\begin{itemize}
    \item Let \( N \) be the set of all product types, indexed by \( i \).
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{assemblyHour}_i \): Hours of assembly labor required for one unit of product \( i \).
    \item \( \text{testingHour}_i \): Hours of testing required for one unit of product \( i \).
    \item \( \text{materialCost}_i \): Cost of raw materials for one unit of product \( i \) in dollars.
    \item \( \text{price}_i \): Price of one unit of product \( i \) in dollars.
    \item \( \text{maxAssembly} \): Maximum regular assembly hours available per day.
    \item \( \text{maxTesting} \): Maximum testing hours available per day.
    \item \( \text{maxOvertimeAssembly} \): Maximum overtime assembly hours available per day.
    \item \( \text{overtimeAssemblyCost} \): Cost per overtime assembly hour in dollars.
    \item \( \text{materialDiscount} \): Discount percentage on raw materials if the total exceeds the threshold.
    \item \( \text{discountThreshold} \): Dollar amount threshold for receiving a raw material discount.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( x_i \): Number of units produced for product \( i \), \( x_i \geq 0 \).
    \item \( \text{overtimeAssembly} \): Number of overtime assembly hours scheduled, \( \text{overtimeAssembly} \geq 0 \) and \( \text{overtimeAssembly} \leq \text{maxOvertimeAssembly} \).
    \item \( y \): Binary variable indicating whether the raw material discount is applied (1 if discount is applied, 0 otherwise).
\end{itemize}

\subsection*{Objective Function}
Maximize the daily profit:
\[
\text{Maximize } \quad \sum_{i \in N} \text{price}_i \times x_i - (1 - \text{materialDiscount} \times y) \sum_{i \in N} \text{materialCost}_i \times x_i - \text{overtimeAssemblyCost} \times \text{overtimeAssembly}
\]

\subsection*{Constraints}
\begin{align}
    & \sum_{i \in N} \text{assemblyHour}_i \times x_i \leq \text{maxAssembly} + \text{overtimeAssembly} \\
    & \sum_{i \in N} \text{testingHour}_i \times x_i \leq \text{maxTesting} \\
    & \text{materialDiscount} \times \left(\sum_{i \in N} \text{materialCost}_i \times x_i - \text{discountThreshold}\right) \leq M \times y \quad (\text{Big-M constraint}) \\
    & \sum_{i \in N} \text{materialCost}_i \times x_i \geq \text{discountThreshold} \times y \\
    & x_i \geq 0, \quad \forall i \\
    & \text{overtimeAssembly} \geq 0 \\
    & y \in \{0, 1\}
\end{align}
where \( M \) is a sufficiently large constant.

\end{document}