\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Custom Tees Advertising Campaign}

\subsection*{Parameters}
\begin{itemize}
    \item Let \( A \) be the number of different ad types.
    \item Let \( \text{goal\_young} \) be the target clicks from visitors aged 18-25 (in thousands).
    \item Let \( \text{goal\_old} \) be the target clicks from visitors older than 25 (in thousands).
    \item Let \( \text{goal\_unique\_young} \) be the target unique clicks from visitors aged 18-25 (in thousands).
    \item Let \( \text{goal\_unique\_old} \) be the target unique clicks from visitors older than 25 (in thousands).
    \item Let \( \text{young\_click}_{a} \) be the percentage of clicks from age 18-25 for ad type \( a \).
    \item Let \( \text{old\_click}_{a} \) be the percentage of clicks from age 25+ for ad type \( a \).
    \item Let \( \text{cost}_{a} \) be the cost of ad type \( a \) per 1000 clicks.
    \item Let \( \text{max\_click}_{a} \) be the maximum allowable clicks for ad type \( a \) (in thousands).
    \item Let \( \text{unique\_click}_{a} \) be the percentage of unique visitors for ad type \( a \).
\end{itemize}

\subsection*{Decision Variables}
Let \( \text{clicks}_{a} \) represent the number of clicks purchased for ad type \( a \) (in thousands).

\subsection*{Objective Function}
Minimize the total cost:
\[
\text{Total Cost} = \sum_{a=1}^{A} \text{cost}_{a} \cdot \text{clicks}_{a}
\]

\subsection*{Constraints}

1. Total clicks for visitors aged 18-25:
\[
\sum_{a=1}^{A} \text{young\_click}_{a} \cdot \text{clicks}_{a} \geq \text{goal\_young}
\]

2. Total clicks for visitors older than 25:
\[
\sum_{a=1}^{A} \text{old\_click}_{a} \cdot \text{clicks}_{a} \geq \text{goal\_old}
\]

3. Unique clicks for visitors aged 18-25:
\[
\sum_{a=1}^{A} \text{unique\_click}_{a} \cdot \text{clicks}_{a} \geq \text{goal\_unique\_young}
\]

4. Unique clicks for visitors older than 25:
\[
\sum_{a=1}^{A} \text{unique\_click}_{a} \cdot \text{clicks}_{a} \geq \text{goal\_unique\_old}
\]

5. Maximum allowable clicks for each ad type:
\[
\text{clicks}_{a} \leq \text{max\_click}_{a}, \quad \forall a = 1, \ldots, A
\]

6. Non-negativity constraints:
\[
\text{clicks}_{a} \geq 0, \quad \forall a = 1, \ldots, A
\]

\subsection*{Output}
The solution will provide:
\begin{itemize}
    \item The number of clicks purchased for each ad type: \( \text{clicks}_{a} \) for \( a = 1, \ldots, A \).
    \item The total cost of the ad campaign: \( \text{total\_cost} \).
\end{itemize}

\end{document}