\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Stock Selling Problem}

Let:
\begin{itemize}
    \item \( N \): Number of different stocks.
    \item \( bought_i \): Number of shares bought of stock \( i \).
    \item \( buyPrice_i \): Price per share at which stock \( i \) was bought.
    \item \( currentPrice_i \): Current price per share of stock \( i \).
    \item \( futurePrice_i \): Expected future price per share of stock \( i \) in one year.
    \item \( transactionRate \): Transaction cost rate (percentage) when selling shares.
    \item \( taxRate \): Tax rate (percentage) on capital gains.
    \item \( K \): Desired amount of money to raise net of capital gains and transaction costs.
    \item \( sell_i \): Number of shares of stock \( i \) to sell.
\end{itemize}

\subsection*{Objective Function}
The objective is to maximize the expected value of the portfolio next year after selling shares. This can be represented as:

\[
\text{Maximize } Z = \sum_{i=1}^{N} futurePrice_i \cdot (bought_i - sell_i)
\]

\subsection*{Constraints}
1. The total net amount raised after selling shares must meet the desired amount \( K \):

\[
\sum_{i=1}^{N} \left( currentPrice_i \cdot sell_i \cdot (1 - \frac{transactionRate}{100}) - (sell_i \cdot (currentPrice_i - buyPrice_i) \cdot \frac{taxRate}{100}) \right) \geq K
\]

2. The number of shares sold cannot exceed the number of shares bought:

\[
sell_i \leq bought_i, \quad \forall i \in \{1, \ldots, N\}
\]

3. The number of shares sold must be non-negative:

\[
sell_i \geq 0, \quad \forall i \in \{1, \ldots, N\}
\]

\subsection*{Conclusion}
The final Linear Programming model can be summarized as follows:

\[
\begin{array}{ll}
\text{Maximize} & Z = \sum_{i=1}^{N} futurePrice_i \cdot (bought_i - sell_i) \\
\text{Subject to} & \sum_{i=1}^{N} \left( currentPrice_i \cdot sell_i \cdot (1 - \frac{transactionRate}{100}) - (sell_i \cdot (currentPrice_i - buyPrice_i) \cdot \frac{taxRate}{100}) \right) \geq K \\
& sell_i \leq bought_i, \quad \forall i \in \{1, \ldots, N\} \\
& sell_i \geq 0, \quad \forall i \in \{1, \ldots, N\}
\end{array}
\]

\end{document}