\documentclass{article}
\usepackage{amsmath}
\begin{document}

\title{Mathematical Model for Container Management at a Seaport}
\author{}
\date{}
\maketitle

\section*{Problem Definition}

Let \( T \) be the total number of months. We define the following variables and parameters:

\subsection*{Parameters}
\begin{itemize}
    \item \( demand_{t} \): Demand for containers by ships in month \( t \) (for \( t = 1, \ldots, T \)).
    \item \( unload\_cost_{t} \): Cost to unload a single container in month \( t \).
    \item \( unload\_capacity_{t} \): Maximum number of containers that can be unloaded in month \( t \).
    \item \( holding\_cost \): Cost to hold a container in the yard for one month.
    \item \( max\_container \): Maximum number of containers that can be stored in the yard at the end of any month.
    \item \( init\_container \): Initial number of containers in the yard at the start of month 1.
    \item \( num\_cranes \): Maximum number of cranes that can be rented each month.
    \item \( crane\_capacity \): Capacity of each crane in terms of containers loaded.
    \item \( crane\_cost \): Cost for renting one crane.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( amount_{t} \): Number of containers unloaded in month \( t \) (for \( t = 1, \ldots, T \)).
    \item \( crane_{t} \): Number of cranes rented in month \( t \) (for \( t = 1, \ldots, T \)).
    \item \( total\_cost \): Total cost incurred over the entire period.
\end{itemize}

\subsection*{Objective Function}
Minimize the total cost:
\[
total\_cost = \sum_{t=1}^{T} (unload\_cost_{t} \cdot amount_{t} + holding\_cost \cdot (C_{t-1} - demand_{t}) + crane\_cost \cdot crane_{t})
\]
Where \( C_{t} \) is the number of containers in the yard at the end of month \( t \).

\subsection*{Constraints}
\begin{align}
    & C_{t} = C_{t-1} + amount_{t} - demand_{t}, \quad \forall t = 1, \ldots, T \\
    & C_{t} \leq max\_container, \quad \forall t = 1, \ldots, T \\
    & C_{1} = init\_container \\
    & amount_{t} \leq unload\_capacity_{t}, \quad \forall t = 1, \ldots, T \\
    & amount_{t} \leq crane_{t} \cdot crane\_capacity, \quad \forall t = 1, \ldots, T \\
    & crane_{t} \leq num\_cranes, \quad \forall t = 1, \ldots, T \\
    & C_{T} = 0 \\
    & amount_{t} \geq 0, \quad crane_{t} \geq 0, \quad \forall t = 1, \ldots, T
\end{align}

\end{document}