\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Auto Parts Manufacturer}

\subsection*{Variables}
Let \( b_p \) be the number of batches produced for part \( p \) where \( p = 1, \ldots, P \).

\subsection*{Parameters}
\begin{itemize}
    \item \( time_{m,p} \): Time required on machine \( m \) to produce one batch of part \( p \) (hours).
    \item \( cost_m \): Cost per hour of using machine \( m \).
    \item \( available_m \): Total available hours of machine \( m \) per month.
    \item \( price_p \): Selling price per batch of part \( p \).
    \item \( min\_batches_p \): Minimum batches required for part \( p \) to fulfill a contract.
    \item \( standard\_cost \): Standard labor cost per hour.
    \item \( overtime\_cost \): Overtime labor cost per hour.
    \item \( overtime\_hour \): Number of hours before overtime starts.
    \item \( min\_profit \): Minimum profit required.
\end{itemize}

\subsection*{Objective Function}
Maximize the total profit:

\[
\text{maximize } Z = \sum_{p=1}^{P} (price_p \cdot b_p) - \sum_{m=1}^{M} \left( cost_m \cdot \left( \sum_{p=1}^{P} time_{m,p} \cdot b_p \right) + \text{Labor Cost} \right)
\]

where labor cost is calculated based on standard and overtime rates.

\subsection*{Constraints}

1. **Machine Availability:**
\[
\sum_{p=1}^{P} time_{m,p} \cdot b_p \leq available_m \quad \forall m = 1, \ldots, M
\]

2. **Minimum Batch Requirement:**
\[
b_p \geq min\_batches_p \quad \forall p = 1, \ldots, P
\]

3. **Desired Profit:**
\[
Z \geq min\_profit
\]

4. **Non-negativity:**
\[
b_p \geq 0 \quad \forall p = 1, \ldots, P
\]

\subsection*{Output}
\begin{itemize}
    \item \( b_p \): Number of batches produced for each part \( p \).
    \item \( total\_profit \): Total profit obtained for the month.
\end{itemize}

\end{document}