\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for DEC Production Problem}

\subsection*{Variables}
Let \( x_i \) be the number of systems produced for system \( i \) where \( i = 1, \ldots, N \).

Let \( m_i \) be the number of 256K memory boards used for system \( i \).

Let \( a_i \) be the number of alternative memory boards used for system \( i \).

Let \( d_i \) be the number of disk drives used for system \( i \).

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{is\_workstation}[i] \): indicates if system \( i \) is a workstation (true) or a general-purpose system (false).
    \item \( \text{price}[i] \): price of system \( i \).
    \item \( \text{disk\_drives}[i] \): average number of disk drives requested for system \( i \).
    \item \( \text{256K\_boards}[i] \): average number of 256K memory boards requested for system \( i \).
    \item \( \text{max\_cpu} \): maximum number of CPUs available.
    \item \( \text{min\_disk} \): minimum supply of disk drives.
    \item \( \text{max\_disk} \): maximum supply of disk drives.
    \item \( \text{min\_mem} \): minimum supply of 256K memory boards.
    \item \( \text{max\_mem} \): maximum supply of 256K memory boards.
    \item \( \text{demand}[i] \): maximum demand for system \( i \).
    \item \( \text{demand\_GP} \): maximum demand for the GP family.
    \item \( \text{demand\_WS} \): maximum demand for the WS family.
    \item \( \text{preorder}[i] \): pre-orders received for system \( i \).
    \item \( \text{alt\_mem} \): total units of alternative memory boards available.
    \item \( \text{alt\_compatible}[i] \): indicates if system \( i \) can use alternative memory boards.
\end{itemize}

\subsection*{Objective Function}
Maximize the total profit:
\[
\text{Profit} = \sum_{i=1}^{N} \left( \text{price}[i] \cdot x_i - \text{cost\_mem}[i] - \text{cost\_disk}[i] \right)
\]

\subsection*{Constraints}
\begin{align}
    & \sum_{i=1}^{N} x_i \leq \text{max\_cpu} \quad \text{(CPU constraint)} \\
    & \sum_{i=1}^{N} \text{disk\_drives}[i] \cdot x_i \geq \text{min\_disk} \\
    & \sum_{i=1}^{N} \text{disk\_drives}[i] \cdot x_i \leq \text{max\_disk} \\
    & \sum_{i=1}^{N} \text{256K\_boards}[i] \cdot x_i \geq \text{min\_mem} \\
    & \sum_{i=1}^{N} \text{256K\_boards}[i] \cdot x_i \leq \text{max\_mem} \\
    & x_i \geq \text{preorder}[i] \quad \text{(for all } i\text{)} \\
    & x_i \leq \text{demand}[i] \quad \text{(for all } i\text{)} \\
    & \sum_{\text{is\_workstation}[i] = \text{true}} x_i \leq \text{demand\_WS} \\
    & \sum_{\text{is\_workstation}[i] = \text{false}} x_i \leq \text{demand\_GP} \\
    & a_i \leq \text{alt\_mem} \quad \text{(if alt\_compatible[i] is true)} 
\end{align}

\end{document}