\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for DEC Production Optimization}

\subsection*{Parameters}

\begin{itemize}
    \item \(N\): Number of computer systems.
    \item \(is\_workstation_i\): Boolean indicating if system \(i\) is a workstation (WS).
    \item \(price_i\): Price of system \(i\).
    \item \(disk_i\): Average number of disk drives required for system \(i\).
    \item \(mem_i\): Number of 256K memory boards required for system \(i\).
    \item \(max\_cpu\): Maximum number of CPUs available for production.
    \item \(min\_disk\): Minimum supply of disk drives.
    \item \(max\_disk\): Maximum supply of disk drives.
    \item \(min\_mem\): Minimum supply of 256K memory boards.
    \item \(max\_mem\): Maximum supply of 256K memory boards.
    \item \(demand_i\): Maximum demand for system \(i\).
    \item \(demand\_GP\): Maximum demand for the GP family.
    \item \(demand\_WS\): Maximum demand for the WS family.
    \item \(preorder_i\): Preorders for system \(i\) that must be fulfilled.
    \item \(alt\_mem\): Number of alternative memory boards available.
    \item \(alt\_compatible_i\): Boolean indicating if system \(i\) can use alternative memory boards.
\end{itemize}

\subsection*{Decision Variables}

Let \(x_i\) be the number of system \(i\) produced. Define:
\begin{itemize}
    \item \(y_i\): Number of 256K memory boards used for system \(i\).
    \item \(z_i\): Number of alternative memory boards used for system \(i\).
    \item \(d_i\): Number of disk drives used for system \(i\).
\end{itemize}

\subsection*{Objective Function}

Maximize the profit:
\[
\text{Maximize } Z = \sum_{i=1}^{N} (price_i \cdot x_i) - \text{cost\_of\_boards} - \text{cost\_of\_drives}
\]

\subsection*{Constraints}

1. CPU constraint:
\[
\sum_{i=1}^{N} x_i \leq max\_cpu
\]

2. Disk drives constraints:
\[
\sum_{i=1}^{N} d_i \cdot x_i \in [min\_disk, max\_disk]
\]

3. Memory constraints:
\[
\sum_{i=1}^{N} mem_i \cdot x_i + z_i \leq max\_mem
\]
\[
z_i \leq alt\_mem \text{ for } alt\_compatible_i = \text{true}
\]

4. Demand constraints for systems:
\[
preorder_i + x_i \leq demand_i \quad \forall i
\]

5. GP Family Demand Constraint:
\[
\sum_{i: is\_workstation_i = \text{false}} x_i \leq demand\_GP
\]

6. WS Family Demand Constraint:
\[
\sum_{i: is\_workstation_i = \text{true}} x_i \leq demand\_WS
\]

\subsection*{Output}

The output will be given in a JSON format:
\[
\{
    "system\_output": [
        \{
            "num\_produced": x_i,
            "total\_256K\_boards\_used": mem\_used_i,
            "total\_alt\_boards\_used": alt\_used_i,
            "total\_disk\_drives\_used": disk\_used_i
        \} \text{ for } i = 1, \ldots, T
    ],
    "profit": Z
\}
\]

\end{document}