\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for Network Intrusion Intervention}

\textbf{Sets:}
\begin{itemize}
    \item \( N = \{1, 2, \ldots, n\} \): set of clusters.
\end{itemize}

\textbf{Parameters:}
\begin{itemize}
    \item \( \text{isolate\_central}_i \): processing time to isolate cluster \( i \) centrally.
    \item \( \text{scan\_central}_i \): processing time to scan cluster \( i \) centrally.
    \item \( \text{isolate\_distributed}_i \): processing time to isolate cluster \( i \) distributedly.
    \item \( \text{scan\_distributed}_i \): processing time to scan cluster \( i \) distributedly.
    \item \( \text{central\_cost} \): opportunity cost per hour for central processing.
    \item \( \text{distributed\_cost} \): opportunity cost per hour for distributed processing.
    \item \( \text{max\_central} \): maximum hours available for central processing.
    \item \( \text{max\_distributed} \): maximum hours available for distributed processing.
\end{itemize}

\textbf{Decision Variables:}
\begin{itemize}
    \item \( x_{i}^{\text{isolate, central}} \): binary variable, 1 if cluster \( i \) is isolated centrally, 0 otherwise.
    \item \( x_{i}^{\text{scan, central}} \): binary variable, 1 if cluster \( i \) is scanned centrally, 0 otherwise.
    \item \( x_{i}^{\text{isolate, distributed}} \): binary variable, 1 if cluster \( i \) is isolated distributedly, 0 otherwise.
    \item \( x_{i}^{\text{scan, distributed}} \): binary variable, 1 if cluster \( i \) is scanned distributedly, 0 otherwise.
\end{itemize}

\textbf{Objective:}

Minimize the total cost of interventions:
\[
\text{Minimize } \sum_{i \in N} \left( \text{central\_cost} \left( \text{isolate\_central}_i \cdot x_{i}^{\text{isolate, central}} + \text{scan\_central}_i \cdot x_{i}^{\text{scan, central}} \right) + \text{distributed\_cost} \left( \text{isolate\_distributed}_i \cdot x_{i}^{\text{isolate, distributed}} + \text{scan\_distributed}_i \cdot x_{i}^{\text{scan, distributed}} \right) \right)
\]

\textbf{Constraints:}
\begin{itemize}
    \item Each cluster must be treated with one type of intervention:
    \[
    x_{i}^{\text{isolate, central}} + x_{i}^{\text{scan, central}} + x_{i}^{\text{isolate, distributed}} + x_{i}^{\text{scan, distributed}} = 1, \quad \forall i \in N
    \]
    
    \item Total central processing time should not exceed maximum available hours:
    \[
    \sum_{i \in N} \left( \text{isolate\_central}_i \cdot x_{i}^{\text{isolate, central}} + \text{scan\_central}_i \cdot x_{i}^{\text{scan, central}} \right) \leq \text{max\_central}
    \]
    
    \item Total distributed processing time should not exceed maximum available hours:
    \[
    \sum_{i \in N} \left( \text{isolate\_distributed}_i \cdot x_{i}^{\text{isolate, distributed}} + \text{scan\_distributed}_i \cdot x_{i}^{\text{scan, distributed}} \right) \leq \text{max\_distributed}
    \]
    
    \item Binary constraints:
    \[
    x_{i}^{\text{isolate, central}}, x_{i}^{\text{scan, central}}, x_{i}^{\text{isolate, distributed}}, x_{i}^{\text{scan, distributed}} \in \{0,1\}, \quad \forall i \in N
    \]
\end{itemize}

\end{document}