\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{MILP Model for Maximizing Daily Profit}

\textbf{Sets and Indices:}
\begin{itemize}
    \item Let \( i = 1, \ldots, N \) index the types of products.
\end{itemize}

\textbf{Parameters:}
\begin{itemize}
    \item \( \text{assemblyHour}_i \): Hours of assembly required for product \( i \).
    \item \( \text{testingHour}_i \): Hours of testing required for product \( i \).
    \item \( \text{materialCost}_i \): Material cost for product \( i \) in dollars.
    \item \( \text{price}_i \): Selling price for product \( i \) in dollars.
    \item \( \text{maxAssembly} \): Maximum assembly hours available per day.
    \item \( \text{maxTesting} \): Maximum testing hours available per day.
    \item \( \text{maxOvertimeAssembly} \): Maximum overtime assembly hours available.
    \item \( \text{overtimeAssemblyCost} \): Cost of overtime assembly per hour in dollars.
    \item \( \text{materialDiscount} \): Discount percentage on materials (between 0 and 100).
    \item \( \text{discountThreshold} \): Threshold for material discount in dollars.
\end{itemize}

\textbf{Decision Variables:}
\begin{itemize}
    \item \( x_i \): Number of units of product \( i \) produced (integer).
    \item \( y \): Number of overtime assembly hours used (integer).
    \item \( z \): Binary variable indicating whether discount on materials is applied.
\end{itemize}

\textbf{Objective:}
Maximize the daily profit:

\[
\text{Maximize} \quad \sum_{i=1}^{N} \left( \text{price}_i \cdot x_i \right) - \left( \sum_{i=1}^{N} \text{materialCost}_i \cdot x_i \cdot (1 - \text{materialDiscount} \cdot z / 100) \right) - \text{overtimeAssemblyCost} \cdot y
\]

\textbf{Constraints:}
\begin{align}
    &\sum_{i=1}^{N} \text{assemblyHour}_i \cdot x_i \leq \text{maxAssembly} + y \\
    &\sum_{i=1}^{N} \text{testingHour}_i \cdot x_i \leq \text{maxTesting} \\
    &y \leq \text{maxOvertimeAssembly} \\
    &\sum_{i=1}^{N} \text{materialCost}_i \cdot x_i \geq \text{discountThreshold} \cdot z \\
    &x_i \geq 0, \quad x_i \in \mathbb{Z} \quad \forall i \\
    &y \geq 0, \quad y \in \mathbb{Z} \\
    &z \in \{0, 1\}
\end{align}

\textbf{Output:}
\begin{itemize}
    \item \text{dailyProfit}: The optimal daily profit.
    \item \text{unitsProduced}_i: The optimal number of units of product \( i \) to produce.
    \item \text{overtimeAssembly}: The optimal number of hours of overtime assembly.
    \item \text{materialBought}: The total cost spent on materials, considering discounts.
\end{itemize}

\end{document}