\documentclass{article}
\usepackage{amsmath}
\begin{document}

\title{Linear Programming Model for Warehouse Operations}
\author{}
\date{}
\maketitle

\section*{Problem Definition}

We consider a warehouse that operates for \(N\) periods, aiming to maximize profit through the buying and selling of a commodity while respecting certain constraints.

Let:
\begin{itemize}
    \item \(C\): the fixed capacity of the warehouse,
    \item \(h\): the holding cost per unit per period,
    \item \(p_n\): the selling price of the commodity in period \(n\),
    \item \(c_n\): the cost of the commodity for purchase in period \(n\),
    \item \(b_n\): the quantity bought in period \(n\),
    \item \(s_n\): the quantity sold in period \(n\),
    \item \(x_n\): the stock remaining in the warehouse at the end of period \(n\).
\end{itemize}

\section*{Objective Function}

The objective is to maximize the total profit over \(N\) periods, which can be expressed as:

\[
\text{Maximize } Z = \sum_{n=1}^{N} (p_n s_n - c_n b_n - h x_n)
\]

\section*{Constraints}

1. **Capacity Constraint**: The stock at any time must not exceed the warehouse capacity.

\[
x_n = x_{n-1} + b_n - s_n \quad \forall n \in \{1, \ldots, N\}
\]

\[
x_n \leq C \quad \forall n \in \{1, \ldots, N\}
\]

2. **Non-negativity Constraints**: The quantities bought, sold, and stock must be non-negative.

\[
b_n \geq 0, \quad s_n \geq 0, \quad x_n \geq 0 \quad \forall n \in \{1, \ldots, N\}
\]

3. **Initial Condition**: The warehouse starts empty.

\[
x_0 = 0
\]

4. **Final Condition**: The warehouse must be empty at the end of the last period.

\[
x_N = 0
\]

\section*{Output Variables}

The solution will yield the following output:

\begin{itemize}
    \item \(b_n\): the amount bought in each period.
    \item \(s_n\): the amount sold in each period.
    \item \(x_n\): the stock at the end of each period, excluding the initial stock.
\end{itemize}

\section*{Output Format}

The results are provided in the following format:

\[
\{
    \text{"buyquantity"}: [b_1, b_2, \ldots, b_N],
    \text{"sellquantity"}: [s_1, s_2, \ldots, s_N],
    \text{"stock"}: [x_1, x_2, \ldots, x_N]
\}
\]

\end{document}