\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Custom Tees Advertising Campaign}

\subsection*{Parameters}
\begin{itemize}
    \item Let \( A \) be the number of different ad types.
    \item Let \( \text{goal\_young} \) be the target number of clicks from visitors aged 18-25 (in thousands).
    \item Let \( \text{goal\_old} \) be the target number of clicks from visitors older than 25 (in thousands).
    \item Let \( \text{goal\_unique\_young} \) be the target number of unique clicks from visitors aged 18-25 (in thousands).
    \item Let \( \text{goal\_unique\_old} \) be the target number of unique clicks from visitors older than 25 (in thousands).
    \item Let \( \text{young\_click}_{a} \) be the estimated percentage of clicks from the 18-25 age range for ad type \( a \).
    \item Let \( \text{old\_click}_{a} \) be the estimated percentage of clicks from older visitors for ad type \( a \).
    \item Let \( \text{cost}_{a} \) be the cost per 1000 clicks for ad type \( a \).
    \item Let \( \text{max\_click}_{a} \) be the maximum allowable clicks (in thousands) for ad type \( a \).
    \item Let \( \text{unique\_click}_{a} \) be the estimated percentage of unique visitors for each ad type \( a \).
    \item Let \( \text{budget} \) be the total advertising budget.
\end{itemize}

\subsection*{Decision Variables}
Let \( \text{clicks}_{a} \) be the number of clicks purchased for ad type \( a \) (in thousands).

\subsection*{Objective Function}
Maximize the total number of unique clicks:
\[
\text{Maximize } Z = \sum_{a=1}^{A} \text{unique\_click}_{a} \cdot \text{clicks}_a
\]

\subsection*{Constraints}
1. Total budget constraint:
\[
\sum_{a=1}^{A} \text{cost}_{a} \cdot \text{clicks}_a \leq \text{budget}
\]
2. Young clicks constraint:
\[
\sum_{a=1}^{A} \text{young\_click}_{a} \cdot \text{clicks}_a \geq \text{goal\_young}
\]
3. Old clicks constraint:
\[
\sum_{a=1}^{A} \text{old\_click}_{a} \cdot \text{clicks}_a \geq \text{goal\_old}
\]
4. Unique clicks constraints for the young demographic:
\[
\sum_{a=1}^{A} \text{unique\_click}_{a} \cdot \text{clicks}_a \geq \text{goal\_unique\_young}
\]
5. Unique clicks constraints for the old demographic:
\[
\sum_{a=1}^{A} \text{unique\_click}_{a} \cdot \text{clicks}_a \geq \text{goal\_unique\_old}
\]
6. Maximum clicks constraint:
\[
\text{clicks}_{a} \leq \text{max\_click}_{a}, \quad \forall a = 1, \ldots, A
\]
7. Non-negativity constraints:
\[
\text{clicks}_{a} \geq 0, \quad \forall a = 1, \ldots, A
\]

\subsection*{Output}
The solution will provide:
\begin{itemize}
    \item The number of clicks purchased for each ad type: \( \text{clicks}_{a} \) (in thousands).
    \item The total number of unique clicks: \( \text{total\_unique\_clicks} \).
\end{itemize}
\end{document}