\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Oil Refining and Blending}

\subsection*{Variables}

Let:
\begin{itemize}
    \item $buyquantity_{i,m}$ be the amount of oil $i$ bought in month $m$.
    \item $refine_{i,m}$ be the amount of oil $i$ refined in month $m$.
    \item $storage_{i,m}$ be the amount of oil $i$ stored at the end of month $m$.
\end{itemize}

\subsection*{Parameters}

Let:
\begin{itemize}
    \item $price_{i,m}$ be the buying price of oil $i$ in month $m$.
    \item $sell\_price$ be the selling price per ton of the final product.
    \item $is\_vegetable_{i}$ be a binary variable indicating whether oil $i$ is vegetable (1) or non-vegetable (0).
    \item $max\_veg$ be the maximum tons of vegetable oil that can be refined per month.
    \item $max\_veg$ be the maximum tons of non-vegetable oil that can be refined per month.
    \item $storage\_size$ be the maximum storage size for each oil.
    \item $storage\_cost$ be the cost of storing one ton of oil per month.
    \item $max\_hardness$ be the maximum allowable hardness of the final product.
    \item $min\_hardness$ be the minimum allowable hardness of the final product.
    \item $hardness_{i}$ be the hardness of oil $i$.
    \item $init\_amount$ be the initial amount of each type of oil in storage.
\end{itemize}

\subsection*{Objective Function}

The objective is to maximize profit defined as:

\[
\text{Maximize } Z = \sum_{m=1}^{M} \left( sell\_price \cdot \sum_{i=1}^{I} refine_{i,m} - \sum_{i=1}^{I} price_{i,m} \cdot buyquantity_{i,m} - storage\_cost \cdot \sum_{i=1}^{I} storage_{i,m} \right)
\]

\subsection*{Constraints}

1. **Refining Constraints:**
   \[
   \sum_{i=1}^{I} refine_{i,m} \leq max\_veg \quad \text{if } is\_vegetable_{i}=1
   \]
   \[
   \sum_{i=1}^{I} refine_{i,m} \leq max\_veg \quad \text{if } is\_vegetable_{i}=0
   \]

2. **Storage Constraints:**
   \[
   storage_{i,m} \leq storage\_size \quad \forall i,m
   \]

3. **Initial Storage Condition:**
   \[
   storage_{i,0} = init\_amount \quad \forall i
   \]

4. **Final Storage Condition:**
   \[
   storage_{i,M} = init\_amount \quad \forall i
   \]

5. **Balance Constraints:**
   \[
   storage_{i,m} = storage_{i,m-1} + buyquantity_{i,m} - refine_{i,m} \quad \forall i, m
   \]

6. **Hardness Constraints:**
   Let $H_m$ be the hardness of the final product in month $m$:
   \[
   H_m = \frac{\sum_{i=1}^{I} (hardness_{i} \cdot refine_{i,m})}{\sum_{i=1}^{I} refine_{i,m}} \quad \forall m
   \]
   \[
   min\_hardness \leq H_m \leq max\_hardness \quad \forall m
   \]

7. **Non-negativity Constraints:**
   \[
   buyquantity_{i,m} \geq 0, \quad refine_{i,m} \geq 0, \quad storage_{i,m} \geq 0 \quad \forall i, m
   \]

\end{document}