\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mixed Integer Linear Programming (MILP) Model for Network Intervention}

\subsection*{Sets}
\begin{itemize}
    \item Let \( N \) be the number of clusters.
    \end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{isolate\_central}_i \): Processing time for isolating cluster \( i \) using central intervention.
    \item \( \text{scan\_central}_i \): Processing time for scanning cluster \( i \) using central intervention.
    \item \( \text{isolate\_distributed}_i \): Processing time for isolating cluster \( i \) using distributed intervention.
    \item \( \text{scan\_distributed}_i \): Processing time for scanning cluster \( i \) using distributed intervention.
    \item \( \text{central\_cost} \): Cost per hour for central processing.
    \item \( \text{distributed\_cost} \): Cost per hour for distributed processing.
    \item \( \text{max\_central} \): Maximum hours available for central processing.
    \item \( \text{max\_distributed} \): Maximum hours available for distributed processing.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( x_{i,j} \): Binary variable where \( x_{i,j} = 1 \) if cluster \( i \) uses intervention type \( j \) (where \( j \in \{ \text{isolate}, \text{scan} \} \)) and processing method (central or distributed), and \( 0 \) otherwise.
    \item \( y_{c} \): Continuous variable representing the total time spent on central processing.
    \item \( y_{d} \): Continuous variable representing the total time spent on distributed processing.
\end{itemize}

\subsection*{Objective Function}
Minimize the total cost:
\[
\text{Minimize } Z = \sum_{i=1}^{N} \left( \text{central\_cost} \cdot x_{i,\text{isolate}} \cdot \text{isolate\_central}_i + \text{central\_cost} \cdot x_{i,\text{scan}} \cdot \text{scan\_central}_i + \text{distributed\_cost} \cdot (1 - x_{i,\text{isolate}}) \cdot \text{isolate\_distributed}_i + \text{distributed\_cost} \cdot (1 - x_{i,\text{scan}}) \cdot \text{scan\_distributed}_i \right)
\]

\subsection*{Constraints}
\begin{itemize}
    \item Time constraints for central processing:
    \[
    \sum_{i=1}^{N} \left( x_{i,\text{isolate}} \cdot \text{isolate\_central}_i + x_{i,\text{scan}} \cdot \text{scan\_central}_i \right) \leq \text{max\_central}
    \]
    
    \item Time constraints for distributed processing:
    \[
    \sum_{i=1}^{N} \left( (1 - x_{i,\text{isolate}}) \cdot \text{isolate\_distributed}_i + (1 - x_{i,\text{scan}}) \cdot \text{scan\_distributed}_i \right) \leq \text{max\_distributed}
    \]

    \item Ensure each cluster has exactly one intervention type:
    \[
    x_{i,\text{isolate}} + x_{i,\text{scan}} = 1, \quad \forall i = 1, \ldots, N
    \]

\end{itemize}

\subsection*{Output}
\begin{itemize}
    \item Interventions:
    \begin{itemize}
        \item For each cluster \( i \):
        \[
        \begin{align*}
        \text{intervention}_{i} = \{ \text{cluster\_id}: i, \text{type}: \text{isolate or scan}, \text{method}: \text{central or distributed}, \text{amount}: x_{i,j} \} 
        \end{align*}
        \end{itemize}
    \item Total cost:
    \[
    \text{total\_cost} = Z
    \]
\end{itemize}

\end{document}