\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model}

Let:
\begin{itemize}
    \item \( P \) be the number of different products.
    \item \( production_i \) be the quantity produced of product \( i \) (for \( i=1, \ldots, P \)).
    \item \( upgrade \) be a binary variable indicating whether to upgrade machine capacity (1 for yes, 0 for no).
\end{itemize}

Define the parameters:
\begin{itemize}
    \item \( cash \): available cash.
    \item \( hour_i \): machine hours required for each unit of product \( i \).
    \item \( cost_i \): production cost per unit of product \( i \).
    \item \( price_i \): selling price per unit of product \( i \).
    \item \( investPercentage_i \): percentage of sales revenue from product \( i \) that will be reinvested.
    \item \( upgradeHours \): additional machine hours available after upgrades.
    \item \( upgradeCost \): cost incurred for upgrading the machine.
    \item \( availableHours \): initial machine hours available.
\end{itemize}

\subsection*{Objective Function}
We aim to maximize the total net income:

\[
\text{Maximize } Z = \sum_{i=1}^{P} \left( (price_i \times production_i) - (cost_i \times production_i) - (investPercentage_i \times price_i \times production_i) \right)
\]

\subsection*{Constraints}

1. **Machine Capacity Constraint**:
\[
\sum_{i=1}^{P} hour_i \times production_i \leq availableHours + (upgrade \times upgradeHours)
\]

2. **Cash Availability Constraint**:
\[
\sum_{i=1}^{P} cost_i \times production_i + upgrade \times upgradeCost \leq cash
\]

3. **Non-negativity Constraints**:
\[
production_i \geq 0 \quad \text{for } i=1, \ldots, P
\]
\[
upgrade \in \{0, 1\}
\]

\subsection*{Outputs}
The results will include:
\begin{itemize}
    \item \( net\_income \): total net income of the company.
    \item \( production \): array of production quantities \( [production_1, production_2, \ldots, production_P] \).
    \item \( upgrade \): a boolean variable indicating whether to upgrade the machine capacity.
\end{itemize}

\end{document}