\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for DEC's Production Optimization Problem}

\subsection*{Sets}
\begin{itemize}
    \item \( i \in \{1, 2, \ldots, N\} \): represents different system types.
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( is\_workstation[i] \): boolean indicating if system \( i \) is a workstation (WS).
    \item \( price[i] \): price of system \( i \).
    \item \( disk[i] \): average number of disk drives requested for system \( i \).
    \item \( mem[i] \): average number of 256K memory boards requested for system \( i \).
    \item \( max\_cpu \): maximum number of CPUs available.
    \item \( min\_disk \): minimum number of disk drives available.
    \item \( max\_disk \): maximum number of disk drives available.
    \item \( min\_mem \): minimum number of 256K memory boards available.
    \item \( max\_mem \): maximum number of 256K memory boards available.
    \item \( demand[i] \): estimated maximum demand for system \( i \).
    \item \( demand\_GP \): estimated maximum demand for the general-purpose (GP) family.
    \item \( demand\_WS \): estimated maximum demand for the workstation (WS) family.
    \item \( preorder[i] \): preorders received for system \( i \).
    \item \( alt\_mem \): available alternative memory boards.
    \item \( alt\_compatible[i] \): boolean indicating if alternative memory can be used for system \( i \).
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( x[i] \): number of systems of type \( i \) to produce, \( x[i] \geq 0 \).
    \item \( alt[i] \): number of alternative memory boards used for system \( i \), \( alt[i] \geq 0 \).
\end{itemize}

\subsection*{Objective Function}
Maximize total profit:
\[
\text{Max } Z = \sum_{i=1}^{N} \left( price[i] \cdot x[i] - (mem[i] \cdot 256K\_cost + disk[i] \cdot disk\_cost + alt[i] \cdot alt\_cost) \right)
\]

\subsection*{Constraints}
\begin{align}
    \sum_{i=1}^{N} x[i] & \leq max\_cpu \quad \text{(CPU constraint)} \\
    \sum_{i=1}^{N} disk[i] \cdot x[i] & \geq min\_disk \quad \text{(Disk supply constraint)} \\
    \sum_{i=1}^{N} disk[i] \cdot x[i] & \leq max\_disk \quad \text{(Disk supply constraint)} \\
    \sum_{i=1}^{N} mem[i] \cdot x[i] & \geq min\_mem \quad \text{(Memory supply constraint)} \\
    \sum_{i=1}^{N} mem[i] \cdot x[i] & \leq max\_mem \quad \text{(Memory supply constraint)} \\
    x[i] & \leq demand[i] \quad \forall i \quad \text{(Demand constraint for each system)} \\
    \sum_{i \text{ s.t. } is\_workstation[i]} x[i] & \leq demand\_WS \quad \text{(Total WS demand constraint)} \\
    \sum_{i \text{ s.t. } \neg is\_workstation[i]} x[i] & \leq demand\_GP \quad \text{(Total GP demand constraint)} \\
    x[i] & \geq preorder[i] \quad \forall i \quad \text{(Preorder constraint)} \\
    alt[i] & \leq alt\_mem \quad \text{(Alternative memory board constraint)} \\
    alt[i] & \leq alt\_compatible[i] \cdot  x[i] \quad \forall i \quad \text{(Alternative memory compatibility)}
\end{align}

\subsection*{Output}
The output will be in the following JSON format:
\begin{verbatim}
{
    "system_output": [
        {
            "num_produced": x[i],
            "total_256K_boards_used": mem[i] \cdot x[i],
            "total_alt_boards_used": alt[i],
            "total_disk_drives_used": disk[i] \cdot x[i]
        }
        for i in 1, ..., N
    ],
    "profit": Z
}
\end{verbatim}

\end{document}