\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mixed Integer Linear Programming Model}

\textbf{Variables:}
\begin{itemize}
    \item Let $x_i$ be the number of units of product $i$ produced, for $i = 1, \ldots, N$.
    \item Let $o$ be the number of hours of overtime assembly labor scheduled.
\end{itemize}

\textbf{Parameters:}
\begin{itemize}
    \item $assemblyHour_i$: hours of assembly labor required for product $i$.
    \item $testingHour_i$: hours of testing required for product $i$.
    \item $materialCost_i$: cost of raw materials for product $i$.
    \item $maxAssembly$: maximum available assembly hours per day.
    \item $maxTesting$: maximum available testing hours per day.
    \item $price_i$: selling price of product $i$.
    \item $maxOvertimeAssembly$: maximum available overtime assembly hours.
    \item $overtimeAssemblyCost$: cost per hour of overtime assembly labor.
    \item $materialDiscount$: percentage discount on raw materials.
    \item $discountThreshold$: minimum amount for discount eligibility.
\end{itemize}

\textbf{Objective Function:}
\begin{align*}
\text{Maximize } Z &= \sum_{i=1}^{N} (price_i \cdot x_i) - \left( \sum_{i=1}^{N} (materialCost_i \cdot x_i) \cdot (1 - \frac{materialDiscount}{100}) + overtimeAssemblyCost \cdot o \right)
\end{align*}

\textbf{Constraints:}
\begin{align*}
\sum_{i=1}^{N} (assemblyHour_i \cdot x_i) + o &\leq maxAssembly + maxOvertimeAssembly \\
\sum_{i=1}^{N} (testingHour_i \cdot x_i) &\leq maxTesting \\
\sum_{i=1}^{N} (materialCost_i \cdot x_i) &\geq discountThreshold \\
x_i &\geq 0 \quad \text{(integer for all } i\text{)} \\
o &\geq 0 \quad \text{(non-negative)}
\end{align*}

\textbf{Output:}
\begin{itemize}
    \item $dailyProfit$: the maximum daily profit of the company.
    \item $unitsProduced$: the array of number of units produced for each product $i$.
    \item $overtimeAssembly$: the total hours of overtime assembly labor scheduled.
    \item $materialBought$: the total amount of raw materials bought.
\end{itemize}

\end{document}