\documentclass{article}
\usepackage{amsmath}
\begin{document}

% Sets and parameters
Let \( N \) be the number of Streets, and \( W \) be the number of Avenues. \\
Let \( \text{west\_time}_{n,w} \) be the time to move west from the intersection of \( w \)th Avenue and \( n \)th Street. \\
Let \( \text{north\_time}_{n,w} \) be the time to move north from the intersection of \( w \)th Avenue and \( n \)th Street. \\

% Decision variables
Define \( x_{n,w}^{west} \) as a binary variable that is 1 if moving west from intersection \((n, w)\), 0 otherwise. \\
Define \( x_{n,w}^{north} \) as a binary variable that is 1 if moving north from intersection \((n, w)\), 0 otherwise. \\

% Objective function
\textbf{Minimize:} 
\[
\text{Total time} = \sum_{n=1}^{N} \sum_{w=1}^{W-1} \text{west\_time}_{n,w} \cdot x_{n,w}^{west} + \sum_{n=1}^{N-1} \sum_{w=1}^{W} \text{north\_time}_{n,w} \cdot x_{n,w}^{north}
\]

% Constraints
\textbf{Subject to:}
\begin{align*}
1. & \quad \sum_{w=1}^{W-1} x_{1,w}^{west} + \sum_{n=1}^{N-1} x_{n,1}^{north} = m \\
2. & \quad \sum_{n=1}^{N} x_{n,W-1}^{west} + \sum_{w=1}^{W} x_{N-1,w}^{north} = m \\
3. & \quad \sum_{w=1}^{W-1} x_{n,w}^{west} + x_{n,1}^{north} \leq 1 \quad \text{for all } n \\
4. & \quad \sum_{n=1}^{N-1} x_{n,w}^{north} + x_{1,w}^{west} \leq 1 \quad \text{for all } w \\
5. & \quad x_{n,w}^{west}, x_{n,w}^{north} \in \{0, 1\} \quad \text{for all } n,w
\end{align*}

\textbf{Explanation:}
\begin{itemize}
    \item The objective is to minimize the total travel time by choosing optimal paths.
    \item The constraints ensure that the delivery person starts from the initial position and reaches the destination by moving only northward or westward per the defined path constraints.
    \item Each path from \( (n, w) \) involves a binary decision of moving either north or west.
\end{itemize}

\end{document}