\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for the Intrusion Intervention Problem}

\subsection*{Sets and Parameters}
\begin{itemize}
    \item Let \( N \) be the number of clusters.
    \item Let \( \text{isolate\_central}_i \) be the processing time for isolation intervention at cluster \( i \) using central processing.
    \item Let \( \text{scan\_central}_i \) be the processing time for scanning intervention at cluster \( i \) using central processing.
    \item Let \( \text{isolate\_distributed}_i \) be the processing time for isolation intervention at cluster \( i \) using distributed processing.
    \item Let \( \text{scan\_distributed}_i \) be the processing time for scanning intervention at cluster \( i \) using distributed processing.
    \item Let \( \text{central\_cost} \) be the cost of using central processing per hour.
    \item Let \( \text{distributed\_cost} \) be the cost of using distributed processing per hour.
    \item Let \( \text{max\_central} \) be the maximum number of hours available for central processing.
    \item Let \( \text{max\_distributed} \) be the maximum number of hours available for distributed processing.
\end{itemize}

\subsection*{Decision Variables}
Let \( x_{i,j,k} \) be a binary variable such that:
\[
x_{i,j,k} = 
\begin{cases} 
1 & \text{if intervention type } j \text{ (isolate or scan) is applied at cluster } i \text{ using method } k \text{ (central or distributed)} \\
0 & \text{otherwise}
\end{cases}
\]

where \( j \in \{ \text{isolate}, \text{scan} \} \) and \( k \in \{ \text{central}, \text{distributed} \} \).

\subsection*{Objective Function}
Minimize the total cost:
\[
\text{Total Cost} = \sum_{i=1}^{N} \left( ( \text{isolate\_central}_i \cdot x_{i,\text{isolate},\text{central}} + \text{scan\_central}_i \cdot x_{i,\text{scan},\text{central}} ) \cdot \text{central\_cost} + ( \text{isolate\_distributed}_i \cdot x_{i,\text{isolate},\text{distributed}} + \text{scan\_distributed}_i \cdot x_{i,\text{scan},\text{distributed}} ) \cdot \text{distributed\_cost} \right)
\]

\subsection*{Constraints}
1. Each cluster must have exactly one intervention type applied:
\[
\forall i \in \{1, \ldots, N\}, \quad x_{i,\text{isolate},\text{central}} + x_{i,\text{scan},\text{central}} + x_{i,\text{isolate},\text{distributed}} + x_{i,\text{scan},\text{distributed}} = 1
\]

2. Maximum processing hours for central processing:
\[
\sum_{i=1}^{N} ( \text{isolate\_central}_i \cdot x_{i,\text{isolate},\text{central}} + \text{scan\_central}_i \cdot x_{i,\text{scan},\text{central}} ) \leq \text{max\_central}
\]

3. Maximum processing hours for distributed processing:
\[
\sum_{i=1}^{N} ( \text{isolate\_distributed}_i \cdot x_{i,\text{isolate},\text{distributed}} + \text{scan\_distributed}_i \cdot x_{i,\text{scan},\text{distributed}} ) \leq \text{max\_distributed}
\]

\subsection*{Output}
The output consists of:
\begin{itemize}
    \item A list of interventions detailing:
    \begin{itemize}
        \item cluster_id
        \item type (isolate or scan)
        \item method (central or distributed)
        \item amount (amount_i)
    \end{itemize}
    \item The total cost calculated by the objective function.
\end{itemize}

\end{document}