\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for DEC Production Problem}

\subsection*{Sets}
Let \( N \) be the number of computer systems.

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{is\_workstation}_i \): Boolean indicating if system \( i \) is a workstation.
    \item \( \text{price}_i \): Price of system \( i \) in dollars.
    \item \( \text{disk\_drives}_i \): Average disk drives requested for system \( i \).
    \item \( \text{mem}_i \): Average 256K memory boards requested for system \( i \).
    \item \( \text{max\_cpu} \): Maximum units of CPUs available.
    \item \( \text{min\_disk} \): Minimum units of disk drives available.
    \item \( \text{max\_disk} \): Maximum units of disk drives available.
    \item \( \text{min\_mem} \): Minimum units of 256K memory boards available.
    \item \( \text{max\_mem} \): Maximum units of 256K memory boards available.
    \item \( \text{demand}_i \): Maximum demand for system \( i \).
    \item \( \text{demand\_GP} \): Maximum demand for the GP family.
    \item \( \text{demand\_WS} \): Maximum demand for the WS family.
    \item \( \text{preorder}_i \): Preorder units for system \( i \).
    \item \( \text{alt\_mem} \): Units of alternative memory boards available.
    \item \( \text{alt\_compatible}_i \): Boolean indicating if alternative memory can be used with system \( i \).
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( x_i \): Number of units produced of system \( i \).
    \item \( y_i \): Number of alternative memory boards used for system \( i \).
\end{itemize}

\subsection*{Objective Function}
Maximize total profit:
\[
\text{Maximize } Z = \sum_{i=1}^{N} \text{price}_i \cdot x_i - \sum_{i=1}^{N} \text{cost\_memory}_i \cdot \left( \text{mem}_i \cdot x_i - y_i \right) - \sum_{i=1}^{N} \text{cost\_disk}_i \cdot \text{disk\_drives}_i \cdot x_i
\]

\subsection*{Constraints}
1. CPU constraint:
\[
\sum_{i=1}^{N} x_i \leq \text{max\_cpu}
\]

2. Disk drives constraint:
\[
\sum_{i=1}^{N} \text{disk\_drives}_i \cdot x_i \geq \text{min\_disk}
\]
\[
\sum_{i=1}^{N} \text{disk\_drives}_i \cdot x_i \leq \text{max\_disk}
\]

3. Memory board constraints:
\[
\sum_{i=1}^{N} \text{mem}_i \cdot x_i \geq \text{min\_mem}
\]
\[
\sum_{i=1}^{N} \text{mem}_i \cdot x_i \leq \text{max\_mem}
\]

4. Demand constraints:
\[
x_i \geq \text{preorder}_i \quad \forall i
\]
\[
\sum_{\text{is\_workstation}_i} x_i \leq \text{demand\_WS}
\]
\[
\sum_{\text{is\_workstation}_i = \text{false}} x_i \leq \text{demand\_GP}
\]

5. Alternative memory constraints:
\[
y_i \leq \text{alt\_mem} \quad \forall i \quad \text{if } \text{alt\_compatible}_i
\]

\subsection*{Output}
The resulting solution will be in the following format:
\[
\text{Output} = \left\{
    \text{"system\_output"}: \left[ 
        \left\{ 
            \text{"num\_produced"}: x_i, 
            \text{"total\_256K\_boards\_used"}: \text{mem}_i \cdot x_i, 
            \text{"total\_alt\_boards\_used"}: y_i, 
            \text{"total\_disk\_drives\_used"}: \text{disk\_drives}_i \cdot x_i 
        \right\} 
        \text{ for } i = 1, \ldots, N 
    \right], 
    \text{"profit"}: Z 
\right\}
\]

\end{document}