\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Custom Tees Advertising Campaign}

\subsection*{Parameters}
\begin{itemize}
    \item Let \( A \) be the number of different ad types.
    \item Let \( \text{goal\_young} \) be the goal of clicks from visitors aged 18-25 (in thousands).
    \item Let \( \text{goal\_old} \) be the goal of clicks from visitors older than 25 (in thousands).
    \item Let \( \text{goal\_unique\_young} \) be the goal of unique clicks from visitors aged 18-25 (in thousands).
    \item Let \( \text{goal\_unique\_old} \) be the goal of unique clicks from visitors older than 25 (in thousands).
    \item Let \( \text{young\_click}_{a} \) be the estimated percentage of clicks for ad type \( a \) from the 18-25 age range.
    \item Let \( \text{old\_click}_{a} \) be the estimated percentage of clicks for ad type \( a \) from older visitors.
    \item Let \( \text{cost}_{a} \) be the cost of ad type \( a \) per 1000 clicks.
    \item Let \( \text{max\_click}_{a} \) be the maximum allowable clicks for ad type \( a \) (in thousands).
    \item Let \( \text{unique\_click}_{a} \) be the estimated percentage of unique visitors for ad type \( a \).
    \item Let \( \text{budget} \) be the total advertising budget.
\end{itemize}

\subsection*{Decision Variables}
Let 
\[
x_a \quad \text{for } a = 1, \ldots, A
\]
be the number of clicks purchased for each ad type \( a \) (in thousands).

\subsection*{Objective Function}
Maximize the total number of unique clicks:
\[
\text{Maximize } Z = \sum_{a=1}^{A} \text{unique\_click}_{a} \cdot x_a
\]

\subsection*{Constraints}

1. Total clicks from young visitors:
\[
\sum_{a=1}^{A} \text{young\_click}_{a} \cdot x_a \geq \text{goal\_young}
\]

2. Total clicks from older visitors:
\[
\sum_{a=1}^{A} \text{old\_click}_{a} \cdot x_a \geq \text{goal\_old}
\]

3. Total unique clicks from young visitors:
\[
\sum_{a=1}^{A} \text{unique\_click}_{a} \cdot x_a \geq \text{goal\_unique\_young}
\]

4. Total unique clicks from older visitors:
\[
\sum_{a=1}^{A} \text{unique\_click}_{a} \cdot x_a \geq \text{goal\_unique\_old}
\]

5. Budget constraint:
\[
\sum_{a=1}^{A} \text{cost}_{a} \cdot x_a \leq \text{budget}
\]

6. Maximum clicks constraint:
\[
0 \leq x_a \leq \text{max\_click}_{a}, \quad \text{for } a = 1, \ldots, A
\]

\subsection*{Output}
\begin{itemize}
    \item The solution will provide the number of clicks purchased for each ad type: 
    \[
    \text{clicks} = [x_a \text{ for } a = 1, \ldots, A]
    \]
    \item The total number of unique clicks obtained:
    \[
    \text{total\_unique\_clicks} = Z
    \end{itemize}
\end{document}