\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Production Schedule}

\subsection*{Parameters}
\begin{itemize}
    \item Let \( N \) be the number of months.
    \item Let \( demand_n \) be the demand in month \( n \) for \( n = 1, \ldots, N \).
    \item Let \( max\_regular\_amount \) be the maximum quantity that can be produced using regular production in any month.
    \item Let \( cost\_regular \) be the cost of producing one unit using regular production.
    \item Let \( cost\_overtime \) be the cost of producing one unit using overtime production.
    \item Let \( store\_cost \) be the cost of storing one unit from one month to the next.
    \item Let \( reg\_quant_n \) be the quantity of products produced using regular production in month \( n \).
    \item Let \( over\_quant_n \) be the quantity of products produced using overtime production in month \( n \).
    \item Let \( inventory_n \) be the inventory at the end of month \( n \).
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( reg\_quant_n \) for \( n = 1, \ldots, N \): quantity produced using regular production.
    \item \( over\_quant_n \) for \( n = 1, \ldots, N \): quantity produced using overtime production.
    \item \( inventory_n \) for \( n = 1, \ldots, N \): inventory at the end of month \( n \).
\end{itemize}

\subsection*{Objective Function}
The objective is to minimize the total cost, which includes production costs and storage costs:
\[
\text{Minimize } Z = \sum_{n=1}^{N} \left( cost\_regular \cdot reg\_quant_n + cost\_overtime \cdot over\_quant_n + store\_cost \cdot inventory_n \right)
\]

\subsection*{Constraints}
\begin{itemize}
    \item Demand satisfaction:
    \[
    inventory_n + reg\_quant_n + over\_quant_n \geq demand_n \quad \forall n = 1, \ldots, N
    \]
    
    \item Production capacity (regular production):
    \[
    reg\_quant_n \leq max\_regular\_amount \quad \forall n = 1, \ldots, N
    \]

    \item Inventory balance:
    \[
    inventory_n = (inventory_{n-1} + reg\_quant_n + over\_quant_n - demand_n) \quad \forall n = 2, \ldots, N
    \]
    with \( inventory_1 = 0 \) (no initial inventory).

    \item Non-negativity constraints:
    \[
    reg\_quant_n \geq 0, \quad over\_quant_n \geq 0, \quad inventory_n \geq 0 \quad \forall n = 1, \ldots, N
    \]
\end{itemize}

\end{document}