\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Problem Formulation}

We want to optimize the delivery path for a person starting from the intersection of the 1st Avenue and 1st Street to reach the intersection of the Wth Avenue and Nth Street in a N-1 × W-1 grid. The criterion is to minimize the total travel time.

\subsection*{Variables}

Let:
\begin{itemize}
    \item \( x_{n,w} \) = time taken to travel either north or west from the intersection of the \( w \)th Avenue and \( n \)th Street.
    \item \( \text{west\_time}_{n,w} \) = time taken to move from the intersection of \( w \)th Avenue and \( n \)th Street to the intersection of \( (w+1) \)th Avenue and \( n \)th Street.
    \item \( \text{north\_time}_{n,w} \) = time taken to move from the intersection of \( w \)th Avenue and \( n \)th Street to the intersection of \( w \)th Avenue and \( (n+1) \)th Street.
\end{itemize}

\subsection*{Objective Function}

The objective is to minimize the total travel time \( T \):

\[
\min T = \sum_{i=1}^{m} x_{n_i, w_i}
\]

Where \( m \) is the number of stages (or steps taken).

\subsection*{Constraints}

The movement is restricted to going north or west:

1. From the intersection of \( (w, n) \):
   \[
   x_{n,w} = \begin{cases}
   \text{west\_time}_{n,w} + x_{n,w+1}, & \text{if moving west} \\
   \text{north\_time}_{n,w} + x_{n+1,w}, & \text{if moving north}
   \end{cases}
   \]

2. The boundary conditions are:
   \[
   x_{N-1, W} = 0 \quad \text{(destination)}
   \]
   \[
   x_{N, W-1} = 0 \quad \text{(destination)}
   \]

\subsection*{Output}

The solution will yield:
\begin{itemize}
    \item \( \text{paths} \): A sequence of intersections representing the optimal path taken.
    \item \( \text{total\_time} \): Total time spent to complete the path.
\end{itemize}

\end{document}