\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Oil Refining and Blending}

\subsection*{Parameters}
\begin{itemize}
    \item $I$: Number of raw oils.
    \item $M$: Number of months.
    \item $price_{i,m}$: Purchase price of oil $i$ in month $m$.
    \item $sell\_price$: Selling price per ton of the final product.
    \item $is\_vegetable_i$: Indicator if oil $i$ is a vegetable oil.
    \item $max\_veg$: Maximum refining capacity per month for vegetable oils.
    \item $max\_non\_veg$: Maximum refining capacity per month for non-vegetable oils.
    \item $storage\_size$: Maximum storage capacity for each oil.
    \item $storage\_cost$: Cost per ton per month for storage.
    \item $max\_hardness$: Maximum hardness of the final product.
    \item $min\_hardness$: Minimum hardness of the final product.
    \item $hardness_i$: Hardness of oil $i$.
    \item $init\_amount$: Initial amount of each oil in storage.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item $buyquantity_{i,m}$: Tons of oil $i$ purchased in month $m$.
    \item $refine_{i,m}$: Tons of oil $i$ refined in month $m$.
    \item $storage_{i,m}$: Tons of oil $i$ stored at the end of month $m$.
\end{itemize}

\subsection*{Objective Function}
Maximize profit:
\[
\max \sum_{m=1}^{M} \left( sell\_price \sum_{i=1}^{I} refine_{i,m} - \sum_{i=1}^{I} \left( price_{i,m} \cdot buyquantity_{i,m} + storage\_cost \cdot storage_{i,m} \right) \right)
\]

\subsection*{Constraints}
\begin{align}
    &\text{Storage balance:} \notag \\
    &\quad storage_{i,m} = storage_{i,m-1} + buyquantity_{i,m} - refine_{i,m} \quad \forall i, \, m = 1,...,M \\
    &\quad storage_{i,0} = init\_amount \quad \forall i \\
    &\quad storage_{i,M} = init\_amount \quad \forall i \\
    &\text{Refining capacity:} \notag \\
    &\quad \sum_{i \text{ is vegetable}} refine_{i,m} \leq max\_veg \quad \forall m \\
    &\quad \sum_{i \text{ is non-vegetable}} refine_{i,m} \leq max\_non\_veg \quad \forall m \\
    &\text{Storage capacity:} \notag \\
    &\quad storage_{i,m} \leq storage\_size \quad \forall i, \, m \\
    &\text{Hardness constraints:} \notag \\
    &\quad min\_hardness \leq \frac{\sum_{i=1}^{I} hardness_i \cdot refine_{i,m}}{\sum_{i=1}^{I} refine_{i,m}} \leq max\_hardness \quad \forall m \\
    &\text{Non-negativity:} \notag \\
    &\quad buyquantity_{i,m}, refine_{i,m}, storage_{i,m} \geq 0 \quad \forall i, \, m
\end{align}

\end{document}