\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for DEC Production Optimization}

\subsection*{Sets and Parameters}
Let \( N \) be the number of different computer systems.
\begin{itemize}
    \item \( is\_workstation_i \in \{0, 1\} \): indicator variable for whether system \( i \) is a workstation (1) or a general-purpose system (0).
    \item \( price_i \): price of system \( i \) in dollars.
    \item \( disk_i \): average number of disk drives requested by customers for system \( i \).
    \item \( mem_i \): average units of 256K memory boards required for system \( i \).
    \item \( max\_cpu \): maximum number of CPUs available.
    \item \( min\_disk \): minimum number of disk drives available.
    \item \( max\_disk \): maximum number of disk drives available.
    \item \( min\_mem \): minimum number of 256K memory boards available.
    \item \( max\_mem \): maximum number of 256K memory boards available.
    \item \( demand_i \): maximum demand for system \( i \) in the next quarter.
    \item \( demand\_GP \): maximum demand for the whole GP family.
    \item \( demand\_WS \): maximum demand for the whole WS family.
    \item \( preorder_i \): number of preorders for system \( i \).
    \item \( alt\_mem \): units of alternative memory boards available.
    \item \( alt\_compatible_i \in \{0, 1\} \): indicator for whether the alternative memory board can be used in system \( i \).
\end{itemize}

\subsection*{Decision Variables}
Let \( x_i \) denote the number of systems produced of type \( i \), where \( i = 1, \ldots, N \).

Define:
\[
mem\_used_i = mem_i \cdot x_i
\]
\[
alt\_used_i = \begin{cases} 
0 & \text{if } alt\_compatible_i = 0 \\
x_i & \text{if } alt\_compatible_i = 1 
\end{cases}
\]
\[
disk\_used_i = disk_i \cdot x_i
\]

\subsection*{Objective Function}
Maximize total profit \( P \):
\[
P = \sum_{i=1}^{N} price_i \cdot x_i - \text{costs}
\]

\subsection*{Constraints}
1. CPU constraint:
\[
\sum_{i=1}^{N} x_i \leq max\_cpu
\]

2. Disk drives constraint:
\[
\sum_{i=1}^{N} disk\_used_i \geq min\_disk
\]
\[
\sum_{i=1}^{N} disk\_used_i \leq max\_disk
\]

3. Memory boards constraint:
\[
\sum_{i=1}^{N} mem\_used_i + \sum_{i=1}^{N} alt\_used_i \geq min\_mem
\]
\[
\sum_{i=1}^{N} mem\_used_i + \sum_{i=1}^{N} alt\_used_i \leq max\_mem
\]

4. Demand constraints for each system:
\[
x_i \leq demand_i \quad \forall i
\]

5. Demand constraints for GP and WS families:
\[
\sum_{i \, : \, is\_workstation_i = 0} x_i \leq demand\_GP
\]
\[
\sum_{i \, : \, is\_workstation_i = 1} x_i \leq demand\_WS
\]

6. Preorder constraints:
\[
x_i \geq preorder_i \quad \forall i
\]

\subsection*{Output}
The output will include:
\begin{itemize}
    \item A list of systems produced with the number of systems, total memory boards used, total alternative boards used, and total disk drives used.
    \item The total profit for the next quarter.
\end{itemize}

\end{document}