\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Oil Refining and Blending}

\subsection*{Variables}
Let:
\begin{itemize}
    \item \( buyquantity_{i,m} \) be the amount of oil \( i \) bought in month \( m \).
    \item \( refine_{i,m} \) be the amount of oil \( i \) refined in month \( m \).
    \item \( storage_{i,m} \) be the amount of oil \( i \) stored at the end of month \( m \).
\end{itemize}

\subsection*{Parameters}
Define the following parameters:
\begin{itemize}
    \item \( price_{i,m} \): Price of oil \( i \) in month \( m \).
    \item \( sell\_price \): Selling price per ton of the final product.
    \item \( max\_veg \): Maximum tons of vegetable oils refined per month.
    \item \( max\_non\_veg \): Maximum tons of non-vegetable oils refined per month.
    \item \( storage\_size \): Maximum tons of each raw oil that can be stored.
    \item \( storage\_cost \): Cost of storage per ton per month.
    \item \( max\_hardness \): Maximum allowable hardness of the final product.
    \item \( min\_hardness \): Minimum allowable hardness of the final product.
    \item \( hardness_{i} \): Hardness of oil \( i \).
    \item \( init\_amount \): Initial amount of each type of raw oil in storage.
    \item \( min\_usage \): Minimum tons of each oil that must be used if the oil is selected.
    \item \( dependency_{i,j} \): Dependency matrix indicating oil usage relations.
\end{itemize}

\subsection*{Objective Function}
Maximize the profit given by:
\[
\text{Profit} = \sum_{m=1}^{M} \left( sell\_price \cdot \sum_{i=1}^{I} refine_{i,m} - \sum_{i=1}^{I} (price_{i,m} \cdot buyquantity_{i,m} + storage\_cost \cdot storage_{i,m}) \right)
\]

\subsection*{Constraints}

\textbf{1. Storage Balance:}
\[
storage_{i,m} = storage_{i,m-1} + buyquantity_{i,m} - refine_{i,m} \quad \forall i, m
\]
\[
storage_{i,0} = init\_amount \quad \forall i
\]
\[
storage_{i,M} = init\_amount \quad \forall i
\]

\textbf{2. Refining Limits:}
\[
\sum_{i \in \text{veg}} refine_{i,m} \leq max\_veg \quad \forall m
\]
\[
\sum_{i \in \text{non-veg}} refine_{i,m} \leq max\_non\_veg \quad \forall m
\]

\textbf{3. Hardness Constraints:}
\[
min\_hardness \leq \frac{\sum_{i=1}^{I} hardness_{i} \cdot refine_{i,m}}{\sum_{i=1}^{I} refine_{i,m}} \leq max\_hardness \quad \forall m
\]

\textbf{4. Usage Minimum:}
If oil \( i \) is used (\( refine_{i,m} > 0 \)), then:
\[
refine_{i,m} \geq min\_usage \quad \forall i, m
\]

\textbf{5. Dependency Constraints:}
If \( dependency_{i,j} = 1 \) and \( refine_{i,m} > 0 \), then:
\[
refine_{j,m} \geq min\_usage \quad \forall j \text{ such that } dependency_{i,j} = 1, m
\]

\textbf{6. Oil Selection Limit:}
At most three different oils can be used in any month:
\[
\sum_{i=1}^{I} \text{if } refine_{i,m} > 0 \leq 3 \quad \forall m
\]

\subsection*{Non-negativity Constraints:}
\[
buyquantity_{i,m} \geq 0, \quad refine_{i,m} \geq 0, \quad storage_{i,m} \geq 0 \quad \forall i, m
\]

\end{document}