\documentclass{article}
\usepackage{amsmath}
\begin{document}

\title{Mathematical Model for Floppy Disk Backup Problem}
\author{}
\date{}
\maketitle

\section*{Problem Description}
We are given several files that need to be backed up onto floppy disks, each having a certain capacity. The objective is to minimize the number of floppy disks used while ensuring that the files do not exceed the capacity of the disks.

\section*{Parameters}
\begin{itemize}
    \item Let \( C \) be the capacity of each floppy disk (in GB).
    \item Let \( N \) be the total number of files.
    \item Let \( s_j \) be the size of file \( j \) where \( j \in \{1, 2, \ldots, N\} \).
\end{itemize}

\section*{Decision Variables}
\begin{itemize}
    \item Let \( n \) be the total number of floppy disks used.
    \item Let \( x_{ij} \) be a binary variable that equals 1 if file \( j \) is placed on floppy disk \( i \), and 0 otherwise, where \( i \in \{1, 2, \ldots, n\} \) and \( j \in \{1, 2, \ldots, N\} \).
\end{itemize}

\section*{Objective Function}
The objective is to minimize the total number of floppy disks used:

\[
\text{Minimize } n = \sum_{i=1}^{n} y_i
\]

where \( y_i \) is a binary variable that equals 1 if disk \( i \) is used, and 0 otherwise.

\section*{Constraints}
1. Each file must be assigned to exactly one disk:
   \[
   \sum_{i=1}^{n} x_{ij} = 1 \quad \forall j \in \{1, 2, \ldots, N\}
   \]

2. The total size of files assigned to each disk must not exceed its capacity:
   \[
   \sum_{j=1}^{N} s_j x_{ij} \leq C y_i \quad \forall i \in \{1, 2, \ldots, n\}
   \]

3. The total number of disks used is given by:
   \[
   n \geq y_i \quad \forall i \in \{1, 2, \ldots, n\}
   \]

4. Binary constraints:
   \[
   x_{ij} \in \{0, 1\} \quad \forall i, j
   \]
   \[
   y_i \in \{0, 1\} \quad \forall i
   \]

\section*{Output}
The output of the model will provide:
\begin{itemize}
    \item \( n \): the total number of floppy disks used.
    \item \( \text{whichdisk} \): an array indicating on which disk each file is distributed.
\end{itemize}

\end{document}