\documentclass{article}
\usepackage{amsmath}

\begin{document}

\textbf{MILP Formulation}

\textbf{Sets:}
\begin{itemize}
    \item $N$: Set of clusters, indexed by $i$.
\end{itemize}

\textbf{Parameters:}
\begin{itemize}
    \item $p^{\text{central}}_{\text{isolate},i}$: Processing time for isolation using central processing for cluster $i$.
    \item $p^{\text{central}}_{\text{scan},i}$: Processing time for scanning using central processing for cluster $i$.
    \item $p^{\text{distributed}}_{\text{isolate},i}$: Processing time for isolation using distributed processing for cluster $i$.
    \item $p^{\text{distributed}}_{\text{scan},i}$: Processing time for scanning using distributed processing for cluster $i$.
    \item $c^{\text{central}}$: Opportunity cost per hour for central processing.
    \item $c^{\text{distributed}}$: Opportunity cost per hour for distributed processing.
    \item $h^{\text{max}}_{\text{central}}$: Maximum allowed hours for central processing.
    \item $h^{\text{max}}_{\text{distributed}}$: Maximum allowed hours for distributed processing.
\end{itemize}

\textbf{Variables:}
\begin{itemize}
    \item $x^{\text{central}}_{\text{isolate},i}$: Binary variable, 1 if cluster $i$ is isolated using central processing, 0 otherwise.
    \item $x^{\text{central}}_{\text{scan},i}$: Binary variable, 1 if cluster $i$ is scanned using central processing, 0 otherwise.
    \item $x^{\text{distributed}}_{\text{isolate},i}$: Binary variable, 1 if cluster $i$ is isolated using distributed processing, 0 otherwise.
    \item $x^{\text{distributed}}_{\text{scan},i}$: Binary variable, 1 if cluster $i$ is scanned using distributed processing, 0 otherwise.
\end{itemize}

\textbf{Objective:}
\begin{align}
    \min \ & \sum_{i \in N} \left[ c^{\text{central}} \left( p^{\text{central}}_{\text{isolate},i} x^{\text{central}}_{\text{isolate},i} + p^{\text{central}}_{\text{scan},i} x^{\text{central}}_{\text{scan},i} \right) \right. \nonumber \\
    & \left. + c^{\text{distributed}} \left( p^{\text{distributed}}_{\text{isolate},i} x^{\text{distributed}}_{\text{isolate},i} + p^{\text{distributed}}_{\text{scan},i} x^{\text{distributed}}_{\text{scan},i} \right) \right]
\end{align}

\textbf{Constraints:}
\begin{align}
    & x^{\text{central}}_{\text{isolate},i} + x^{\text{central}}_{\text{scan},i} + x^{\text{distributed}}_{\text{isolate},i} + x^{\text{distributed}}_{\text{scan},i} = 1, \quad \forall i \in N \\
    & \sum_{i \in N} \left(p^{\text{central}}_{\text{isolate},i} x^{\text{central}}_{\text{isolate},i} + p^{\text{central}}_{\text{scan},i} x^{\text{central}}_{\text{scan},i}\right) \leq h^{\text{max}}_{\text{central}} \\
    & \sum_{i \in N} \left(p^{\text{distributed}}_{\text{isolate},i} x^{\text{distributed}}_{\text{isolate},i} + p^{\text{distributed}}_{\text{scan},i} x^{\text{distributed}}_{\text{scan},i}\right) \leq h^{\text{max}}_{\text{distributed}} \\
    & x^{\text{central}}_{\text{isolate},i}, x^{\text{central}}_{\text{scan},i}, x^{\text{distributed}}_{\text{isolate},i}, x^{\text{distributed}}_{\text{scan},i} \in \{0, 1\}, \quad \forall i \in N
\end{align}

\end{document}