\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model}

\subsection*{Variables}
\begin{itemize}
    \item \( buyquantity_{i,m} \): Amount of raw oil \( i \) bought in month \( m \).
    \item \( refine_{i,m} \): Amount of refined oil \( i \) produced in month \( m \).
    \item \( storage_{i,m} \): Amount of raw oil \( i \) stored at the end of month \( m \).
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( price_{i,m} \): Buying price of oil \( i \) in month \( m \).
    \item \( sell\_price \): Selling price of the final product per ton.
    \item \( is\_vegetable_{i} \): Indicator for oil \( i \) being vegetable (1) or non-vegetable (0).
    \item \( max\_veg \): Maximum tons of vegetable oils that can be refined per month.
    \item \( max\_non\_veg \): Maximum tons of non-vegetable oils that can be refined per month.
    \item \( storage\_size \): Maximum storage capacity for each raw oil.
    \item \( storage\_cost \): Cost of storing oil per ton per month.
    \item \( max\_hardness \): Maximum allowable hardness of the final product.
    \item \( min\_hardness \): Minimum allowable hardness of the final product.
    \item \( hardness_{i} \): Hardness of oil \( i \).
    \item \( init\_amount \): Initial amount of each type of raw oil in storage.
    \item \( min\_usage \): Minimum usage required for any oil when it is used.
    \item \( dependency_{i,j} \): Dependency matrix indicating if oil \( j \) must be used when oil \( i \) is used.
\end{itemize}

\subsection*{Objective Function}
Maximize the profit:
\[
\text{Profit} = \sum_{m=1}^{M} \left( sell\_price \cdot \sum_{i=1}^{I} refine_{i,m} - \sum_{i=1}^{I} (price_{i,m} \cdot buyquantity_{i,m}) - storage\_cost \cdot \sum_{i=1}^{I} storage_{i,m} \right)
\]

\subsection*{Constraints}

\begin{itemize}
    \item \textbf{Refining Capacity:}
    \[
    \sum_{i \in \text{vegetable}} refine_{i,m} \leq max\_veg, \quad \forall m
    \]
    \[
    \sum_{i \in \text{non-vegetable}} refine_{i,m} \leq max\_non\_veg, \quad \forall m
    \]
    
    \item \textbf{Storage Capacity:}
    \[
    storage_{i,m} \leq storage\_size, \quad \forall i, \forall m
    \]
    
    \item \textbf{Hardness Constraints:}
    \[
    min\_hardness \leq \frac{\sum_{i=1}^{I} hardness_{i} \cdot refine_{i,m}}{\sum_{i=1}^{I} refine_{i,m}} \leq max\_hardness, \quad \forall m
    \]
    
    \item \textbf{Initial and Final Storage Constraints:}
    \[
    storage_{i,0} = init\_amount, \quad \forall i
    \]
    \[
    storage_{i,M} = init\_amount, \quad \forall i
    \]
    
    \item \textbf{Storage Update:}
    \[
    storage_{i,m} = storage_{i,m-1} + buyquantity_{i,m} - refine_{i,m}, \quad \forall i, \forall m
    \]
    
    \item \textbf{Minimum Usage:}
    \[
    refine_{i,m} \geq min\_usage \cdot \delta_{i,m}, \quad \forall i, \forall m
    \]
    where \( \delta_{i,m} \) is a binary variable indicating whether oil \( i \) is used in month \( m \).

    \item \textbf{Dependency Constraints:}
    \[
    refine_{j,m} \geq dependency_{i,j} \cdot refine_{i,m}, \quad \forall i,j, \forall m \quad \text{(if } dependency_{i,j} = 1)
    \]
    
    \item \textbf{Three Oil Limit:}
    \[
    \sum_{i=1}^{I} \delta_{i,m} \leq 3, \quad \forall m
    \]
\end{itemize}

\end{document}