\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Manufacturing Optimization}

\textbf{Decision Variables:}
\begin{itemize}
    \item Let \( sell_{k,i} \) be the amount of product \( k \) sold in month \( i \).
    \item Let \( manufacture_{k,i} \) be the amount of product \( k \) manufactured in month \( i \).
    \item Let \( storage_{k,i} \) be the amount of product \( k \) stored at the end of month \( i \).
\end{itemize}

\textbf{Parameters:}
\begin{itemize}
    \item \( num_{m} \): Number of machines in the factory.
    \item \( profit_{k} \): Profit for product \( k \) per unit.
    \item \( time_{k,m} \): Time required to produce one unit of product \( k \) on machine \( m \).
    \item \( maintain_{i,m} \): Number of machines that will be down for maintenance in month \( i \).
    \item \( limit_{k,i} \): Marketing limitations on product \( k \) in month \( i \).
    \item \( store\_price \): Cost of storing one unit of product per month.
    \item \( keep\_quantity \): Required stock of each product at the end of subsequent months.
    \item \( n\_workhours \): Total working hours in a month.
\end{itemize}

\textbf{Objective Function:}
\[
\text{Maximize } Z = \sum_{i=1}^{I} \sum_{k=1}^{K} \left( profit_{k} \cdot sell_{k,i} - store\_price \cdot storage_{k,i} \right)
\]

\textbf{Constraints:}

1. \textbf{Production time constraint:}
\[
\sum_{k=1}^{K} \sum_{m=1}^{M} time_{k,m} \cdot manufacture_{k,i} \leq n\_workhours \cdot (num_{m} - \sum_{m=1}^{M} maintain_{i,m}) \quad \forall i
\]

2. \textbf{Selling constraints:}
\[
sell_{k,i} \leq limit_{k,i} \quad \forall k, \forall i
\]

3. \textbf{Inventory balance constraints:}
\[
storage_{k,i} = storage_{k,i-1} + manufacture_{k,i} - sell_{k,i} \quad \forall k, \forall i
\]
\[
storage_{k,i} \leq 100 \quad \forall k, \forall i
\]
\[
storage_{k,I} \geq keep\_quantity \quad \forall k
\]

4. \textbf{Non-negativity constraints:}
\[
sell_{k,i} \geq 0, \quad manufacture_{k,i} \geq 0, \quad storage_{k,i} \geq 0 \quad \forall k, \forall i
\]

\textbf{Output Format:}
\begin{itemize}
    \item \( sell \): Selling quantities for each product in each month.
    \item \( manufacture \): Manufactured quantities for each product in each month.
    \item \( storage \): Storage levels for each product in each month.
\end{itemize}

\end{document}