\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for DEC Production Decision}

\subsection*{Variables}
Let:
\begin{itemize}
    \item $x_i$: the number of systems produced for system $i$ where $i = 1, \ldots, N$.
    \item $y_i$: the number of 256K memory boards used for system $i$.
    \item $z_i$: the number of alternative memory boards used for system $i$.
    \item $d_i$: the number of disk drives used for system $i$.
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item $N$: number of different systems.
    \item $is\_workstation[i]$: boolean indicating if system $i$ is a workstation.
    \item $price[i]$: price of system $i$ in dollars.
    \item $disk[i]$: average number of disk drives requested for system $i$.
    \item $mem[i]$: average number of 256K memory boards requested for system $i$.
    \item $max\_cpu$: maximum number of CPUs available.
    \item $min\_disk$: minimum disk drives available.
    \item $max\_disk$: maximum disk drives available.
    \item $min\_mem$: minimum 256K memory boards available.
    \item $max\_mem$: maximum 256K memory boards available.
    \item $demand[i]$: maximum demand for system $i$.
    \item $demand\_GP$: maximum demand for the GP family.
    \item $demand\_WS$: maximum demand for the WS family.
    \item $preorder[i]$: preorders for system $i$.
    \item $alt\_mem$: units of alternative memory boards available.
    \item $alt\_compatible[i]$: boolean indicating if alternative memory can be used in system $i$.
\end{itemize}

\subsection*{Objective Function}
Maximize the profit:
\[
\text{Profit} = \sum_{i=1}^{N} (price[i] \cdot x_i) - \text{Costs}
\]

\subsection*{Constraints}
\begin{itemize}
    \item CPU Constraint:
    \[
    \sum_{i=1}^{N} x_i \leq max\_cpu
    \]

    \item Disk Drives Constraint:
    \[
    \sum_{i=1}^{N} disk[i] \cdot x_i \leq max\_disk \quad \text{and} \quad \sum_{i=1}^{N} disk[i] \cdot x_i \geq min\_disk
    \]

    \item Memory Boards Constraint:
    \[
    \sum_{i=1}^{N} mem[i] \cdot x_i \leq max\_mem \quad \text{and} \quad \sum_{i=1}^{N} mem[i] \cdot x_i \geq min\_mem
    \]

    \item Demand Constraints:
    \[
    x_i \leq demand[i] \quad \forall i
    \]
    \[
    \sum_{i \text{ such that } is\_workstation[i]} x_i \leq demand\_WS
    \]
    \[
    \sum_{i \text{ such that } \neg is\_workstation[i]} x_i \leq demand\_GP
    \]

    \item Preorder Constraints:
    \[
    x_i \geq preorder[i] \quad \forall i
    \]

    \item Alternative Memory Boards Usage Constraint (only for compatible systems):
    \[
    z_i \leq alt\_mem \quad \text{if } alt\_compatible[i] \text{ is true}
    \]

    \item 256K Boards Usage:
    \[
    y_i = mem[i] \cdot x_i \quad \forall i
    \]

    \item Disk Drives Usage:
    \[
    d_i = disk[i] \cdot x_i \quad \forall i
    \]

\end{itemize}

\end{document}