\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Custom Tees Advertising Campaign}

\subsection*{Variables}
Let \( x_a \) be the number of clicks purchased for ad type \( a \) in thousands, where \( a = 1, 2, \ldots, A \).

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{goal\_young} \): Target clicks from visitors aged 18-25 (in thousands).
    \item \( \text{goal\_old} \): Target clicks from visitors older than 25 (in thousands).
    \item \( \text{goal\_unique\_young} \): Target unique clicks from visitors aged 18-25 (in thousands).
    \item \( \text{goal\_unique\_old} \): Target unique clicks from visitors older than 25 (in thousands).
    \item \( \text{young\_click}_a \): Estimated percentage of clicks from 18-25 age range for ad type \( a \).
    \item \( \text{old\_click}_a \): Estimated percentage of clicks from older visitors for ad type \( a \).
    \item \( \text{cost}_a \): Cost of ad type \( a \) (per 1000 clicks).
    \item \( \text{max\_click}_a \): Maximum allowable clicks for ad type \( a \) (in thousands).
    \item \( \text{unique\_click}_a \): Estimated percentage of unique visitors for ad type \( a \).
\end{itemize}

\subsection*{Objective Function}
Minimize the total cost:
\[
\text{Total Cost} = \sum_{a=1}^{A} \text{cost}_a \cdot x_a
\]

\subsection*{Constraints}

1. Clicks from visitors aged 18-25:
\[
\sum_{a=1}^{A} \text{young\_click}_a \cdot x_a \geq \text{goal\_young}
\]

2. Clicks from visitors older than 25:
\[
\sum_{a=1}^{A} \text{old\_click}_a \cdot x_a \geq \text{goal\_old}
\]

3. Unique clicks from visitors aged 18-25:
\[
\sum_{a=1}^{A} \text{unique\_click}_a \cdot x_a \geq \text{goal\_unique\_young}
\]

4. Unique clicks from visitors older than 25:
\[
\sum_{a=1}^{A} (1 - \text{unique\_click}_a) \cdot x_a \geq \text{goal\_unique\_old}
\]

5. Maximum allowable clicks for each ad type:
\[
x_a \leq \text{max\_click}_a \quad \forall a
\]

6. Non-negativity:
\[
x_a \geq 0 \quad \forall a
\]

\subsection*{Output}
The solution will provide:
\begin{itemize}
    \item \( x_a \): The number of clicks purchased for each ad type \( a \) in thousands.
    \item \text{total\_cost}: The total cost of the ad campaign.
\end{itemize}

\end{document}