\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model}

\subsection*{Sets}
\begin{itemize}
    \item Let \( I \) be the set of oils, indexed by \( i \).
    \item Let \( M \) be the set of months, indexed by \( m \).
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( price_{i,m} \): Price of oil \( i \) in month \( m \).
    \item \( sell\_price \): Selling price of the final product per ton.
    \item \( is\_vegetable_{i} \): Indicator if oil \( i \) is vegetable or not.
    \item \( max\_veg \): Maximum tons of vegetable oils refinable per month.
    \item \( max\_non\_veg \): Maximum tons of non-vegetable oils refinable per month.
    \item \( storage\_size \): Maximum tons of oil that can be stored.
    \item \( storage\_cost \): Cost of storage per ton per month.
    \item \( max\_hardness \): Maximum hardness of the final product.
    \item \( min\_hardness \): Minimum hardness of the final product.
    \item \( hardness_{i} \): Hardness of oil \( i \).
    \item \( init\_amount \): Initial amount of each type of oil in storage.
    \item \( min\_usage \): Minimum tons of oil \( i \) to use if it is used.
    \item \( dependency_{i,j} \): Dependency relation where if \( dependency_{i,j} = 1 \), then oil \( j \) must be used if oil \( i \) is used.
\end{itemize}

\subsection*{Variables}
\begin{itemize}
    \item \( buyquantity_{i,m} \): Amount of oil \( i \) bought in month \( m \).
    \item \( refine_{i,m} \): Amount of oil \( i \) refined in month \( m \).
    \item \( storage_{i,m} \): Amount of oil \( i \) stored at the end of month \( m \).
\end{itemize}

\subsection*{Objective Function}
Maximize profit:
\[
\text{Maximize} \quad Z = \sum_{m=1}^{M} \left( sell\_price \cdot \sum_{i=1}^{I} refine_{i,m} - \sum_{i=1}^{I} (buyquantity_{i,m} \cdot price_{i,m} + storage_{i,m} \cdot storage\_cost) \right)
\]

\subsection*{Constraints}

\subsubsection*{1. Refining Limitations}
For each month \( m \):
\[
\sum_{i \in I, is\_vegetable_i=1} refine_{i,m} \leq max\_veg
\]
\[
\sum_{i \in I, is\_vegetable_i=0} refine_{i,m} \leq max\_non\_veg
\]

\subsubsection*{2. Storage Limitations}
For each oil \( i \) in month \( m \):
\[
storage_{i,m} \leq storage\_size
\]

\subsubsection*{3. Initial and Final Storage Condition}
For each oil \( i \):
\[
storage_{i,0} = init\_amount
\]
\[
storage_{i,M} = init\_amount
\]

\subsubsection*{4. Hardness Constraint}
For each month \( m \):
\[
min\_hardness \leq \frac{\sum_{i=1}^{I} hardness_{i} \cdot refine_{i,m}}{\sum_{i=1}^{I} refine_{i,m}} \leq max\_hardness
\]

\subsubsection*{5. Dependency Condition}
For each oil \( i \) used in month \( m \):
\[
refine_{i,m} \geq min\_usage \quad \text{if } \sum_{j=1}^{I} refine_{j,m} > 0
\]
If \( dependency_{i,j} = 1 \) and \( refine_{i,m} > 0 \):
\[
refine_{j,m} \geq min\_usage
\]

\subsubsection*{6. Storage Update Equation}
For each oil \( i \) in month \( m \):
\[
storage_{i,m} = storage_{i,m-1} + buyquantity_{i,m} - refine_{i,m}
\]

\subsubsection*{7. Oil Usage Limitation}
The food may be made up of at most three oils in any month:
\[
\sum_{i=1}^{I} \left( \text{IF } refine_{i,m} > 0 \text{ THEN } 1 \text{ ELSE } 0 \right) \leq 3
\]

\end{document}