\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for the Company Production Problem}

\subsection*{Variables}
Let:
\begin{itemize}
    \item $x_i$ be the number of units produced of product $i$ for $i = 1, \ldots, N$.
    \item $o$ be the number of hours of overtime assembly labor scheduled.
    \item $m$ be the total amount of raw materials bought.
\end{itemize}

\subsection*{Parameters}
Let:
\begin{itemize}
    \item $assemblyHour_i$: hours of assembly labor required for product $i$.
    \item $testingHour_i$: hours of testing required for product $i$.
    \item $materialCost_i$: cost of materials for product $i$ in dollars.
    \item $maxAssembly$: maximum hours of assembly labor available daily.
    \item $maxTesting$: maximum hours of testing available daily.
    \item $price_i$: selling price of product $i$ in dollars.
    \item $maxOvertimeAssembly$: maximum hours of overtime assembly labor that can be scheduled.
    \item $overtimeAssemblyCost$: cost of overtime assembly labor per hour.
    \item $materialDiscount$: percentage discount on materials if the daily bill exceeds the threshold.
    \item $discountThreshold$: threshold amount for the material discount in dollars.
\end{itemize}

\subsection*{Objective Function}
We want to maximize the daily profit:
\[
\text{Maximize } Z = \sum_{i=1}^{N} (price_i \cdot x_i) - \left( \sum_{i=1}^{N} (materialCost_i \cdot x_i) - \text{Discount} + overtimeAssemblyCost \cdot o \right)
\]
where the discount is calculated as:
\[
\text{Discount} = 
\begin{cases} 
\frac{materialDiscount}{100} \cdot \sum_{i=1}^{N} (materialCost_i \cdot x_i) & \text{if } \sum_{i=1}^{N} (materialCost_i \cdot x_i) > discountThreshold \\
0 & \text{otherwise}
\end{cases}
\]

\subsection*{Constraints}
1. Assembly labor constraint:
\[
\sum_{i=1}^{N} (assemblyHour_i \cdot x_i) + o \leq maxAssembly + maxOvertimeAssembly
\]

2. Testing labor constraint:
\[
\sum_{i=1}^{N} (testingHour_i \cdot x_i) \leq maxTesting
\]

3. Non-negativity and integer constraints:
\[
x_i \geq 0 \quad \text{and must be integer for } i = 1, \ldots, N
\]
\[
o \geq 0
\]

4. Raw material bought:
\[
m = \sum_{i=1}^{N} (materialCost_i \cdot x_i)
\]

\subsection*{Output}
The outputs will include:
\begin{itemize}
    \item $dailyProfit$: The maximized daily profit.
    \item $unitsProduced_i$: The number of units of product $i$ produced, for $i = 1, \ldots, N$.
    \item $overtimeAssembly$: The number of hours of overtime assembly labor scheduled.
    \item $materialBought$: The total amount of raw materials bought.
\end{itemize}

\end{document}