\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Food Manufacturing}

\subsection*{Parameters}
\begin{itemize}
    \item Let \( I \) be the number of oils.
    \item Let \( M \) be the number of months.
    \item \( price_{i,m} \): Price of oil \( i \) in month \( m \).
    \item \( sell\_price \): Selling price per ton of the final product.
    \item \( is\_vegetable_i \): Indicator if oil \( i \) is vegetable (1) or non-vegetable (0).
    \item \( max\_veg \): Maximum tons of vegetable oils refined per month.
    \item \( max\_non\_veg \): Maximum tons of non-vegetable oils refined per month.
    \item \( storage\_size \): Maximum storage capacity per oil.
    \item \( storage\_cost \): Cost of storing oil per ton per month.
    \item \( max\_hardness \): Maximum allowable hardness of the final product.
    \item \( min\_hardness \): Minimum allowable hardness of the final product.
    \item \( hardness_i \): Hardness of oil \( i \).
    \item \( init\_amount \): Initial amount of each oil in storage.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( buyquantity_{i,m} \): Amount of oil \( i \) bought in month \( m \).
    \item \( refine_{i,m} \): Amount of oil \( i \) refined in month \( m \).
    \item \( storage_{i,m} \): Amount of oil \( i \) stored at the end of month \( m \).
\end{itemize}

\subsection*{Objective Function}
Maximize profit:
\[
\text{Maximize } Z = \sum_{m=1}^{M} \left( sell\_price \cdot \sum_{i=1}^{I} refine_{i,m} - \sum_{i=1}^{I} price_{i,m} \cdot buyquantity_{i,m} - storage\_cost \cdot \sum_{i=1}^{I} storage_{i,m} \right)
\]

\subsection*{Constraints}

\begin{itemize}
    \item Refining Constraints:
    \begin{align*}
        \sum_{i=1}^{I} \text{is\_vegetable}_i \cdot refine_{i,m} & \leq max\_veg, \quad \forall m = 1,\ldots,M \\
        \sum_{i=1}^{I} (1 - \text{is\_vegetable}_i) \cdot refine_{i,m} & \leq max\_non\_veg, \quad \forall m = 1,\ldots,M
    \end{align*}

    \item Storage Constraints:
    \begin{align*}
        storage_{i,m} & \leq storage\_size, \quad \forall i = 1,\ldots,I, \forall m = 1,\ldots,M \\
        storage_{i,m} & \geq 0, \quad \forall i = 1,\ldots,I, \forall m = 1,\ldots,M \\
        storage_{i,m} & = storage_{i,m-1} + buyquantity_{i,m} - refine_{i,m}, \quad \forall i = 1,\ldots,I, \forall m = 1,\ldots,M
    \end{align*}
    
    \item Initial and Final Storage:
    \begin{align*}
        storage_{i,0} & = init\_amount, \quad \forall i = 1,\ldots,I \\
        storage_{i,M} & = init\_amount, \quad \forall i = 1,\ldots,I
    \end{align*}

    \item Hardness Constraints:
    \begin{align*}
        \frac{\sum_{i=1}^{I} hardness_i \cdot refine_{i,m}}{\sum_{i=1}^{I} refine_{i,m}} & \leq max\_hardness, \quad \forall m = 1,\ldots,M \\
        \frac{\sum_{i=1}^{I} hardness_i \cdot refine_{i,m}}{\sum_{i=1}^{I} refine_{i,m}} & \geq min\_hardness, \quad \forall m = 1,\ldots,M
    \end{align*}
\end{itemize}

\end{document}