\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model}

\textbf{Variables:}
\begin{itemize}
    \item Let \( x_i \) be the production quantity of the \( i \)-th product, where \( i = 1, 2, \ldots, P \).
    \item Let \( u \) be a binary variable that indicates whether the company upgrades its machine capacity (\( u = 1 \)) or not (\( u = 0 \)).
\end{itemize}

\textbf{Parameters:}
\begin{itemize}
    \item \( \text{cash} \): Total available cash.
    \item \( \text{hour}_i \): Machine hours required per unit of the \( i \)-th product.
    \item \( \text{cost}_i \): Production cost per unit of the \( i \)-th product.
    \item \( \text{price}_i \): Selling price per unit of the \( i \)-th product.
    \item \( \text{investPercentage}_i \): Percentage of sales revenue from the \( i \)-th product made available for operations.
    \item \( \text{upgradeHours} \): Additional machine hours gained by upgrading.
    \item \( \text{upgradeCost} \): Cost of upgrading.
    \item \( \text{availableHours} \): Total available machine hours in the current production period.
\end{itemize}

\textbf{Objective Function:}
We aim to maximize the total net income:
\[
\text{Maximize } Z = \sum_{i=1}^{P} \left( \text{price}_i x_i - \text{cost}_i x_i - \text{investPercentage}_i \cdot \text{price}_i x_i \right) - \text{upgradeCost} \cdot u
\]

\textbf{Constraints:}

1. Cash availability constraint:
\[
\sum_{i=1}^{P} \text{cost}_i x_i \leq \text{cash}
\]

2. Machine capacity constraint:
\[
\sum_{i=1}^{P} \text{hour}_i x_i \leq \text{availableHours} + \text{upgradeHours} \cdot u
\]

3. Non-negativity and integer constraints:
\[
x_i \geq 0, \quad \forall i \in \{1, 2, \ldots, P\}
\]
\[
u \in \{0, 1\}
\]

\textbf{Output Variables:}
\begin{itemize}
    \item \( \text{net\_income} = Z \)
    \item \( \text{production} = [x_1, x_2, \ldots, x_P] \)
    \item \( \text{upgrade} = u \)
\end{itemize}

\end{document}