\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Mathematical Model for Mining Operations}

\subsection*{Indices and Sets}
\begin{itemize}
    \item $k \in \{1, 2, \dots, n\_mines\}$: Index for mines.
    \item $i \in \{1, 2, \dots, I\}$: Index for years.
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item $n\_maxwork$: Maximum number of mines that can be operated in any one year.
    \item $royalty_k$: Yearly royalties payable for keeping mine $k$ open.
    \item $limit_k$: Upper limit of ore that can be extracted from mine $k$ in a year.
    \item $quality_k$: Quality of ore from mine $k$.
    \item $requiredquality_i$: Required quality of the blended ore in year $i$.
    \item $price$: Selling price per ton of the blended ore.
    \item $discount$: Discount rate per annum.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item $isoperated_{k,i} \in \{0, 1\}$: Binary variable, 1 if mine $k$ is operated in year $i$, 0 otherwise.
    \item $amount_{k,i} \geq 0$: Amount of ore produced by mine $k$ in year $i$.
\end{itemize}

\subsection*{Objective Function}
Maximize the present value of profit over the years:

\[
\text{Maximize} \quad \sum_{i=1}^{I} \frac{1}{(1 + discount)^i} \left( \text{Revenue}_i - \text{Cost}_i \right)
\]

where:

\[
\text{Revenue}_i = price \times \sum_{k=1}^{n\_mines} amount_{k,i}
\]

\[
\text{Cost}_i = \sum_{k=1}^{n\_mines} royalty_k \times isoperated_{k,i}
\]

\subsection*{Constraints}
\begin{itemize}
    \item Blended quality constraint for each year $i$:
    \[
    \sum_{k=1}^{n\_mines} quality_k \times amount_{k,i} = requiredquality_i \times \sum_{k=1}^{n\_mines} amount_{k,i}
    \]

    \item Ore production limit for each mine $k$ and year $i$:
    \[
    amount_{k,i} \leq limit_k \times isoperated_{k,i}
    \]

    \item Maximum number of mines operated in each year $i$:
    \[
    \sum_{k=1}^{n\_mines} isoperated_{k,i} \leq n\_maxwork
    \]

    \item Non-negativity constraint for ore amount:
    \[
    amount_{k,i} \geq 0
    \]

    \item Binary constraint for operation:
    \[
    isoperated_{k,i} \in \{0, 1\}
    \]
\end{itemize}

\subsection*{Output}
The output includes the operation status of each mine and their production levels for each year.

\begin{itemize}
    \item $isoperated = [[isoperated_{k,i} \text{ for } i \text{ in } 1,\ldots,I] \text{ for } k \text{ in } 1,\ldots,K]$
    \item $amount = [[amount_{k,i} \text{ for } i \text{ in } 1,\ldots,I] \text{ for } k \text{ in } 1,\ldots,K]$
\end{itemize}

\end{document}