\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Custom Tees Advertising Campaign}

\subsection*{Variables}
Let \( x_a \) be the number of clicks purchased for ad type \( a \) (in thousands), where \( a = 1, 2, \ldots, A \).

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{goal\_young} \): Target clicks from visitors aged 18-25 (in thousands).
    \item \( \text{goal\_old} \): Target clicks from visitors older than 25 (in thousands).
    \item \( \text{goal\_unique\_young} \): Target unique clicks from visitors aged 18-25 (in thousands).
    \item \( \text{goal\_unique\_old} \): Target unique clicks from visitors older than 25 (in thousands).
    \item \( \text{young\_click}_a \): Estimated percentage of clicks from 18-25 age range for ad type \( a \).
    \item \( \text{old\_click}_a \): Estimated percentage of clicks from older visitors for ad type \( a \).
    \item \( \text{cost}_a \): Cost per 1000 clicks for ad type \( a \).
    \item \( \text{max\_click}_a \): Maximum allowable clicks for ad type \( a \) (in thousands).
    \item \( \text{unique\_click}_a \): Estimated percentage of unique visitors for each ad type \( a \).
    \item \( \text{budget} \): Total advertising budget.
\end{itemize}

\subsection*{Objective Function}
Maximize the total number of unique clicks:

\[
\text{Maximize } Z = \sum_{a=1}^{A} \text{unique\_click}_a \cdot x_a
\]

\subsection*{Constraints}
\begin{align*}
    & \sum_{a=1}^{A} \text{young\_click}_a \cdot x_a \geq \text{goal\_young} \quad & \text{(Target clicks from young visitors)} \\
    & \sum_{a=1}^{A} \text{old\_click}_a \cdot x_a \geq \text{goal\_old} \quad & \text{(Target clicks from old visitors)} \\
    & \sum_{a=1}^{A} \text{unique\_click}_a \cdot x_a \geq \text{goal\_unique\_young} \quad & \text{(Target unique clicks from young visitors)} \\
    & \sum_{a=1}^{A} \text{unique\_click}_a \cdot x_a \geq \text{goal\_unique\_old} \quad & \text{(Target unique clicks from old visitors)} \\
    & \sum_{a=1}^{A} \text{cost}_a \cdot x_a \leq \text{budget} \quad & \text{(Budget constraint)} \\
    & x_a \leq \text{max\_click}_a \quad & \text{for each } a = 1, 2, \ldots, A \\
    & x_a \geq 0 \quad & \text{for each } a = 1, 2, \ldots, A
\end{align*}

\subsection*{Output Variables}
\begin{itemize}
    \item \( \text{clicks} = [x_1, x_2, \ldots, x_A] \): Number of clicks purchased for each ad type (in thousands).
    \item \( \text{total\_unique\_clicks} = \sum_{a=1}^{A} \text{unique\_click}_a \cdot x_a \): Total number of unique clicks.
\end{itemize}

\end{document}