\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Minimizing Labour Costs}

\subsection*{Indices and Sets}
\begin{itemize}
    \item \( k \): Index for manpower categories, \( k = 1, 2, \ldots, K \).
    \item \( i \): Index for years, \( i = 1, 2, \ldots, I \).
\end{itemize}

\subsection*{Parameters}
\begin{itemize}
    \item \( \text{requirement}_{k,i} \): Required number of manpower \( k \) in year \( i \).
    \item \( \text{strength}_k \): Current strength of manpower \( k \).
    \item \( \text{lessonewaste}_k \): Wastage rate for manpower \( k \) with less than one year's service.
    \item \( \text{moreonewaste}_k \): Wastage rate for manpower \( k \) with more than one year's service.
    \item \( \text{recruit}_k \): Maximum number of recruitments possible for manpower \( k \) in any year.
    \item \( \text{costredundancy}_k \): Cost of making one manpower \( k \) redundant.
    \item \( \text{num\_overman} \): Maximum number of overmanning allowed for the whole company.
    \item \( \text{costoverman}_k \): Extra cost per overmanned manpower \( k \) per year.
    \item \( \text{num\_shortwork} \): Maximum number of short-time workers allowed per manpower category.
    \item \( \text{costshort}_k \): Cost per short-time working employee of manpower \( k \) per year.
\end{itemize}

\subsection*{Decision Variables}
\begin{itemize}
    \item \( \text{recruit}_{k,i} \): Number of manpower \( k \) recruited in year \( i \).
    \item \( \text{redundant}_{k,i} \): Number of manpower \( k \) made redundant in year \( i \).
    \item \( \text{overmanning}_{k,i} \): Number of overmanned manpower \( k \) in year \( i \).
    \item \( \text{short}_{k,i} \): Number of manpower \( k \) on short-time working in year \( i \).
    \item \( \text{employed}_{k,i} \): Number of manpower \( k \) employed at the start of year \( i \).
\end{itemize}

\subsection*{Objective Function}
Minimize the total cost:
\[
\begin{align*}
\text{Minimize} \quad & \sum_{i=1}^{I} \sum_{k=1}^{K} \left( \text{costredundancy}_k \cdot \text{redundant}_{k,i} + \text{costoverman}_k \cdot \text{overmanning}_{k,i} + \text{costshort}_k \cdot \text{short}_{k,i} \right)
\end{align*}
\]

\subsection*{Constraints}
\begin{itemize}
    \item \textbf{Manpower Balancing:} For each \( k, i \),
    \[
    \text{employed}_{k,i} = 
    \begin{cases} 
    \text{strength}_k, & i = 1 \\
    (1 - \text{moreonewaste}_k) \cdot (\text{employed}_{k,i-1} - \text{redundant}_{k,i-1}) + (1 - \text{lessonewaste}_k) \cdot \text{recruit}_{k,i-1}, & i > 1
    \end{cases}
    \]
    
    \item \textbf{Requirement Fulfillment:} For each \( k, i \),
    \[
    \text{employed}_{k,i} + \text{overmanning}_{k,i} + 0.5 \cdot \text{short}_{k,i} \geq \text{requirement}_{k,i}
    \]

    \item \textbf{Recruitment Limitation:} For each \( k, i \),
    \[
    \text{recruit}_{k,i} \leq \text{recruit}_k
    \]

    \item \textbf{Overmanning Limitation:} For each \( i \),
    \[
    \sum_{k=1}^{K} \text{overmanning}_{k,i} \leq \text{num\_overman}
    \]
    
    \item \textbf{Short-time Working Limitation:} For each \( k, i \),
    \[
    \text{short}_{k,i} \leq \text{num\_shortwork}
    \]

    \item \textbf{Non-negativity:} All decision variables \(\text{recruit}_{k,i}, \text{redundant}_{k,i}, \text{overmanning}_{k,i}, \text{short}_{k,i}\) must be non-negative.
\end{itemize}

\end{document}