\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Linear Programming Model for Steel Production}

\textbf{Variables:}
\begin{itemize}
    \item \( x_k \): Amount of mineral \( k \) melted (in tons), for \( k = 1, 2, \ldots, K \).
    \item \( n_{mang} \): Amount of Manganese added (in tons).
\end{itemize}

\textbf{Parameters:}
\begin{itemize}
    \item \( n_{steel\_quant} \): Total quantity of steel required (in tons).
    \item \( mn_{percent} \): Minimum percentage of Manganese in the steel.
    \item \( si_{min} \): Minimum percentage of Silicon in the steel.
    \item \( si_{max} \): Maximum percentage of Silicon in the steel.
    \item \( contsi_k \): Percentage of Silicon in mineral \( k \).
    \item \( contmn_k \): Percentage of Manganese in mineral \( k \).
    \item \( mang\_price \): Price of Manganese (in million euros per ton).
    \item \( cost_k \): Cost of mineral \( k \) (in million euros per thousand tons).
    \item \( sell\_price \): Selling price of the produced steel (in million euros per ton).
    \item \( melt\_price \): Cost of melting a ton of mineral (in million euros).
\end{itemize}

\textbf{Objective:} Maximize profit, given by

\[
\text{Profit} = (sell\_price \cdot n_{steel\_quant}) - \left( \sum_{k=1}^{K} \left( \frac{cost_k}{1000} \cdot x_k + melt\_price \cdot x_k \right) + mang\_price \cdot n_{mang} \right)
\]

\textbf{Constraints:}
1. Total weight of steel produced:
\[
n_{mang} + \sum_{k=1}^{K} x_k = n_{steel\_quant}
\]

2. Manganese percentage in steel:
\[
\frac{\sum_{k=1}^{K} contmn_k \cdot x_k + n_{mang}}{n_{steel\_quant}} \geq \frac{mn_{percent}}{100}
\]

3. Silicon percentage in steel:
\[
si_{min} \leq \frac{\sum_{k=1}^{K} contsi_k \cdot x_k}{n_{steel\_quant}} \leq si_{max}
\]

4. Non-negativity:
\[
x_k \geq 0, \quad n_{mang} \geq 0 \quad \forall k
\]

\textbf{Output:}
\begin{itemize}
    \item \( amount = [x_1, x_2, \ldots, x_K] \): Amount of each mineral melted.
    \item \( num_{mang} = n_{mang} \): Amount of Manganese directly added.
\end{itemize}

\end{document}